% !TEX root = z_output/_BjornClasses.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% 80 characters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\input{../macros.tex}

%\def\excludeversion#1{\includeversion{#1}}

\excludeversion{Oct18}
\excludeversion{Oct20}
\excludeversion{Oct25}
\excludeversion{Oct27}
\excludeversion{Nov1}
\includeversion{Nov3}
\includeversion{Nov8}
\includeversion{Nov10}


\begin{document}
\begin{Oct18}
\section*{Algebraic Geometry --- 18 October}
\subsubsection*{Valuative criterion for Separatedness}
$K[x]_{(x)}$ is a DVR --- the local ring of a point on a curve. Thinking of it this way, a DVR should always have two points, as you take out all the points but the generic and the point zero. The local ring of a point on a curve should always be a DVR, as you can measure the vanishing at zero.

To obtain a criterion for the separatedness of $X$, we'd like to map $C-\{x\}$, for $C$ a curve, into $X$, and see if it extends to $C$ in more than one way. The problem is that $C$ might be too big to fit inside $X$, say if $X$ is missing a bunch of points. Taking the limit of curves with less and less points, you get DVRs. It'll suffice to use DVRs if it's of finite type, but in general we need all valuation rings.

\begin{thm*}
Let $f:X\to Y$ be
any morphism where $X$ is noetherian. The $f$ is separated \Iff
\begin{enumerate}\squishlist
\item $X\to X\times_Y X$ is quasicompact
\item whenever $R$ is a valuation ring over $S$, if $K=\text{frac}(R)$, there is at most one lifting (dotted) in any commuting
diagram of the following form:
\[\xymatrix@C=0cm{
(0)\,\makebox[-.05cm][l]{$\in$}\ar@{|->}[d]&&\Spec K\ar[rr]\ar[d]&
\qquad \qquad &X\ar[d]^f\\
\xi\,\makebox[-.05cm][l]{\,\,$\in$}&&\Spec R\ar[rr]\ar@{-->}[rru]&&Y
}\]
i.e.\ the map $X(R)\to X(K)$ is injective.
\end{enumerate}
\end{thm*}
\begin{defn*}
A $k$-variety is a separated scheme of finite type over a field $k$.
\end{defn*}
\noindent Hartshorne wants $k=\overline k$ and integrality. ``If you want a variety to act like the set of its points, you really want it to be reduced and $k=\overline k$.'' ``In going from a perfect field to its algebraic closure, why not look at the variety over the closure taken with the action of the absolute Galois group?''
\subsubsection*{Rational Functions}
\begin{defn*} If $X$ is an integral scheme, a rational function on $X$ is an element of the function field $\calO_{X,\eta}$. Alternatively, it's an equivalence class of functions on open subsets on $X$.
\end{defn*}
\noindent Note that in this situation, as $X$ is integral, these are rational maps to something separated, and these can be sewed...
\begin{defn*} Let $X$, $Y$ be $S$-schemes. A rational map $X\to Y$ is an equivalence class of $S$-maps from a dense open subscheme of $X$ to $Y$.
\end{defn*}
Thus usual situation is where $X$ is integral and $Y$ is separated over $S$. In this case, if $(U,\phi)\sim(V,\psi)$, then $\phi$ and $\psi$ agree on $U\cup V$, so we can sew representatives together --- the the pairs in an equivalence class glue. [This fails if $Y$ is not separated --- try mapping $\A^1$ into the bug-eyed line.]
\begin{exmp*}
$\A^2\to\PP^1$ given by $(x,y)\mapsto [x:y]$. [Doesn't extend to a morphism, as it takes two different constant values on the two axes.]
\end{exmp*}
\begin{prop*}
Let $k$ be any field, $X$ be an integral $k$-variety and $Y$ a $k$-variety. Let $K=\kappa(X)=\calO_{X,\eta}$ be the function field. Then there is a bijection
\[\{\text{rational maps $X\to Y$}\}\longleftrightarrow\{\text{$k$-morphisms $\Spec K\to Y$}\}=Y(K)\]
given by $\phi\mapsto (\spec K\to U\to Y)$.
\end{prop*}
\begin{proof}[Sketch]
Let $(\spec A_i)$ be the inverse system of all nonempty affine open subschemes of $X$, so that $A_i$ is a directed system of rings, with $\varinjlim A_i=K$. Then if $U$ runs over all dense opens in $X$
\[\{\text{rational maps $X\to Y$}\}:=\varinjlim_U Y(U)=\varinjlim Y(A_i)= Y(\varinjlim A_i)=Y(K)\]
The second last thing holds in general when $Y$ is locally of finite presentation.

In fact, suppose that $Z$ is an $S$-scheme locally of finite presentation, and suppose for simplicity that both $Z$ and $S$ are affine. Then we want to show that $\varinjlim [\spec A_i,Z]=[\spec K,Z]$. The idea is that given $\phi:\Spec A_n\to Z$, we obtain a map $\Spec K\to Z$ via the composite
\[\xymatrix{
\spec A_n\ar[r]^\phi&Z\\
\spec K\ar[u]
}\]
Now $\phi$ as an element of $\varinjlim [\spec A_i,Z]$ determines and is determined by this composite, as to specify $\phi$ is to specify a finite collection of elements of $A_n$ satisfying some relations, allowing ourselves to stabilise by passing deeper into the direct limit, and this is the same as to give the same type of collection of elements of $K$.
\end{proof}
\begin{defn*}
Locally of finite presentation --- you get finitely presented things, as in definition of locally of finite type.
\end{defn*}
\begin{defn*}
A rational map $X\to Y$ is \emph{dominant} if the image of some (hence all) representative is closed in $Y$.
\end{defn*}
[There's no way to compose rational maps, so we use dominant ones in the following.]
\begin{thm*}
Fix a field $k$. There is a contravariant equivalence of categories, between the category of integral $k$-varieties with DRMs, and the category of finitely generated field extensions of $k$, with $k$-algebra homomorphisms.
\end{thm*}
\begin{proof}
In a dominant rational map, the generic point maps to the generic point! (Otherwise, it couldn't be dominant, as the image would like in the closure of the image of the generic point, which would be closed and proper.) Thus we get a map on local rings at the generic points, i.e.\ a map on function fields.

We should now check that the functor is full, faithful and essentially surjective (everything in the target is isomorphic to something in the image). For full and faithfulness, recall the bijection:
\[\{\text{rational maps $X\to Y$}\}\longleftrightarrow\{\text{$k$-morphisms $\Spec K\to Y$}\}=Y(K)\]
If we restrict to \emph{dominant} rational maps, get a bijection
\begin{alignat*}{2}
\{\text{dominant rational maps $X\to Y$}\}&\longleftrightarrow\{\text{$k$-morphisms $\Spec K\to Y$ mapping $\eta_K\to \eta_Y$}\}\\
&\ \qquad=\Hom_k(\kappa(Y),\kappa(X))
\end{alignat*}
For essential surjectivity, given $K$ a finitely generated field over $k$, let $t_1,\ldots,t_n$ be the generators, and let $A$ be the $k$-subalgebra generated by $t_1,\ldots,t_n$. Use $\Spec A$.
\end{proof}
\begin{defn*}
Integral $k$-varieties are birational \Iff they are isomorphic in the category of dominant rational maps.
\end{defn*}
[The image of a constructible subset is constructible (Chevalley), and a dense constructible subset contains a dense open subset.]
\begin{prop*} TFAE:
\begin{enumerate}\squishlist
\item $X$ and $Y$ are birational.
\item $X$ and $Y$ contain dense open subschemes which admit a $k$-isomorphism between them.
\item $\kappa(X)$ and $\kappa(Y)$ are isomorphic as $k$-algebras.
\end{enumerate}
\end{prop*}
\begin{proof}
That $2\implies 3$ is easy. $3\iff 1$ is done. Need $1\implies 2$. By definition, we have $X_1\subset X$ and $Y_1\subset Y$ and morphisms $f:X_1\to Y$ and $g:Y_1\to X$ such that $fg$ and $gf$ are the identity where defined. How does one find open subsets that match up? It's sneaky.

Let $X_n=\{x\in X\ :\ \text{$x$ can be mapped $n$ times by $f$ and $g$ alternately without getting stuck}\}$ --- this is an $n$-fold inverse image, and is thus open in $X$. Similarly define $Y_n$. Define $X_\infty$ ($Y_\infty$) to be the intersection of the $X_n$ ($Y_n)$. Then $X_\infty=X_2$! So $f:X_\infty\longleftrightarrow Y_\infty:g$ (and can be viewed as maps to $Y$ and $X$ respectively).
\end{proof}
\begin{exmp*}
$xz(x+z)=yw(y+w)$ is rational --- birational to $\PP^2$.
\end{exmp*}
\end{Oct18}
\begin{Oct20}
\section*{Algebraic Geometry --- 20 October}
\begin{exmp*}
$xz(x+z)=yw(y+w)$ is rational --- birational to $\PP^2$.
\end{exmp*}
\begin{proof}
Let $L$ be the line $x=y=0$ in $\PP^3$, and let $L'$ be $w=z=0$. $L,L'\subset X$, and $L\cap L'=\emptyset$. We'll define a rational map $L\times L'\to X$, taking $(p,p')$ to the third intersection of the line through them with $X$. This works a charm, except when $pp'$ lies entirely in $X$ (problems with double points can be resolved).

For the inverse, any $(a:b:c:d)\in\PP^3$ not on $L\cup L'$ lies on a unique line $pp'$ with $p\in L$, $p'\in L'$, defining the rational map inverse to that above. So is is birational to $P^1\times P^1$, which is birational to $\PP^2$.
\end{proof}
\subsubsection*{Projective morphisms}
\begin{defn*}
$\PP^n_A:=\proj A[x_0,\ldots,x_n]\simeq \PP^n_\Z\times A$. For $S$ a scheme, $\PP^n_S:= \PP^n_\Z\times S$.
\end{defn*}
\begin{lem*}
If $(X_i)$ is an open cover of an $S$-scheme $X$, and that $R$ is a local ring over $S$ (i.e.\ it's an $S$-algebra). Then $X(R)=\bigcup X_i(R)$.
\end{lem*}
[This is obviously not true when $R$ is not local.]
\begin{proof}
Let $t\in\spec R$ be the closed point, corresponding to the maximal ideal. Any morphism $f:\spec R\to X$ sends $t$ into some $X_i$. We need to see that all of $\spec R$ maps into $X_i$. Well $f^{-1}X_i$ is open, containing the point $t$, but the only open subset containing the unique maximal ideal is $\spec R$.
\end{proof}
\begin{cor*}
If $R$ is a local ring, then we can describe the $R$-points of projective space:
\[\PP^n_\Z(R)\simeq\{(a_0,\ldots,a_n)\in R^{n+1}\,|\,\text{some $a_i\in R^\times$}\}/R^\times\]
\end{cor*}
[You can make this work for a PID if you demand that the $a_i$ generate the unit ideal, but even for other Dedekind rings, this doesn't work.]
\begin{proof}
$\PP^n(R)=\bigcup D_+(x_i)$, and $D_+(x_i)=\A^n_\Z$, and points of $\A^n_\Z$ are $n$-tuples of elements of $R$. Thus 
\[\PP^n(R)=\bigcup \{a_0,\ldots,a_{i-1},1,a_{i+1},\ldots,a_n\}\qedhere\]
\end{proof}
\begin{cor*}
If $R$ is a valuation ring, and $K$ is its fraction field, then $\PP^n(R)\weakequiv \PP^n(K)$.
\end{cor*}
\begin{proof}
Given $(a_0,\ldots,a_n)\in K^{n+1}\setminus\{0\}$, we can scale up just enough to get all in the valuation ring, but not so far that they all fail to be units. This expression is uniquely determined up to a unit of $R^\times$.
\end{proof}
\begin{defn*}
$X\to S$ is projective \Iff it factors as a composite $X\cofibration \PP^n_S\to S$. That is, the composite of a closed immersion into projective space with the structure map.
\end{defn*}
[The definition in EGA is different. Here, $\PP V=\proj\Sym V^*$. To do this relatively, you use a vector bundle on $S$. These are equivalent under mild hypothesis, for example if $S$ is of finite type over a field.]
\begin{defn*}
$X\to S$ is quasi-projective if it factors as the composite of an open immersion $X\cofibration Y$ and a projective morphism $Y\to S$.
\end{defn*}
\subsubsection*{Proper morphisms}
\begin{defn*}
A morphism $f:X\to Y$ is closed if the image of an closed subset of $X$ is closed in $Y$. This property is not preserved under base extension. A morphism $f:X\to Y$ is universally closed if any base extension thereof is closed.
\end{defn*}
\begin{nonexmp*} The map $\A^1_k\to \spec k$ is not universally closed. Consider:
\[\xymatrix{
\ar[d]\A^2_k\ar[r]&\A^1_k\ar[d]\\
\A^1_k\ar[r]&\spec k
}\]
The hyperbola $xy=1$ maps to a non-closed set.
\end{nonexmp*}
\begin{defn*}
$f:X\to Y$ is proper \Iff it is separated, of finite type, and universally closed.
\end{defn*}
\begin{exmp*}
Closed immersions, compositions of proper maps and base changes of proper maps are all proper. Properness is local on the base.
\end{exmp*}
\begin{thm*}[Valuative criterion for properness]
Suppose $f:X\to S$ is of finite type, where $S$ is noetherian. Then $f$ is proper \Iff for every (discrete)\footnote{It's a pain to go from the VR version to the DVR version.} valuation ring $R$ over $S$, if $K:=\text{frac}(R)$, then the natural restriction map $X(R)\to X(K)$ is bijective.
\end{thm*}
\noindent [This is good both for checking properness, and for extending morphisms!]
\begin{thm*} For a morphism of noetherian schemes, projective $\implies$ proper.
\end{thm*}
\begin{proof}
First, we'll prove that $\PP^n_Z\to\spec\Z$ is proper. By the valuative criterion for properness, this comes from a recent corollary. In general, we have to check this for composites of a closed immersion into $\PP^n_S$ and the structure map $\PP^n_S\to S$. The structure map, being a base extension of $\PP^n_Z\to\spec\Z$, is proper. But closed immersions are proper --- they're locally affine, thus separated, clearly finite type, and universally closed, as closed immersions are closed under base change. As compositions of proper morphisms are proper, we're done.
\end{proof}
\begin{exmp*}
Let $A=k[a,b,c,d]$, and $X=\proj \frac{A[x,y]}{(ax+by,cx+dy)}\subseteq\PP^1_A$. There's a map $f:X\to Y=\spec A=\A^4$. Now $f$ is projective, hence proper, hence universally closed, hence closed. Then $f(X)$ is the closed subset defined by $ad-bc=0$ in $\A^4$. 

In general, you get the closed subset defined by the resultant. \emph{This is really a proof of the existence of the resultant, a polynomial characterising when two homogeneous forms have a common zero --- to see that there's only one polynomial, one counts dimensions, and sees that you get a hypersurface.}\footnote{It's Krull's Hauptidealsatz which shows that a closed codimension one subset of affine space is a hypersurface.}
\end{exmp*}
\begin{thm*}
Suppose that $f:X\to Y$ is a morphism of $k$-varieties, and $X$ is projective (over $k$). Then the image $f(X)$ is closed in $Y$.
\end{thm*}
\begin{proof}
\[\xymatrix{
X\ar[d]_f\ar@/^1cm/[dd]^{\text{proper}}\\%bend me.
Y\ar[d]_{\text{separated}}\\
\spec k
}\]
Thus $f$ is proper. In particular, $f$ is universally closed, and $f(X)$ is closed in $Y$.
\end{proof}
[This is part of elimination thy --- if $f$ is the elimination of a variable, what you get is still defined by equations.....]
\begin{defn*}
A constructible subset is a Boolean combination of closed sets.
\end{defn*}
\begin{thm*}[Chevalley]
Any morphism of varieties $X\to Y$ sends constructible sets to constructible sets. More generally, this holds for any morphism of finite type of noetherian schemes.
\end{thm*}
There's a reinterpretation of this in terms of logic, called elimination of quantifiers, when $k$ is algebraically closed.
\begin{thm*}[elimination of quantifiers]
Any first order formula in the language $(+,\cdot,\text{a symbol for each element of $k$})$ is equivalent to a quantifier-free formula.
\end{thm*}
\begin{exmp*}
$(\exists y)\ xy=1\iff \text{not}(x=0)$.
\end{exmp*}
\noindent Over the reals, you also need to throw in the symbol $\leq$, and call things ``semi-algebraic''.
\end{Oct20}
\begin{Oct27}
\section*{Algebraic Geometry --- 27 October}
Smooth was defined by local obvious smoothness.
\begin{fact*}
If $(A,m)$ is a regular local ring of dimension $n$, and $x_1,\ldots, x_r\in m$, then $A/(x_1,\ldots,x_r)$ is a regular local ring of dimension $n-r$ \Iff the images of $x_1,\ldots,x_r$ in $m/m^2$ are linearly independent.
\end{fact*}
\begin{defn*}
Given $x\in\Spec\frac{ A[t_1,\ldots,t_n]}{(g_{r+1},\ldots,g_n)}\overset{f}{\to} \Spec A$, call $f$ obviously smooth of relative dimension $r$ at $x$ \Iff the matrix $(\partial g_i/\partial t_j(x))\in M_{n-r,n}(k(x))$ has rank $n-r$.
\end{defn*}
\begin{defn*}
Given any morphism of schemes $X\to Y$ and $x\in X$, call $f$ smooth of relative dimension $r$ at $x$ \Iff there are open neighbourhoods mapping into  each other in an obviously smooth way.
\end{defn*}
\begin{defn*}
A morphism is \'etale if it is smooth of relative dimension zero.
\end{defn*}
\noindent For $\C$-varieties, $X\to Y$ is \'etale \Iff the corresponding map of analytic spaces is locally biholomorphic. Finite \'etale maps correspond to finite-sheeted covering spaces in algebraic topology.

\begin{prop*}
For $k$ any field, suppose that $X=\Spec \frac{k[t_1,\ldots,t_n]}{(g_{r+1},\ldots,g_n)}$, and $x\in X(k)$. Then $X$ is obviously smooth (over $\spec k$) of relative dimension $r$ at $x$ \Iff $\calO_{X,x}$ is a regular local ring.
\end{prop*}
\begin{proof}
We may assume that $x=(0,0,\ldots,0)$. $X$ is obviously smooth of relative dimension $r$ at $x$ \Iff $(\partial g_i/\partial t_j(x))\in M_{n-r,n}(k(x))$ has rank $n-r$, \Iff $\overline g_{r+1},\ldots,\overline g_n\in m_{\A^n,x}/m_{\A^n,x}^2=\langle \overline t_1,\ldots,\overline t_n\rangle $ are linearly independent (as these are the rows of the matrix).

Using the above fact, this happens \Iff $\calO_{\A^n,x}/(g_{r+1},\ldots,g_n)$ is a regular local ring of dimension $r$. But this ring is exactly $\calO_{X,x}$.
\end{proof}
Fortunately, anything which is smooth is in fact obviously smooth:
\begin{prop*}
Suppose $x\in U:=\spec\frac{A[t_1,\ldots,t_n]}{(g_{r+1},\ldots,g_n)}\subset X$, and $X\downarrow\spec A$.
Then $X\downarrow \spec A$ is smooth of relative dimension $r$ at $x$ \Iff $U\downarrow\spec A$ is obviously smooth at $x$.
\end{prop*}
\begin{proof}
If it's obviously smooth, then obviously, it's smooth, by definition. For the other direction, let $k=k(x)$, giving a map $\spec k\cofibration X$. If we're given that $X\downarrow \spec A$ is smooth of relative dimension $r$ at $x$, then $U\downarrow\spec A$ is smooth of relative dimension $r$ at $x$. Now as smoothness is preserved by base extension, we have that $U_k\downarrow \spec k$ is smooth at $x$. This implies that $\calO_{U_x,x}$ is a regular local ring of dimension $r$. But now, $U_k\downarrow \spec k$ is obviously smooth of relative dimension $r$, by the above proposition. This implies that $U\downarrow\spec A$ is obviously smooth, as it doesn't make much difference whether we're evaluating at $k$ or what, the matrices are the same.
\end{proof}
\begin{fact*}
Suppose that $X$ is of finite type over any field, of pure dimension $r$. The $X$ is smooth over $\spec k$ \Iff $X$ is geometrically regular. Either of these conditions imply that $X$ is regular. [By regular, we mean that all the local rings are regular local rings. By geometrically regular, we mean regular after extending to an algebraic closure.]

There's a converse if $k$ is perfect --- then $X$ is smooth \Iff it is regular.
\end{fact*}
\begin{fact*}
If you localise a regular local ring at a prime, you get another regular local ring.
\end{fact*}

\begin{defn*}
The word `nonsingular' means either smooth or regular, depending on context.
\end{defn*}
\begin{defn*}
The \emph{singular locus} of a scheme $X$ of pure dimension $r$ over $k$ is
\[X_{\text{sing}}:=\left\{x\in X\,\middle|\,X\text{ is not smooth of relative dimension $r$ at $x$}\right\}\]
\end{defn*}
\begin{prop*}
$X_{\text{sing}}$ is a closed subset of $X$.
\end{prop*}
\begin{proof}
Obvious smoothness is an open condition --- locally it's the common zero locus of the minors of the matrix in the local smoothness condition.
\end{proof}
Note that smooth is a relative notion, while regular is absolute.
\begin{exmp*}
Consider $X\to Y$ given by $\spec k[x,t,y]/(xy-t)\to k[t]$. Then $X$ is regular, as it's isomorphic to $\A^2$ as a $k$-scheme. However, the map is not smooth at $(0,0,0)$. [To check smoothness, we can check that it's obviously smooth. The Jacobian matrix is $[y\ \ x]$. This has maximal rank when $(x,y)\neq(0,0)$ (recall that one evaluates into the residue field in order to discuss rank). Thus this morphism is smooth away from $(0,0,0)$.]
\end{exmp*}
\subsection*{Sheaves of modules}
\begin{defn*} A sheaf of $\calO_X$-modules is a sheaf of abelian groups $\calF$ on $X$ such that for any open subset $U$ of $X$, $\calF(U)$ is an $\calO(U)$-module, compatibly with restriction. A morphism thereof is the obvious.
\end{defn*}
The category $\calO_X\Modules$ of these is an abelian category, which is monoidal and self-enriched. For the tensor product, one needs to sheafify, and a section of the tensor is locally a tensor of sections.

There are the obvious notions of freeness and local freeness. A vector bundle is a locally free sheaf of finite rank. A line bundle (or invertible sheaf) is a locally free sheaf of dimension one.

Recall that given a ring homomorphism $B\from A$, there's an adjunction
\[B\Modules\longleftrightarrow A\Modules.\]
Similarly, given a morphism of schemes $f:X\to Y$, we have
\[f_*:\calO_X\Modules\longleftrightarrow\calO_Y\Modules:f^*.\]
Given $\calF$ an $\calO_X$-module, take $f_*\calF$, with structure given by the map $\calO_Y\to f_*\calO_X$. Given $\calG$ an $\calO_Y$-module, $f^{-1}\scrG$ is an $f^{-1}\calO_Y$-module, so we form
\[f^*\calG:=f^{-1}\calG\otimes_{f^{-1}{\calO_Y}}\calO_X.\]
\end{Oct27}
\begin{Nov1}
\section*{Algebraic Geometry --- 1 November}
Given an affine scheme $\spec A$, there's a functor
\funcdef{A\Modules}{\calO_X\Modules}{M}{\text{$\widetilde M$, where $\widetilde M(D(f))=M_f$}}
This functor is fully faithful, exact, and respects tensor product and arbitrary direct sums. Moreover, given a ring hom $B\from A$ and $M\in A\Modules$ and $N\in B\Modules$. We have a map $f:\spec B\to\spec A$. Then $f_*\widetilde N=\widetilde{_AN}$, and $f^*\widetilde M=\widetilde{M\otimes_AB}$.
\begin{exmp*}
Suppose $A$ is a Dedekind domain (e.g.\ the integral closure of $\Z$ in a finite extension of $\Q$), and $I$ is a fractional ideal (a nonzero f.g.\ $A$-submodule of $\Frac A$). Then $\widetilde I$ is locally free of rank one on $\spec A$. [As a fractional ideal of a DVR is always free.]  Moreover, $\widetilde I$ is free \Iff $I$ is principal.
\end{exmp*}
\begin{defn*}
An $\calO_x$-module $\calF$ is \emph{quasicoherent} \Iff there's an affine open cover $(X_i)$ with $X_i=\spec A_i$ such that $\calF|_{X_i}$ is isomorphic to $\widetilde {M_i}$ for some $A_i$-module $M_i$. $\calF$ is \emph{coherent} if all of the modules involved are finitely generated (we'll only use this term when the underlying scheme is noetherian).
\end{defn*}
\begin{prop*}
The following are equivalent:
\begin{itemise}
\item $\calF$ is quasicoherent
\item this condition on every affine open in $X$.
\item For every $\Spec A_f\subset\spec A\subset X$, the natural map
\[(\calF(\spec A))_f\to\calF(\spec A_f)\]
is an isomorphism.
\end{itemise}
\end{prop*}
\begin{exmp*}
If $X=\spec A$, then there are equivalences of categories:
\[A\Modules\longleftrightarrow\QuasiCoherent_X\ \ \ A\fgModules\longleftrightarrow\Coherent_X\]
For any scheme, $\QuasiCoherent_X$ is an abelian subcategory of $\calO_X\Modules$, closed under taking extensions. So is $\Coherent_X$ if $X$ is noetherian.
\end{exmp*}
\begin{exmp*}
The sheaf of 1-forms on a variety, whose sections are locally of the form $\sum a_i df_i$, with $a_i,f_i$ in the structure sheaf, is quasi-coherent.
\end{exmp*}
\begin{prop*}
Suppose that $f:X\to Y$,  $\calF\in\calO_X\Modules$, and $\calG\in\calO_Y\Modules$.
Then
\begin{itemise}
\item if $\calG\in\QuasiCoherent_Y$ then $f^*\calG\in\QuasiCoherent_X$.
\item if $\calG\in\Coherent_Y$ then $f^*\calG\in\Coherent_X$.
\item Suppose that $X$ is quasi-compact and quasi-separated\footnote{the intersection of two affine opens in $X$ is a finite union of affine opens} (e.g.\ if $X$ is noetherian). If $\calF\in\QuasiCoherent_X$, then $f_*\calF\in\Coherent_Y$.
\item If $X$ is proper, and if $\calF\in\Coherent_X$, then $f_*\calF\in\Coherent_Y$.
\end{itemise}
\end{prop*}
\begin{fact*}
It's hard to come up with examples of schemes which aren't quasi-separated. An example is the bug-eyed infinite-dimensional affine space.
\end{fact*}
\subsection*{Closed subschemes}
Recall that closed subschemes of $\spec A$ correspond to ideals of $A$. Given an ideal, one takes $\spec A/I$, and given a closed subscheme $Z\cofibration \spec A$, take $I=\ker\{\Gamma(\calO_{\spec A})\to\Gamma(\calO_Z)\}$.

We seek to generalise this to a bijection between closed subschemes of $X$ and quasi-coherent sheaves of ideals of $\calO_X$. The bijection is just about the same:
\[Z\mapsto\calI_Z:=\ker\{\calO_X\to i_*\calO_Z\}.\]
That is, the ideal sheaf $\calI_Z$ of $Z$ in $X$ is the ideal of functions which vanish upon restriction to $\Z$. For this inverse to this map, we send a quasi-coherent sheaf of ideals $\calI$ to $\SPEC\,\calO_X/\calI$. [Here, $\calO_x/\calI$ is a quasiocoherent sheaf ($\calF$) of $\calO_X$-algebras. Over each affine open $\spec A\subset X$, $\calF(\spec A)$ is an $A$-algebra, so that $\spec(\calF(\spec A))$ is a scheme over $\spec A$, and these can be glued to form $\SPEC \calF$.]
\begin{defn*}
The \emph{scheme-theoretic image}\footnote{The scheme-theoretic image is like `the closure of the image'.} of a morphism of schemes $f:X\to Y$ is the smallest closed subscheme $Z\cofibration Y$ through which $f$ factors. This corresponds to the largest quasi-coherent sheaf $\calI$ of ideals contained in $\calK=\ker\{\calO_Y\to f_*\calO_X\}$.
\end{defn*}
\begin{fact*}
If $f$ is quasi-compact, then:
\begin{itemise}
\item $\scrK$ is quasi-coherent, so that $\calI=\calK$;
\item the formation of $\calI$ and $Z$ is local on $Y$. That is, for $U$ open in $Y$, $\im(f^{-1}U\to U)=\Z\cap U$.
\item The underlying topological space of $Z$ is the closure of $f(X)$.
\end{itemise}
\end{fact*}
\subsection*{Quasicoherent sheaves on $\proj S$}
Given a graded ring $S=\bigoplus _{n\geq 0}S_n$ we can form a scheme $X=\Proj S$. Given a graded $S$-module $M=\bigoplus _{n\in \Z}M_n$, we obtain a quasi-coherent sheaf \reflectbox{$\widetilde {\reflectbox{$M$}}$} on $\proj S$ characterised by $\widetilde M(D_+(f)):=M_{(f)}$ (the degree zero localisation). This is quasi-coherent, as $\widetilde M|_{D_+(f)}\simeq \widetilde{M_{(f)}}$ on $\spec S_{(f)}$. In particular, $\widetilde M$ is coherent if $M$ is finitely generated.

Given a graded $S$-module $M$, we can \emph{twist} it, defining $M(n)$ to be the graded $S$-module with $M(n)_i=M_{n+i}$. The key example is $\calO_X(n):=\widetilde {S(n)}$. From now on, we'll assume that:
\[\text{ $S$ is generated by $S_1$ as an $S_0$-algebra,}\]
e.g.\ $S$ is a quotient of a polynomial ring in dimension one.
\begin{prop*}
$\calO_X(n)$ is a line bundle.
\end{prop*}
\begin{proof}
$X$ is covered by the $D_+(f)$ for $f\in S_1$. Fix $f\in S_1$. Then $\calO_X(n)|_{D_+(F)}\simeq \widetilde{S(n)_{(f)}}$, and it's enough to see that this module is a free $S_{(f)}$-module of rank one. However, there's an obvious $S_{(f)}$-module isomorphism between $S(n)_{(f)}$ and $S_{(f)}$ given by multiplication by $f^{\pm n}$.
\end{proof}
\begin{prop}
$\widetilde{M\otimes_SN}=\widetilde M\otimes_X\widetilde N$.
\end{prop}
\begin{proof}
On $D_+(f)$ for $f\in S_1$, we have $(M\otimes_S N)_{(f)}\simeq M_{(f)}\otimes_{S_{(f)}}N_{(f)}$.
\end{proof}
\begin{cor*}
$\calO_X(m)\otimes\calO_X(n)=\calO_X(m+n)$.
\end{cor*}
\end{Nov1}
\begin{Nov3}
\section*{Algebraic Geometry --- 3 November}
\begin{claim}
Take $S=k[x_0,\ldots,x_n]$, so that $X=\PP^r$. Then $\Gamma(\PP^r,\calO(n))=S_n$, the module of homogeneous polynomials of degree $n$.
\begin{proof}
$\Gamma(D_+(x_i),\calO(n))=S(n)_{(x_i)}$, which is the $k$-span of the monomials $\prod x_j^{a_j}$ where $\sum a_j=n$ and $a_j\geq0$ for $j\neq i$. The result follows.
\end{proof}
\end{claim}
\begin{cor*}
$\bigoplus_{n\in\Z}\Gamma(\PP^r,\calO(n))$ recovers $S$ as a graded ring.
\end{cor*}
\begin{defn*}
For $\calF$ on $X:=\proj S$, define $\Gamma_*(\calF):=\bigoplus_{n\in\Z}\Gamma(X,\calF(n))$, a graded $S$-module.
\end{defn*}
Then there are functors
\[\widetilde{\DASH}:\text{graded S-modules}\longleftrightarrow\text{quasicoherent $\calO_X$-modules}:\Gamma_*(\DASH)\]
\begin{prop*}
$\widetilde{\Gamma_*(\calF)}\simeq\calF$, but $M\to \Gamma_*(\widetilde M)$ need not be an isomorphism. [If $M$ is a sheaf of ideals, then $\Gamma_*(\widetilde M)$ is its saturation.]
\end{prop*}
Recall that $\PP^n_Y$ is equipped with a projection to $\PP^n_Z$:
\[\PP^n_Y:=\PP^n_Z\times Y\overset{\pi}{\to}\PP^n_Z.\]
We define $\calO(1)$ on $\PP^n_Y$ to be $\pi^*(\calO(1)\text{ on $\PP^n_\Z$})$.
\begin{defn*}
Given an immersion $i$, (a composite $X\overset{open}{\cofibration} U\overset{closed}{\cofibration} \PP^n_Y$), we define $\calO_{X}(1):=i^*\calO(1)$. Any line bundle on $X$ arising in this way is called \textit{very ample relative to $Y$}.
\end{defn*}
\noindent [Somehow, understanding all of the very ample line bundles on $X$ is tantamount to understanding all of the embeddings of $X$ in projective space.]
\begin{exmp*}
Recall the 2-uple embedding of $\PP^2$, a.k.a.\ the Veronese embedding, a closed immersion:
\[\PP^2\overset{i}{\cofibration} \PP^5\text{\qquad given by\qquad}(x:y:z:\mapsto(x^2:y^2:z^2:xy:xz:yz).\]
This satisfies $i^*\calO_{\PP^5}(1)=\calO_{\PP^2}(2)$. This shows that $\calO_{\PP^2}(@)$ is very ample relative to $k$.
\end{exmp*}
\begin{defn*}
Suppose that $X$ is a scheme, and $\calF$ is an $\calO_X$-module> Suppose that we are given some global sections $s_i\in\Gamma(X,\calF)$. We say that the $s_i$ \emph{generate} $\calF$ \Iff at each point $x\in X$, the images of the $s_i$ generate the stalk $\calF_{x,X}$ as an $\calO_{x,X}$-module.

This is equivalent to the statement that the  $\calO_X$-module homomorphism $\bigoplus_i\calO_X\to\calF$ corresponding to these sections is surjective.

We say that $\calF$ is \emph{generated by global sections} if such a collection of sections exists.
\end{defn*}
\begin{exmp*}
$x_1,\ldots,x_n\in\Gamma(\PP^n,\calO(1))$ generate $\calO(1)$. $\calO(-1)$ cannot be generated by global sections.
\end{exmp*}
\noindent In the special case that $\calF$ is very ample, generating global sections correspond to the coordinates of an embedding, for this reason.
\begin{exmp*}
Suppose that $r\geq1$. Then the sheaf $\calO(d)$ on $\PP^r$ is g.b.g.s.\ \Iff $d\geq0$. It is vey ample \Iff $d>0$. Note that we have the $d$-uple embedding, and if $d\leq0$, there aren't enough global sections for it to be very ample.
\end{exmp*}
\begin{exmp*}
Let $X:=\PP^1\times\PP^1$. This has two projections to $\PP^1$. For any $m,n\in\Z$, we form $\calO(m,n):=\pi_1^*\calO(m)\otimes\pi_2^*\calO(n)$, a line bundle. Now
\[\Gamma(\PP^1\times\PP^1,\calO(m,n))=\{\text{bihomogeneous polynomials of degree $m,n$.}\}.\]
This has dimension $(m+1)(n+1)$ over $k$.  $\calO(m,n)$ is g.b.g.s.\ \Iff $m,n\geq0$. It is very ample \Iff $m,n\geq1$.
\end{exmp*}
\begin{exmp*}
Under the Segre embedding $\PP^1\times\PP^1\cofibration \PP^3$, we have $\phi^*\calO_{\PP^3}(1)=\calO(1,1)$, and we can get the other very ample ones by mixing in some $m$-uple and $n$-uple embeddings.
\end{exmp*}
\begin{thm*}[Serre]
Suppose $A$ is a noethrian ring, and we have a closed immersion $X\cofibration \PP^n_A$, so that $X$ is projective over $A$, and we have a very ample sheaf $\calO(1)$ on $X$. Suppose that $\calF$ is a coherent $\calO_X$-module. Then for $n\gg1$ (depending on $\calF$), then $\calF(n)$ is g.b.g.s.

Another way to say this is that $\calO(1)$ is \textbf{ample}.
\end{thm*}
\begin{proof}
Over the affine patches, you choose some generators. All this is finite. These have some denominators, which can be cleared by twisting!
\end{proof}
\begin{defn*}
A line bundle $\calL$ on (any scheme) $X$ is \emph{ample} \Iff for any coherent scheme $\calF$, for $n\gg0$, $\calF\otimes\calL^{\otimes n}$ is g.b.g.s.\ for $n\gg1$. 
\end{defn*}
\begin{thm*}[II.7.6]
If $X$ is of finite type over a noetherian ring $A$, $\calF$ is ample \Iff for some $n>0$, $\calL^{\otimes n}$ is very ample over $A$.
\end{thm*}
\begin{cor*}
Suppose that $A$ is a noetherian ring and $X\cofibration \PP^r_A$ is a closed embedding, and that $\calF$ is an $\calO_X$-module. Then $\calF$ is  coherent \Iff there is a surjection
\[\bigoplus_{i=1}^s\calO(n_i)\fibration\calF.\]
\end{cor*}
\begin{proof}
By the theorem we have a surjection $\bigoplus \calO_X\fibration \calF(n)$. Untwisting is exact!
\end{proof}
Recall that if $X$ is a projective variety over an algebraically closed field, then $\Gamma(X,\calO_X)=k$. This `algebraic Liouville theorem' generalises.
\begin{prop*}
Suppose that $X$ is any field, $X$ is a projective scheme over $k$, and $\calF$ is a coherent $\calO_X$-module. Then $\dim_k\Gamma(X,\calF)$ is always finite.
\end{prop*}
\begin{exmp*}
$\dim_k\Gamma(\PP^n_K,\calO(d))={n+d\choose d}$.
\end{exmp*}
\begin{exmp*}
$\dim_k(\Gamma(\A^n_k,\calO)=\infty$.
\end{exmp*}
An even wider generalisation, in which we view $f_*$ as a relative version of global sections, is:
\begin{prop*}[Grothendieck]
Suppose that $Y$ is a noetherian scheme, $f:X\to Y$ is a proper morphism, and $\calF$ is a coherent $\calO_X$-module. Then $f_*\calF$ is a coherent $\calO_Y$-module.
\end{prop*}
\end{Nov3}

\end{document}
























