% !TEX root = z_output/Characteristic_Classes.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% 80 characters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
\input{../macros.tex}



\title{Characteristic Classes}
\author{John W.\ Milnor, James D.\ Stasheff}
\date{}

\begin{document}
\maketitle

\section{Smooth Manifolds}
\begin{itemise}
\item `$D$', the tangent space, is an endofunctor on the category of smooth manifolds, doubling dimension.
\item If $f:M\to \R$ is a smooth function, $Df_x:DM_x\to D\R_{f(x)}=\R$ is an element of $\Hom(DM_x,\R)$, the cotangent space. $Df_x$ is more commonly written $df_x$.
\end{itemise}
\section{Vector Bundles}
\begin{itemise}
\item Discusses continuous and smooth vector bundles.
\item If $M$ is a smooth manifold with $\tau_M$ trivial, say that $M$ is parallelisable.
\item Write $\gamma_n^1$ for the canonical line bundle on $\RP^n$. Then
\begin{itemize}\squishlist
\item $\gamma_n^1$ has non non-vanishing section (pull $\gamma_n^1$ back to $S^n$ to get the normal bundle; consider a path between antipodal points).
\item $\gamma_1^1$ is the open M\"obius band.
\end{itemize}
\end{itemise}
\subsection*{Euclidean Vector Bundles}
\begin{itemise}
\item A function $\mu:V\to \R$, with $V$ a finite-dimensional real vector space, if \emph{quadratic} if $\mu(v)=\sum l_i(v)l_i'(v)$ for some linear $l_i$ and $l'_i$. We obtain from such a symmetric bilinear product setting $v\cdot w=(\mu(v+w)-\mu(v)-\mu(w))/2$.
\begin{defn*}
A \emph{Euclidean vector space} is one with a positive definite quadratic form $\mu:V\to\R$ (i.e.\ the corresponding bilinear product is positive definite).
\end{defn*}
\begin{defn*}
A \emph{Euclidean vector bundle} is a real vector bundle with a function  $\mu:E(\xi)\to\R$ which restricts to a positive definite quadratic form on each fibre.
\end{defn*}
\begin{defn*}
A \emph{Riemannian manifold} is a manifold equipped with a Euclidean vector bundle structure on the tangent bundle (called a Riemannian metric).
\end{defn*}
\item A Euclidean metric exists on any vector bundle over a paracompact base.
\end{itemise}
\section{Constructing New Vector Bundles Out of Old}
\begin{itemise}
\item A \emph{bundle map} $\eta\to\xi$ is a continuous/smooth fibre-preserving map $g$ on total spaces which is a fibrewise linear isomorphism. It induces a map $\overline g$ on base spaces, and $\eta=\overline g^*(\xi)$.
\item \textbf{Corollary 3.4.} When $M$ is a smooth submanifold of a Riemannian manifold $N$, the normal bundle $\nu$ is defined, and $\tau_M\oplus\nu=\tau_N|_M$.
\item \textbf{Definition.} A map $f:M\to N$ of smooth manifolds is an \emph{immersion} when each $Df_x$ is injective.
\item \textbf{Corollary 3.5.} For any immersion $f:M\to N$ into a Riemannian manifold $N$, the normal bundle $\nu_f$ is defined, and $\tau_M\oplus\nu_f=f^*\tau_N$.
\item Continuous functors on vector spaces induce operations on vector bundles.
\item If $\xi$ and $\eta$ are bundles over $B$, $f\in\Gamma\Hom(\xi,\eta)$, and if the rank of $f$ on each fibre is locally constant, there there are kernel and cokernel bundles on $B$.
\item If $\xi$ admits a Euclidean metric, it is self dual.
\item A real line bundle posesses a metric \Iff it has order at most two in the Picard group.
\item Over a Tychonoff space $B$, vector bundles correspond to finitely generated projective $\R(B)$-modules (and trivial corresponds to free), by mapping a bundle to its global sections.
\end{itemise}
\section{Stiefel-Whitney Classes}
\begin{itemise}
\item Assume that they exist for now, satisfying ($\Z_2$ coeffs):
\begin{enumerate}\squishlist
\item $w_i(\xi)\in H^i(B(\xi))$ satisfy $w_0(\xi)=1$, $w_i(\xi)=0$ for $i>\dim\xi$;
\item naturality;
\item the Whitney product theorem: $w(\xi\oplus\eta)=w(\xi)w(\eta)$;
\item $w_1(\gamma_1^1)\in H^1(\RP^1)$ is nonzero.
\end{enumerate}
\item \textbf{Proposition 2.} If $\varepsilon$ is trivial, then $w(\eta)=1$. \begin{proof} $w(\varepsilon)$ is pulled back from $H^*(*)$.
\end{proof}
\item \textbf{Proposition 4.} If $\xi$ is an $n$-bundle with Euclidean metric, and $\xi$ admits $k$ linearly independent sections, then the top $k$ SW classes of $\xi$ vanish.
\begin{proof} Using the metric, split off the $k$ sections.
\end{proof}
\item The total SW class $w(\xi)$ lives in $H^\Pi(B)$, the ring of formal infinite series in $H^*(B)$. The set of series with leading coefficient one forms a group under multiplication. Inverses can be computed inductively, or by power series inversion. In fact: 
\[\overline w:=w^{-1}=\sum\frac{(i_1+\cdots +i_k)!}{i_1!\cdots i_k!}w_1^{i_1}\cdots w_k^{i_k}.\]
\item \textbf{Whitney Duality Theorem.} If $M\subset \R^n$ is a submanifold, then $w_i(\nu)=\overline w_i(\tau_M)$.\\
\textbf{Example 1.} $w(\tau_{S^n})=1$. [As $\nu$ is trivial. Alternatively, as $\tau_{S^n}=\pi^*\tau_{\RP^n}$, and the map $\pi^*$ on cohomology is zero (using the product structure).]\\
\textbf{Example 2.} $w(\gamma_n^1)=1+a$ where $H^*(\RP^n;\Z_2)=\Z_2[a]/a^{n+1}$. [$\RP^1\to\RP^n$ gives a bundle map.]\\
\textbf{Example 3.} Define $\gamma^\perp=\varepsilon^{n+1}-\gamma_n^1$. Then $w(\gamma^\perp)=1+a+\cdots+a^n$. In particular, none of the $w_i$ are redundant.\\
\textbf{Example 4.} $w(\tau_{\RP_n})=(1+a)^n$. [$\tau+\varepsilon=\Hom(\gamma^1_n,\gamma^\perp\oplus\gamma_n^1)=(\gamma_1^n)^{n+1}$.]\\
\textbf{Corollary 4.6.} $w(\RP^n)=1$ \Iff $n+1=2^i$.\\
\textbf{Theorem 4.7.} Suppose $\R^n$ can be made a real division algebra. Then $\RP^{n-1}$ is parallelisable. Thus $n=2^i$.
\item \textbf{Immersions.} If $M^n\to\R^{n+k}$ is an immersion, then $w_i(\nu)=\overline{w}_i(M)=0$ for $i>k$.\\
\textbf{Example.} $\overline w(\RP^9)=1+a^2+a^4+a^6$, so $\RP^9$ cannot be immersed in $\R^{14}$.\\
\textbf{Example.} If $n$ is a power of $2$, $w(\RP^n)=(1+a)(1+a^n)=(1+a+\cdots+a^{n-1})^{-1}$. Thus $\RP^n$ needs at least $(2n-1)$ dimensions, which always suffice for a smooth compact $n$-manifold.
\end{itemise}
\end{document}















