% !TEX root = z_output/_Conversations.tex
%%% BEGIN NEW ENTRY FORMAT
%
%\pagebreak
%\CONVERSATION{What?}{Who?}{?/1/2012}
%%% END NEW ENTRY FORMAT

%%%%%%%%%%%%%%%%%%%%%%%%%%% 80 characters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\input{../macros.tex}

\includeversion{don't show}

%\CONVERSATION{Title}{person}{date}
\newcommand{\CONVERSATION}[3]{
\subsection*{#1}
\begin{flushright}
{\small #2 --- #3}
\end{flushright}
}

\begin{document}
\begin{don't show}
\CONVERSATION{$E_{\infty}$-operads and algebras; localising a ring spectrum at a homotopy class}{Haynes}{8/11/2011}
The space of long knots in an $E_2$-algebra.

For each $n\geq0$, let $\scrL(n)=\textup{Isom}((\R^\infty)^n,\R^\infty)$. This is an $E_\infty$-operad. In has an action on (a suitable construction of) $BO$.

The connective $K$-theory spectrum is the $\Omega$-spectrum whose spaces are (starting at level zero)
\begin{alignat*}{2}
(\Z\times BU)\langle 3\rangle&=BSU%&\qquad&\text{()}
\\U\langle 2\rangle&=SU%&\qquad&\text{()}
\\(\Z\times BU)\langle 1\rangle&=BU%&\qquad&\text{()}
\\U\langle 0\rangle&=U%&\qquad&\text{()}
\\(\Z\times BU)\langle -1\rangle&=\Z\times BU%&\qquad&\text{()}
\end{alignat*}
It has homotopy polynomial in the 2-dimensional generator. In fact, if we invert the two-dimensional generator, we recover the $K$-theory spectrum.

On way to invert a homotopy element $f:S^n\to E$ is to form the composite $\Sigma^nE\overset{f\sprod1}{\to}E\sprod E\to E$, and use it to form the colimit of:
\[E\to\Sigma^{-n}E\to\Sigma^{-2n}E\to\Sigma^{-3n}E\to\cdots.\]

\pagebreak
\CONVERSATION{Winter Reading; medium-term project}{Haynes}{29/11/2011}
Over winter:
\begin{itemise}
\item Read parts of Ravanel's book:
\begin{enumerate}\squishlist
\item The Adams spectral sequence;
\item The $\Lambda$-algebra;
\item The appendix on formal groups.
\end{enumerate}
\item A project:
\begin{itemize}\squishlist
\item For $X$ a spectrum, $p$ an odd prime, the we have a spectral sequence:
\[\Ext^{s,t}_\calA(H^*(X),\F_p)\implies\pi_*(X^\wedge_p)\]
from the $\Ext$ groups over the mod $p$ Steenrod algebra to the homotopy groups of the $p$-completion of $X$.
\item Suppose that $X$ is connective. Then
\begin{thm*}
There is a line of some slope on the SS, above which we can calculate exactly what the spectral sequence does.
\end{thm*}
\item Note that we normally draw the ASS so that the vertical coordinate measures $s$, while the horizontal measures $t-s$. Thus, the vertical coordinate reflects the filtration \emph{and} topological degrees.
\item Every spectrum is a module over the sphere spectrum $\mathbb{S}$. With $X=\mathbb{S}$, there is an element $q_0$ in some position on the $y$-axis of the $E_2$ page. Presumably this element detects the first nontrivial homotopy in the $p$-localised sphere.

Well, this element acts on any adams spectral sequence. In particular, there is, for general $X$, a localisation map:
\[\Ext^{s,t}_\calA(H^*(X),\F_p)\to q_0^{-1}\Ext^{s,t}_\calA(H^*(X),\F_p).\]
This map is an isomorphism above the line. Moreover, we have an equality:
\[q_0^{-1}\Ext^{s,t}_\calA(H^*(X),\F_p)\cong H(H^*(X,\F_p);\beta)\otimes\F_p[q_0^{\pm1}],\]
so that above the line, the spectral sequence is determined by the Bockstein spectral sequence for $X$, which we can calculate!
\item There's a conjecture related to all this on Haynes' website.
\end{itemize}
\end{itemise}

\pagebreak
\CONVERSATION{The Kan loop group, a theorem of Dold}{Haynes}{6/12/2011}
Kan associates functorially to each reduced\footnote{A simplicial set is reduced if it has only one 0-simplex.} simplicial set a simplicial abelian group, which is free in each degree:
\[G:s\mathsf{Set^{\textup{red}}}\to s(\mathsf{FreeGp})\]
such that the homotopy type of $G(X)$ is that of $\Omega X$ (in some appropriate sense). This gives a strictification of the loops functor.

Given a group, one can take the filtration arising from the lower central series to obtain a graded Lie algebra. If the group was free, we obtain a free graded Lie algebra on the generators.

If we instead take maximal $\F_p$-vector space quotients, we get a filtration whose associated graded is a free \emph{restricted} Lie algebra, yielding
\[L:\mathsf{Gp}\to\mathsf{GrLieAlg}^{\textup{rest}}\]


Now if we take a reduced simplicial set $X$, the simplicial group $GX$ has a lower central series in each degree, and so we obtain a simplicial graded free restricted Lie algebra.
\[L_*G:s\mathsf{Set^{\textup{red}}}\to s(\mathsf{GrLieAlg}^{\textup{rest}}) \]

Some missing details here, pointing out that the generators of the graded Lie algebra are the elements in the first filtered degree --- the elements of the maximal $\F_p$-vector space quotient of the group $GX$.

The following is a theorem of \textbf{Dold}: Suppose that $H:\mathsf{Vect}_\F\to\mathsf{Vect}_\F$ is a functor. Then there is a functor $\calH$ giving a commuting diagram:
\[\xymatrix{
s\mathsf{Vect}_{\F}\ar[r]^{H_*}\ar[d]^{\pi_*}&
s\mathsf{Vect}_{\F}\ar[d]^{\pi_*}\\
\mathsf{GrVect}_{\F}\ar@{-->}[r]^{\calH}&\mathsf{GrVect}_{\F}
}\]
That is, the homotopy of $H_*X$ is in fact a functor in the homotopy of $X$.

All this could be stitched together to give a spectral sequence going from the homology of $X$ to the homotopy. See Curtis, ``Simplicial homotopy theory'' (Advances in Math.\ 6 1971 107).

\textbf{Problem}: Kan and Bousfield have another spectral sequence with this source and target, and the relationship between these is not fully understood.

\pagebreak
\CONVERSATION{The Adams Spectral sequence}{Haynes}{12/1/2012}
\newcommand{\Pproj}{\calP_{\textup{proj}}}
\newcommand{\Pseq}{\calP_{\textup{seq}}}
Suppose that $\calA$ is a triangulated (an in particular, additive) category. Call a pair of composable maps $A'\to A\to A''$ a \emph{sequence} if it has composite zero.

We're going to give a definition of ``relative homological algebra''. This will be relative to a pair $(\Pproj,\Pseq)$, where $\Pproj$ is a class of objects called `relative projectives', and $\Pseq$ is a class of sequences called `relative sequences', satisfying:
\begin{itemize}\squishlist
\item A sequence $A'\to A\to A''$ is a relative sequence \Iff the following is exact for every $P\in\Pproj$:
\[\calA(P,A')\to\calA(P,A)\to\calA(P,A'')\]
\item An object $P$ is a relative projective \Iff for all relative sequences $A'\to A\to A''$, the above is exact.
\item There are enough projectives, in the sense that for every object $X$, we can find a relative projective $P$ and a relative sequence $P\to X\to0$.
\end{itemize}
Such a structure is enough to give a model category structure on the category of positively graded chain complexes on $\calA$.

\begin{exmp*}
Given a ring homomorphism $f:A\to B$, we can give such a structure on the category of $B$-modules. Say that a $B$-module $P$ is $f$-projective \Iff it's a retract of a module $B\otimes_AQ$.\footnote{Note that if $P$ is $f$-projective, then $P$ is in fact a retract of $B\otimes_AP|_A$.} The relative sequences are then determined as those sequences $M'\to M\to M''$ which are split exact when restricted to $A$.
\end{exmp*}
\begin{exmp*}
Hochschild homology is a relative $\Tor$ group.
\end{exmp*}

Now, suppose that $\calA$ is a triangulated category with a \textbf{stable} injective class. That is, with all the same structure dualised, and such that an object is injective \Iff all of its suspensions are injective.

\begin{shaded}
I don't know if we're going with projective or injective right now.
\end{shaded}

Let $\calA=\ho(\scrS)$, and let $R$ be a ring spectrum (i.e.\ a tensor monoid) such that $\pi_{*}(R)$ is commutative. 
\begin{itemize}\squishlist
\item We'll say that $P\in\calA$ is $R$-projective \Iff it's a retract of some spectrum of the form $R\sprod X$. That is, \Iff the map $P\to R\sprod P$ has a section.
\item We'll say that $X'\to X\to X''$ is an $R$-sequence if it is split exact (what does this mean?????) after smashing with $R$. At very least we want each three term sequence $\pi_{n}(R\sprod X')\to\pi_{n}(R\sprod X)\to\pi_{n}(R\sprod X'')$ to be exact.\footnote{For an example, suppose that $R=HA$, the Eilenberg-MacLane spactrum associated with an abelian group $A$. Then $R\sprod X$ is a new spectrum whose homotopy is the homology of $X$.}
\end{itemize}
Now take an injective resolution
\[\xymatrix@R=.5cm@C=.5cm@!C{
X\ar[dr]&%r1c1
&%r1c2
&%r1c3
&%r1c4
&%r1c5
&%r1c6
&%r1c7
\\%r1c8
&%r2c1
I^0\ar[rr]&%r2c2
&%r2c3
I^1\ar[rr]&%r2c4
&%r2c5
I^2\ar[rr]&%r2c6
&%r2c7
\cdots%r2c8
}\]
and complete it to an $R$-Adams resolution:
\[\xymatrix@R=.5cm@C=.5cm@!C{
X\ar[dr]&%r1c1
&%r1c2
X^1\ar@{~>}[ll]\ar[dr]&%r1c3
&%r1c4
X^2\ar@{~>}[ll]\ar@{..>}[dr]&%r1c5
&%r1c6
&%r1c7
\\%r1c8
&%r2c1
\ar[ur]I^0\ar[rr]&%r2c2
&%r2c3
\ar[ur]I^1\ar[rr]&%r2c4
&%r2c5
I^2\ar[rr]&%r2c6
&%r2c7
\cdots%r2c8
}\]
Note that at this stage, we can form the dotted arrow, as the composite $X^1\to I^2$ is null.

Now the fibre in a triangulated category is not canonically defined, instead it is only defined up to non-canonical isomorphism. However, any two of these resolutions are isomorphic, and the failure of the isomorphism to be canonical dies by the $E_2$ page of the spectral sequence.


Now \textbf{assume} that $R_*R$ is flat over $R_*:=\pi_{*}(R)$. This happens when $R$ is any of $H\F$ ($\F$ any field), $K$ and $\textup{MU}$, but not for $H\Z$. With this assumption, we obtain co-operations on the $R$ homology of any spectrum
\[R_*(X)\to R_*(R)\otimes_{R_*}R_*(X).\]
Putting $X=R$, we obtain the diagonal map making $(R_*,R_*R)$ a Hopf algebroid.

Now by our flatness assumption, the category of $R_*R$-comodules is abelian. We define:
\begin{itemize}\squishlist
\item the relative injectives to be the retracts of extended modules $R_*R\otimes_{R_*}(?)$
\item the relative sequences to be... the same as last time?
\end{itemize}
Via these definitions, we have relative homological algebra.

Now we have a Hurewicz map 
\[\pi_{*}(X)\to\Hom_{R_*R}(R_*,R_*(X))\]
 obtained as follows. Given $f:\mathbb{S}\to \Sigma^{-n}X$ and $g:\mathbb{S}\to \Sigma^{-m}R$, we produce:
\[
\xymatrix@1{
\mathbb{S}\ar@{=}[r]&%r1c1
\mathbb{S}\sprod\mathbb{S}\ar[r]^-{f\sprod g}&%r1c2
\Sigma^{-n}X\sprod \Sigma^{-m}R\ar@{=}[r]&%r1c3
\Sigma^{-n-m}X\sprod R
}\]
Moreover, if $X$ is $R$-injective, this is an isomorphism. So, if we apply homotopy to obtain an exact couple:
\[\xymatrix@R=.5cm@C=.5cm@!C{
\pi_*X\ar[dr]&%r1c1
&%r1c2
\pi_*X^1\ar@{~>}[ll]\ar[dr]&%r1c3
&%r1c4
\pi_*X^2\ar@{~>}[ll]\ar[dr]&%r1c5
&%r1c6
&%r1c7
\\%r1c8
&%r2c1
\ar[ur]\pi_*I^0\ar[rr]&%r2c2
&%r2c3
\ar[ur]\pi_*I^1\ar[rr]&%r2c4
&%r2c5
\pi_*I^2\ar[rr]&%r2c6
&%r2c7
\cdots%r2c8
}\]
we find that the bottom row can be replaced with
\[\Hom_{R_*R}(R_*,R_*(I^0))\to\Hom_{R_*R}(R_*,R_*(I^1))\to\Hom_{R_*R}(R_*,R_*(I^2))\to\cdots.\]
So as long as $R_*$ maps resolutions of spectra to resolutions of comodules, we will be able to identify the  $E_2$ page with some derived functor (Ext, right? Or is this Cotor or something!?)

\begin{rmk*}
Convergence is trivial when $R=MU$ and $X$ is connective. In this case, we can make the map $X\to I^0$ an isomorphism on the bottom homotopy group, and thus, push the connectivity of the $X^i$ higher and higher.
\end{rmk*}

\end{don't show}
\pagebreak
\CONVERSATION{Orientations of Thom Spectra}{Haynes}{4/4/2012}
\paragraph*{Orientations of vector bundles via cohomology:}
What does it mean to orient a closed $n$-manifold $M^n$? We often think about it in terms of cohomology, giving a certain class in $H^n(M)$.

Instead, one might think about embedding $M^n\cofibration \R^{n+k}$. Then an orientation of the normal bundle is the same as an orientation of the tangent bundle (once one chooses some conventions). We also like to think about the normal bundle as it brings us closer to the Pontrjagin-Thom story.

To orient the normal bundle is to give a Thom class $\Thom(\nu)\to K(Z,k)$ --- a class whose pullbacks to $\Thom(\nu_x)$ are generators of $H^k(S^k)$ for each $x\in M$.

For another perspective, one can view orientations of $\nu$ as factorisations $\overline{\nu}$
\[
\xymatrix@R=4mm{
&%r1c1
BSO(k)
\ar[d]^-{\textup{2 to 1}}
\\%r1c2
M
\ar@{..>}[ur]^-{\overline{\nu}}
\ar[r]^-{\nu}
&%r2c1
BO(k)%r2c2
}\]
From $\overline{\nu}$ we have a map on thom spaces (left arrow), and on $MSO(k)$ we have the universal Thom class in dimension $k$ (right arrow):
\[\xymatrix@R=4mm{
\Thom(\nu)
\ar[r]
&%r1c1
MSO(k)
\ar[r]^-{U}
&%r1c2
K(\Z,k)\\%r1c3
\makebox[0cm][c]{induces:}&%r2c1
MSO
\ar[r]
&%r2c2
H\Z%r2c3
}\]
Now $MSO$ is a ring spectrum%footnote:
\footnote{Via maps $MSO(k)\wedge MSO(k')\to MSO(k+k')$ induced by the bundle map $ESO(k)\times ESO(k')\to ESO(k+k')$ that classifies the external direct sum of the two universal bundles.}, and this induced map on spectra is a ring map%footnote:
\footnote{Presumably as we have a commuting diagram
\[\xymatrix@R=4mm{
MSO(k)\wedge MSO(k')
\ar[r]
\ar[d]
&%r1c1
MSO(k+k')
\ar[d]
\\%r1c2
K(\Z,k)\wedge K(\Z,k')
\ar[r]
&%r2c1
K(\Z,k+k')%r2c2
}\] as the orientation class on $MSO(k+k')$ restricts to the smash product of the orientation classes on the factors.}.
\paragraph*{The Thom isomorphism:} 
[There were some comments about how to produce genuine bundles on skeleta given a map from a space to $BO$, or was it $BGL_1\mathbb{S}$...]

The Thom isomorphism, when $\nu$ is oriented, is
\[\widetilde{H}_{*}(\Thom(\nu))\cong\widetilde{H}_{*}(\Sigma^kM_+).\]
In fact, there is an equivalence of spectra: \rednote{(what kind of equivalence do we mean here)}
\[\Thom(\nu)\wedge H\Z\simeq \Sigma^k M_+\wedge H\Z.\]
\begin{proof}
All that remains is to produce a map implementing the Thom isomorphism. Here is where it's good that $M$ is a \textbf{space}, so that it has a diagonal map. Pulling back $(0\times \nu)\downarrow(M\times M)$ along $\Delta$ gives a map $\Thom(\nu)\to M_+\wedge \Thom(\nu)$. Then form the top row in:
\[\xymatrix@R=4mm{
\Thom(\nu)
\ar[r]
\ar[d]
&%r1c1
M_+\wedge \Thom(\nu)
\ar[r]^-{\textup{T.class}}
&%r1c2
M_+\wedge \Sigma^kH\Z
\\%r1c3
\Thom(\nu)\wedge H\Z\ar@{..>}[rru]
&%r2c1
&%r2c2
%r2c3
}\]
The dotted arrow, formed using the ring structure on $H\Z$ (which can be viewed as the extension of the top row to the free $H\Z$-module on $\Thom(\nu)$) is the map inducing the homology isomorphism.
\end{proof}
Now given an $R$-orientation, which should just be a map $\Thom(\nu)\to\Sigma^kR$ for some ring spectrum $R$, \rednote{(right?)} we can do exactly the same thing.
\paragraph*{On the diagram (2.11) in ABGHR:}
From a map $X\to BGL_1\mathbb{S}$ one can form \emph{genuine} sphere bundles on the skeleta of $X$. Wait a minute...\ how was that supposed to go?

Anyway, if we could, then we have a bundle of sphere spectra $\xi\downarrow X$. Smashing fiberwise with $R$, we expect to get a bundle of free rank one $R$-modules $(R\wedge _\textup{fib}\xi)\downarrow X$, classified by the composite $X\to BGL_1\mathbb{S}\to BGL_{1}R$. If this system is null, we should view the bundle $\xi$ as orientable. We should view trivialisations of $R\wedge _\textup{fib}\xi$ as orientations of $\xi$.
Now the dotted lifting in
\[\xymatrix@R=4mm{
&%r1c1
B(\mathbb{S},R)
\ar[d]
\ar[r]
&%r1c2
\ast\ar[d]
\\%r1c3
X
\ar@{..>}[ur]
\ar[r]
&%r2c1
BGL_1\mathbb{S}
\ar[r]
&%r2c2
\ar@{}[ul]|-{\textup{pull}}
BGL_1R%r2c3
}\]
is the same as a trivialisation of $R\wedge_{\textup{fib}}\xi$, so should be viewed as an $R$-orientation of $\xi$.

By the way, given a fibration $F\to E\to B$, $\Omega B$ acts on $F$ (by gluing the loop on the end of the path which is part of the data of a point of $F$). Then, $E$ is the homotopy orbit space of $E$ under this action. (Note that $\Omega B$ is only a grouplike $A_\infty$ space, so that you don't actually get a group action, only an $A_\infty$ type thing.)

\paragraph*{Which connective spectra are Thom spectra:}
Both $H\Z$ and $H\Z_2$ are... Let the top map in the following diagram be a generator of $\pi_1(BO)=\pi_0(O)=\Z_2$:
\[\xymatrix@R=4mm{
S^1\ar[r]
\ar[d]
&%r1c1
BO\\%r1c2
\Omega^2S^3\ar[r]
&%r2c1
\ar[u]
\Omega^2\Sigma^2BO%r2c2
}\]
[this extension exists as $BO$ is a 2-fold loopspace. ????]

Then $H_*(\Omega^1 S^3)$ is a tensor algebra, so $H_*(\Omega^1 S^3)$ is a divided polynomial algebra, and 
\[H_*(\Omega^1 S^3;\Z_2)=E[x_2,x_4,x_8,\ldots]\]
Now by the Borel comparison theorem,
\[H_*(\Omega^2 S^3;\Z_2)=\F_2[x_1,x_3,x_7,\ldots]\]
which is the Milnor form of the dual of the Steenrod algebra. In particular, we obtain an algebra mp $H_*(\Omega^2 S^3)\to H_*(BO)$, as \emph{the Thom spectrum of a bundle classified by a ring map is a Ring spectrum, and the Thom isomorphism is then an isomorphism of algebras}.

We then have to do something clever with SW classes, ...
\end{document}








