% !TEX root = z_output/michael_donovan_teaching_statement.tex
\documentclass[11pt]{article}
%\input{../../Dropbox/logbook/_LOGBOOK/macros.tex}
%\usepackage{framed}
%\usepackage{biblatex} 
%\usepackage[style=numeric,%citestyle=numeric,
%\hypersetup{colorlinks=false,pdfborder={0 0 0}}
%\makeatletter
%\renewcommand{\@seccntformat}[1]{\csname the#1\endcsname.\quad}
%\makeatother

%\theoremstyle{plain}
%\newtheorem{theorem}{Theorem}
%\renewcommand*{\thetheorem}{\Alph{theorem}}
%\newtheorem{conjectureAlpha}{Conjecture}
%\renewcommand*{\theconjectureAlpha}{\Alph{conjectureAlpha}}
%
%\newcommand{\NOFULLPAGE}{\relax}
%
%\newcommand{\Sq}{\mathrm{Sq}}
%
%\bibliography{../../Dropbox/logbook/_LOGBOOK/papers}
%

%\documentclass[11pt]{article}
\input{../macros.tex}

\begin{document}
\section*{\huge Teaching statement \hfill\normalsize Michael Donovan}
\pagestyle{empty}

Over almost the entire course of my higher education, I have been lucky enough to be involved in teaching a number of subjects, either as a course assistant or a recitation leader. Such interaction with students is perhaps the key connection between mathematicians and the community at large, and I have always made it my priority to give the students as rewarding an experience of mathematics possible.

During my time as a graduate student at MIT, my primary teaching responsibilities have been to lead recitations in a differential equations course. I have also been involved in the very rewarding directed reading program, which involves mentoring undergraduate students while they study a topic not typically encountered in the undergraduate program. Prior to coming to MIT, I had extensive experience as a recitation leader in actuarial science. My enthusiasm for the material and for sharing with the students has led me to become a more effective teacher, receiving consistently excellent feedback from the students. I was recently jointly awarded the \emph{Charles and Holly Housman Award for Excellence in Teaching} for my teaching contributions at MIT.

% As a recitation leader, I find myself under opposing imperitives: the need to present the material at hand to the students in order that they have strong enough recall that they can successfully complete the recitation task, and the need to give the students plenty of time to try the techniques themselves. I'll explain my approach to balancing these objectives in the next paragraph.


Good preparation has always been the foundation of my teaching method. Before each recitation, I carefully examine the material covered in the surrounding lectures, and assess which aspects are likely to be causing the students difficulty. I then carefully construct an example problem that brings all of these aspects together. By photocopying the example problem onto lined paper, I ensure even those students who don't dependably bring paper to recitation are able to engage with the example. In this way I am able to create momentum from the very beginning of the hour.

About fifteen minutes in, heads are nodding (for better or worse) and the students are able to move swiftly into their work. I enjoy interacting with the students individually while they work, and use that time as an opportunity to assess which learning objectives are being met, and to identify problem areas for the students. I am then able to make effective comments to the class near the end of the session, pointing out the key methods they may use and the main challenges they are facing.

I also make sure that I am available to the students outside recitation times, and students often make appointments with me to discuss both mathematical questions and other issues, including the difficulties they experience managing their course load. I thoroughly enjoy dealing with students in and out of the classroom, and make an effort to always be approachable. In this way I am better able to identify at-risk students and direct them to the available resources.

My main goals as a recitation leader are creating self-motivation amongst the students and imparting learning techniques that will serve them throughout their time at MIT. This is especially important in first year courses such as ordinary differential equations, and I take my role as an opportunity to contribute positively to the culture of learning at MIT.
\end{document}














