% !TEX root = z_output/_notes.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% 80 characters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{article}
%\newcommand{\dontloadhyperref}{}
\input{../macros.tex}

\newcommand{\myheading}[1]
{{\noindent\Large #1}

}
\newcommand{\shrt}[1]{\makebox[0cm]{\ensuremath{#1}}}
\renewcommand{\myheading}[1]{\subsection{#1}}
\setcounter{secnumdepth}{1}
\begin{document}
%\tableofcontents
% {\color{red}In order to write your exact couple how you do,
% nice things need to happen with filtrations. Otherwise the triangles may
% not happen. In the case in mind obviously each of those is coming from a
% LES.}
%
%\noindent Yeah, this setup works really well when it's coming from a bunch of
%exact triangles. In general, if you have an exact couple $A\to A\to E\to A$
%(with any indices and shifts implicit), you can form a diagram
%\[\xymatrix@C=.5cm{
%0\ar[rr]&&A\ar[rr]\ar@{=}[ld]&&A\ar[rr] \ar[ld]&&A\ar[ld]
%\ar[rr]&&\cdots\\
%&\cdots\ar[r]&h_*(E)\\
%&A\ar[ul]&&
%E\ar@{~>}[lu]&&
%E\ar@{~>}[lu]&&
%E\ar@{~>}[lu]
%}\]
%Anyway, hitting this diagram with the same procedure gives a spectral sequence
%converging to the direct limit of the top row. I really don't know if that's
%useful, but I might if I knew the answer to the following question:
%{
%\color{blue} What are the terms $E^r$ in the sequence of derived exact couples
%supposed to converge to, in complete generality?
%}
%
%{\color{red}
%For the $Z^r$ and $B^r$ terms to "reach" the $Z^\infty$, $B^\infty$ terms we
%need two conditions to hold.
%\begin{enumerate}
%\item Every person living in the $i^\text{th}$ period has an age below some
%number
%\item Every person living in the $i^\text{th}$ period who eventually dies, dies
%before a certain age
%\end{enumerate}
%The condition you give makes sure $b_i:\Gr_i P\to E_i^{\infty}$ is an
% isomorphism but $E^r$ may still not reach $E^\infty$.
%}
%
%\noindent Quite so --- I hadn't thought of that. What you're saying is: if you
%want $Z_i^r=Z_i^\infty$ and $B_i^r=B_i^\infty$ for $r\gg0$, then you need your
%two conditions.
%
%Here's a thought: although it's great when $E_i^r=E_i^\infty$ for $r\gg0$, if
%you have a spectral sequence in which this doesn't happen, you can still
%discuss its convergence in some (natural) way. %$Is that actually necessary for
%the whole thing to make sense? I suppose if you want it to be like a
%traditional spectral sequence, you want it all to stabilise, but maybe there's
%a more general setting when you mightn't care that you need to take the union
%and intersection of these groups.
%
%Suppose you have abelian groups $I^r, O^r, E_r$ for each $r>0$, that there are
%maps $I^r\to E^r\to O^r$ with composite zero, and that $E^{r+1}$ is defined to
%be the homology at $E^r$. Then each $E^r$ is a subquotient of $E^1$, and you
%can identify it with $Z^r/B^r$ for some subgroups $Z^r,B^r$ of $E^1$, with the
%$Z^r$ decreasing and the $B^r$ increasing. Then it's not too unnatural to
%consider the subgroups $Z^\infty=\cap Z^r$ and $B^\infty=\cup B^r$ of $E^1$,
%and define $E^\infty:=Z^\infty/B^\infty$.
%
%Thus, if we don't demand the above convergence conditions, we'll not get a
%stabilisation to $E^\infty_i$, but $E^\infty_i$ in determined in a natural way
%from the $E^r_i$, so as long as you know that's going to happen, you should be
%ok. {\color{blue} Does that make sense?}
%
%\pagebreak
\myheading{Births, Deaths, and Marriages}% \'a la 1984}
Ok, fine, so there might not be any marriages, but check this out\,\ldots

\Bullet \textbf{Population:} Consider a graded abelian population $P_*$. That
is, $P_i$ is the abelian group consisting of those people which are alive at
time $i$. There is a map $T_{i}:P_{i-1}\to P_{i}$, representing the passing of
time from $(i-1)$ to $i$.

\Bullet \textbf{Certificates:} The government maintains a graded abelian
database $C_*$. The group $C_i$ consists of birth and death certificates
relevant to the time period from $(i-1)$ to $i$. More on this later.

\Bullet \textbf{Death:} Of course, as this is a graded \emph{abelian}
population, a person in $P_{i-1}$ can be mapped to zero under $T_{i}$, in which
case they must have \emph{died} during the period $(i-1)$ to $i$. We will say
that they \emph{died at $P_{i-1}$}, as $P_{i-1}$ was the last place they were
seen alive. We will also say that their time of death was $(i-1)$.

\Bullet \textbf{Birth:} Similarly, a person $p\in P_i$ need not be in the image
of $T_{i}$, in which case they must have been \emph{born} between $(i-1)$ and
$i$. We will say that they were \emph{born on $P_i$}.

\Bullet \textbf{Age:} We will say that somebody who was born on $P_j$ and who
died at $P_i$ was ``seen at $i-j+1$ times''. This is how we measure age.

\Bullet \textbf{Immortals:} We will not rule out the possibility that some
(nonzero) people live for ever. That is, we will allow for the possibility of
\emph{immortals}.

\Bullet \textbf{Co-immortals:} We will, however, assume that only the zero
person $p\in P_i$ is in the image of $T_{j}\circ\cdots\circ T_i$ for all $j\leq
i$. That is, there are no (nonzero) \emph{co-immortals}: every nonzero person
must have been born some finite time ago. That is to say that the inverse limit
of the $P_i$ is zero.

\Bullet \textbf{Birth certificates:} If a person $p\in P_{i}$ was born on $P_i$,
they report this to the government by submitting a nonzero birth cirtificate
$B_{i}(p)\in C_i$. Naturally, any $p\in P_{i}$ who was not born on $P_i$ submits
the zero birth certificate. Thus there is are `birth certificate' maps
$B_i:P_i\to C_i$.

\Bullet \textbf{Death certificates:} There is also a map $M_{i}:C_{i}\to
P_{i-1}$, the `death certificate' map.\footnote{$M$ for `mortality', as $d$ is
reserved for `differential'.} Any nonzero person in the image of $M_{i}$ has
received a death certificate, and will die at $P_{i-1}$. That is, people receive
their death certificate at the start of the period in which they die ---
terrifying.

\Bullet \textbf{Exactness:} We have found a triangle of maps
$T_{i},\,B_{i},\,M_{i}$ as in the diagram below. Now it must be the case that
this triangle is exact at each vertex. It's exact at $P_{i-1}$, as the people
who die at $P_{i-1}$ are exactly those who received death certificates. It's
exact at $P_i$, as those people $p\in P_i$ who were not born there are exactly
those who submit the zero birth certificate. It's exact at $C_i$, as the
database does not contain any certificates other than birth and death
certificates, and, of course, all birth certificates map to zero under the
`death certificate' map $M_i$.

In particular, we have a collection of exact triangles, consisting of the
straight arrows in the following:
%\[\xymatrix@!0@C=1.1cm@R=1.28cm{
%\makebox[0cm][r]{$\cdots$\ \ }
%P_{i-1}\ar[rrrr]^{T_{i  }}%^{\text{$(i-1)^\text{st}$ period}}
%&&&&\ar[dll]_{B_{i  }}
%\ar@{..>>}[ddl]_{b_{i  }}
%P_{i  }\ar[rrrr]^{T_{i+1}}%^{\text{$ i   ^\text{th}$ period}}
%&&&&\ar[dll]_{B_{i+1}}
%\ar@{..>>}[ddl]_{b_{i+1}}
%P_{i+1}\ar[rrrr]^{T_{i+2}}%^{\text{$(i+1)^\text{st}$ period}}
%&&&&\ar[dll]_{B_{i+2}}
%\ar@{..>>}[ddl]_{b_{i+2}}
%P_{i+2}\makebox[0cm][l]{\ \ $\cdots$}\\
%&&C_{i  }\ar[ull]_{M_{i  }}\ar@{~>}[dl]^\mu&&
%&&C_{i+1}\ar[ull]_{M_{i+1}}\ar@{~>}[dl]^\mu&&
%&&C_{i+2}\ar[ull]_{M_{i+2}}\ar@{~>}[dl]^\mu&&
%\\
%&\coim(M_{i  })\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i  }}
%&&\im(B_{i  })\ar@{~>}[ul]^\beta&
%&\coim(M_{i+1})\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i+1}}
%&&\im(B_{i+1})\ar@{~>}[ul]^\beta&
%&\coim(M_{i+2})\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i+2}}
%&&\im(B_{i+2})\ar@{~>}[ul]^\beta&
%\\
%&0&&0\ar@{~>}[u]&
%&0&&0\ar@{~>}[u]&
%&0&&0\ar@{~>}[u]&
%}\]
\[\xymatrix@!0@C=1.1cm@R=1.28cm{
\makebox[0cm][r]{$\cdots$\ \ }
P_{i-2}\ar[rrrr]^{T_{i-1}}%^{\text{$(i-2)^\text{st}$ period}}
&&&&\ar[dll]_{B_{i-1}}
\ar@{..>>}[ddl]_{b_{i-1}}
P_{i-1}\ar[rrrr]^{T_{i  }}%^{\text{$ i-1 ^\text{th}$ period}}
&&&&\ar[dll]_{B_{i  }}
\ar@{..>>}[ddl]_{b_{i  }}
P_{i  }\ar[rrrr]^{T_{i+1}}%^{\text{$(i  )^\text{st}$ period}}
&&&&\ar[dll]_{B_{i+1}}
\ar@{..>>}[ddl]_{b_{i+1}}
P_{i+1}\makebox[0cm][l]{\ \ $\cdots$}\\
&&C_{i-1}\ar[ull]_{M_{i-1}}\ar@{~>}[dl]^\mu&&
&&C_{i  }\ar[ull]_{M_{i  }}\ar@{~>}[dl]^\mu&&
&&C_{i+1}\ar[ull]_{M_{i+1}}\ar@{~>}[dl]^\mu&&
\\
&\coim(M_{i-1})\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i-1}}
&&\im(B_{i-1})\ar@{~>}[ul]^\beta&
&\coim(M_{i  })\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i  }}
&&\im(B_{i  })\ar@{~>}[ul]^\beta&
&\coim(M_{i+1})\ar@{~>}[d]\ar@{_{(}..>}[uul]_{m_{i+1}}
&&\im(B_{i+1})\ar@{~>}[ul]^\beta&
\\
&0&&0\ar@{~>}[u]&
&0&&0\ar@{~>}[u]&
&0&&0\ar@{~>}[u]&
}\]

\Bullet \textbf{Organisation of certificates:} The database is not particularly
organised, so the group $C_{i}$ does not split into the direct sum of the birth
and death certificates. However, there are the above short exact sequences,
drawn with wavy arrows. Here, $\im(B_{i})$ is the subgroup consisting of birth
certificates, and the quotient group
$\coim(M_{i}):=C_i/\ker(M_i)\cong\coker(B_i)$ consists of the death
certificates. Moreover, the birth and death certificate maps factorise as shown
with dotted arrows.

\Bullet \textbf{A spectral sequence:} We can form a spectral sequence out of
these exact triangles in the usual way, whose terms are defined as follows (for
$r\geq1$):
\begin{alignat*}{2}
Z_{i}^{r-1}:=&\left\{x\in \coim(M_i)\ \middle|\ m_i(x)\in\im(P_{i-r}\to
P_{i-1})\right\}\\
%=&\left\{\text{death certificates $x$ for people at least $r$ periods
%old}\right\}.\\%\footnotemark\\
=&\left\{\text{death certificates $x$ for people $m_i(x)\in P_{i-1}$ who were
born on $P_{i-r}$ or before}\right\}.\\
=&\left\{\text{death certificates $x$ for people $m_i(x)\in P_{i-1}$ seen at $r$
or more times}\right\}.\\
B_{i}^{r-1}:=&\left.b_i(\ker(P_i\to P_{i+r-1}))\right.\\
=&\left\{\text{birth certificates $b_i(p)$ for people $p\in P_i$ who will die at
or before $P_{i+r-2}$}\right\}.\\
=&\left\{\text{birth certificates $b_i(p)$ for people $p\in P_i$ seen at $r-1$
or fewer times}\right\}.\\
E_{i}^{r}:=&\left.\mu^{-1}(Z_{i}^{r-1})/\beta(B_{i}^{r-1}).\right.
\end{alignat*}
Note also that in the quotient $\im(B_i)/B_i^{r-1}$, the birth certificates that
remain are those of people who were seen at $r$ or more times.

\Bullet \textbf{Differentials:} The differential $d_r$ on $E^{r}$ takes a
certificate $c\in\mu^{-1}(Z_i^{r-1})$, and maps it to $M_i(c)\in P_{i-1}$, pulls
it back to a person $p\in P_{i-r}$, and takes their birth certificate
$B_{i-r}(p)$. The only way this certificate can be nonzero in $E_r$ is when $p$
was actually born on $P_{i-r}$. That is, when $p$ was seen at exactly $r$ times.
The point here is that the indeterminacy in $B_{i-r}(p)$ consists birth
certificates of people who die by $P_{i-2}$, i.e.\ who are seen at at most $r-1$
times. These certificates lie in $B_{i-r}^{r-1}$.

Surveying the life of our chosen pullback $p$, we see that their death
certificate $c$ maps to their birth certificate $B_{i-r}(p)$ under $d_r$. Taking
homology to get from $E_*^r=\mu^{-1}(Z_{i}^{r-1})/\beta(B_{i}^{r-1})$ to
$E_*^{r+1}=\mu^{-1}(Z_{i}^{r})/\beta(B_{i}^{r})$ has the effect of
simultaneously annihilating both the birth and the death certificate of every
person seen at exactly $r$ times simultaneously.
% does not die before the end of the $(i-2)^\text{nd}$ period, i.e.\ iff 

%\footnotetext{Of course, zero is alwa}
\Bullet \textbf{$E^\infty$ page:} We make the following obvious extensions of
the above definitions, letting $Z^\infty_i$ be the intersection $\cap_rZ^r_i$,
and $B^\infty_i$ be the union $\cup_rB^r_i$:
\begin{alignat*}{2}
Z_{i}^\infty
=&\left\{\text{death certificates for co-immortals dying at
$P_{i-1}$}\right\}=0.\\
B_{i}^\infty=&\left\{\text{birth certificates $b_i(p)$ for mortals $p\in
 P_i$ born at $P_i$}\right\}.\\
E_{i}^{\infty}=&\left.\im(B_i)\,/\left\{\text{birth certificates $b_i(p)$ for
 mortals $p\in P_i$}\right\}.\right.
\end{alignat*}
Without further hypotheses, it need not be the case that $E_i^r= E_i^\infty$ for
$r\gg0$. However, the above is still a natural definition of the $E^\infty$
page, in the sense that $E^\infty_i$ can be recovered from knowledge of the
$E^r_i$ and the differentials in and out of $E^r_i$ for $r$ exceeding any fixed
number.

\Bullet \textbf{Abutment:} Now let $P=\varinjlim P_i$ be the direct limit of the
population under the maps $T_i$. Then $P$ can be viewed as the group of
immortals (modulo eventual equality). There is an increasing filtration on $P$
defined by $F_{i}P:=\im(P_i\to P)$. Let $\Gr_{i}P$ be the $i^\text{th}$
subquotient $F_{i}P/F_{i-1}P$. One finds that $b_i:\Gr_iP\to E^\infty_i$ is well
defined and an isomorphism.

To summarise: the population of immortals is filtered by time of birth, and the
subquotient consisting of those immortals born on $P_i$ is isomorphic to
$E_i^\infty$, i.e.\ the quotient:
\[\left\{\text{all birth certificates issued at time
$i$}\right\}/\left\{\text{those issued to mortals}\right\}.\]

\Bullet \textbf{The moral:} In passing from $E_*^{r}$ to $E_*^{r+1}$, we kill
off all of the mortals who were seen at $r$ times. To clarify, restricting to
the kernel of the differential $d_r$ out of $E^r_i$, is to restrict interest
only to death certificates for people who are seen at at least $r+1$ times.
Dually, to quotient by the image of $d_r$ coming in to $E^r_i$ is to elect to
ignore the birth certificates of people who are seen at $r$ or fewer times.
% of those people born
%on $P_i$ who die at $P_{i+r-1}$ precisely --- the same story.
%\footnote{We say that a mortal who was
%born at $P_i$ but first goes to zero in $P_{i+r+1}$ lived for $r$ years
%exactly.} 
%To be more precise, we discard both the birth and death certificates
%of these mortals as we pass from $E^{r-1}$ to $E^r$.

As we pass from $E_*^1$ to $E_*^2$ to $E_*^3$, and so on, we are allowing the
birth and death certificates of the shortest lived members of society to
mutually annihilate. When we reach $E_*^\infty$, all the the mortals'
certificates will have been annihilated, and we are only left with the birth
certificates of the immortals.
%
%To be even more precise, we claim that for each mortal that lives for exactly
%$r$ years, the differential $d_{r-1}$ sends its death certificate to its birth
%certificate. Taking homology groups in order to pass from $E^{r-1}$ to $E^r$
%then kills both the birth and death certificate of this element.
%Next we should interpret the group 
%$E_i^r$ is a quotient of the group $\mu^{-1}(Z_i^r)$. Now the groups
%$\mu^{-1}(Z_i^r)$ are a decreasing series of subgroups of $C_i$, and this
%decrease corresponds to the fact that in passing from , a group which decreases
%as $r$ increases. This group consits of (all birth cirtificates) and of death
%certificates for people at least $r$ years old --- a group --- as we run each
%step of the spectral sequence,

% differentials $d_r:E_i^r\to E_{i-r}^r$. Of course, the `formula' for $d_r$ is
%$d_r[x]=[b_i((T_{i-1 }\circ\cdots\circ T_{i-r})^{-1}m_i(x))]$. If this formula
%gives a nonzero result, then it takes a

\myheading{Discussion of the EHP spectral sequence}
For every integer $p$, at the prime 2, there is a fibre sequence: $\xymatrix{S^p\ar[r]^e&\Omega S^{p+1}\ar[r]^h& \Omega S^{2p+1}}$. Stringing these together for $0\leq p<M$, we have a diagram of fibrations:
\[\xymatrix{
\textup{pt}\ar[r]&\Omega S^1\ar[d]\ar[r]&\Omega^2 S^2\ar[d]\ar[r]&\Omega^3 S^3\ar[d]\ar@{.>}[rr]&&\Omega^{p+1}S^{p+1}\ar[d]\ar@{.>}[rr]&&\Omega^{M}S^{M}\ar[d]\\
&\Omega S^1&\Omega^2 S^3& \Omega^3S^5&&\Omega^{p+1}S^{2p+1}&&\Omega^{M}S^{2M-1}
}\]
Applying $\pi_*$ yields an exact couple, and we obtain a spectral sequence. This spectral sequence has exactly $M$ nonzero columns ($0\leq p <M$), and converges to the stem $\pi_{p+q}(\Omega^{M}S^{M})$ of $S^{M}$. Now:
\[E_{pq}^1=\pi_{p+q}(\Omega^{p+1}S^{2p+1})=\pi_q(\Omega^{2p+1}S^{2p+1})\text{ which is stable for $q< 2p$}.\]
Moreover:
\[
\frac{\im\left(e^{M-p-1}:\pi_{p+q}(\Omega^{p+1}S^{p+1})\to\pi_{p+q}(\Omega^MS^M)\right)}
{\im\left(\phantom{e^{M-p-1}:}\makebox[0cm][r]{$e^{M-p}\,\ :$}
\,\makebox[0cm][l]{$\pi_{p+q}(\Omega^{p}S^{p})$}\phantom{\pi_{p+q}(\Omega^{p+1}S^{p+1})}
\to\pi_{p+q}(\Omega^MS^M)\right)}\simeq E_{pq}^\infty\text{\ \ via \ }e^{M-p-1}(\sigma)\mapsto h_*\sigma.\]%\text{ for }\sigma\in\pi_{p+q}(\Omega^{p+1}S^{p+1}) \]
Thus $E^\infty_{pq}$ records those classes in the $(p+q)$-stem of $S^M$ which are born on $S^{p+1}$. Moreover, the way such a class in recorded on the $E^\infty$ page is by its Hopf invariant. Thus, if a class $\sigma\in\pi_{p+q}(\Omega^{p+1}S^{p+1})$ is the birthplace of an element in the $(p+q)$-stem of $S^M$, it is recorded as $h_*\sigma\in\pi_q({\Omega^{2p+1}S^{2p+1}})$ in $E^\infty_{pq}$.

When $q$ is $0$, $h_*\sigma$ is an element of the stable $0$-stem, and thus a genuine integer, which happily equals the old-fashioned Hopf invariant. More generally, when $q\leq 2p-2$, $h_*\sigma$ lands in the stable $q$-stem, so terms on the $E^\infty$ page which lie below a line of slope two are recorded by a `Hopf invariant' which lies in a stable homotopy group of spheres.

{\color{red}Discussion with Michael Andrews:}
There's nothing wrong with having a diagram like:
\[\xymatrix@C=.3cm{
\makebox[0cm][r]{$\cdots$\ }
A_{i-1}\ar@/^1em/[rrrrrr]&&
A_{i  }\ar@/^1em/[rrrrrr]\ar[dl]&&
A_{i+1}\ar@/^1em/[rrrrrr]\ar[ld]&&
A_{i+2}\ar@/^1em/[rrrrrr]\ar[ld]&&
A_{i+3}\ar[ld]&&
A_{i+4}\ar[ld]&&
A_{i+5}\ar[dl]\makebox[0cm][l]{\ $\cdots$}\\
&
\makebox[0cm][r]{$\cdots$\ }
E_{i  }&&
E_{i+1}\ar[lllu]&&
E_{i+2}\ar[lllu]&&
E_{i+3}\ar[lllu]&&
E_{i+4}\ar[lllu]&&
E_{i+5}\ar[lllu]\makebox[0cm][l]{\ $\cdots$}
}\]
That is, if you have an exact couple $A\to A\to E\to A$ of graded modules, and
each map is graded with a shift, you can still form an awesome diagram with
birth and death certificate groups all over it.

One interesting thing here is that the top row (and thus the abutment) is split
into three separate parts, while the body of the spectral sequence is not so
clearly split up.

{\color{red}Discussion with Michael Andrews, part two:}
To get the Atiyah-Hirzebruch spectral sequence for cohomology, you need to
dualise the approach for homology. One can dualise either on the level of
algebra, or on the level of spaces. To wit, one can use either of the following
exact couples.
\[\xymatrix@!0@C=1.6cm@R=1.28cm{%@C=.5cm{
\makebox[0cm][r]{$\cdots$\
}H^*(X,X_2)\ar[rr]&&H^*(X,X_1)\ar[rr]\ar[ld]&&H^*(X,X_0)\ar[rr]
\ar[ld]&&H^*(X)\ar[ld]
\ar@{=}[rr]&&H^*(X)\makebox[0cm][l]{\ $\cdots$}\ar[ld]\\
%&\cdots\ar[r]&h_*(E)\\
&H^*(X_2,X_1)\ar@{~>}[ul]&&
H^*(X_1,X_0)\ar@{~>}[lu]&&
H^*(X_0)\ar@{~>}[lu]&&
0\ar@{~>}[lu]
}\]
Here there an no co-immortals, and the direct limit is $H^*(X)$. The filtration
of $H^*(X)$ is by the images of the maps $H^*(X,X_i)\to H^*(X)$.
\[\xymatrix@!0@C=1.6cm@R=1.28cm{%@C=.5cm{
\makebox[0cm][r]{$\cdots$\ }
H^*(X_2)\ar[rr]&&
H^*(X_1)\ar[rr]\ar@{~>}[ld]&&
H^*(X_0)\ar[rr] \ar@{~>}[ld]&&\ar@{~>}[ld]
0\ar@{=}[rr]&&
0\makebox[0cm][l]{\ $\cdots$}\ar@{~>}[ld]\\
%&\cdots\ar[r]&h_*(E)\\
&H^*(X_2,X_1)\ar[ul]&&
H^*(X_1,X_0)\ar[lu]&&
H^*(X_0)\ar[lu]&&
0\ar[lu]
}\]
Here there are no immortals, and the inverse limit is $H^*(X)$. The filtration
of $H^*(X)$ is by the kernels of the maps $H^*(X)\to H^*(X_i)$. Of course, these
two filtrations coincide, by exactness in the long exact sequence for the pair
$(X,X_i)$.
\myheading{The Spectral Sequence Associated with a Filtered Chain Complex}
\newcommand{\theexp}[4]{\raisebox{-.1cm}[.5cm][0cm]
{\mbox{$\begin{array}{c}H_{#1}(\frac{F_{#2}}{F_{#3}}) \\
=E^1_{#4} \end{array}$}}}%used in the Filtered chain complex SS
Suppose that $C_*=\varinjlim(F_0C_*\hookrightarrow F_1C_*\hookrightarrow
F_2C_*\hookrightarrow\cdots)$ is a filtered chain complex. Then there is a
spectral sequence $\{E^r_{s,t}\}$ converging to $H_{s+t}(C_*)$, such that
$E^1_{s,t}=H_{s+t}(F_sC_*/F_{s-1}C_*)$. Here the target of convergence is graded
via $F_s(H_{s+t}(C_*))=\im(H_{s+t}(F_sC_*)\to H_{s+t}(C_*))$. Thus it is claimed
that $E^\infty_{s,t}\simeq F_s(H_{s+t}(C_*))/F_{s-1}(H_{s+t}(C_*))$. Consider
the following diagram:
% \[\xymatrix{
% &&&0\ar@{.>}[d]&\\
% &&&H_{s+t-1}(F_{s-r-1})\ar[d]^\alpha \ar[r]&\theexp{s+t-1}{s-r-1}{s-r-2}{s-r-1,t+r}\\
% &&&H_{s+t-1}(F_{s-r})\ar@{.>}[d] \ar[r]^{g'}&\theexp{s+t-1}{s-r}{s-r-1}{s-r,t+r-1}\\
% &&&H_{s+t-1}(F_{s-2}) \ar[d]\ar[r]&\theexp{s+t-1}{s-2}{s-3}{s-2,t+1}\\
% \theexp{s+t+1}{s+1}{s}{s+1,t}\ar[r]&H_{s+t}(F_s)\ar[r]^g\ar[d]&
% \theexp{s+t}{s}{s-1}{s,t}\ar[r]^\partial\ar@/^2pc/[rruu]^(.3){\text{``$d_r$''}}
% &H_{s+t-1}(F_{s-1}) \ar[r]&\theexp{s+t-1}{s-1}{s-2}{s-1,t}\\
% \theexp{s+t+1}{s+2}{s+1}{s+2,t-1}\ar[r]&H_{s+t}(F_{s+1})\ar@{.>}[d]\\
% \theexp{s+t+1}{s+r}{s+r-1}{s+r,t-r+2}\ar[r]^{\partial'}&H_{s+t}(F_{s+r-1})\ar[d]^{\beta}\\
% \theexp{s+t+1}{s+r+1}{s+r}{s+r,t-r+1}\ar[r]&H_{s+t}(F_{s+r})\ar@{.>}[d]\\
% &H_{s+t}(C_*)
% }\]
\[\xymatrix@C=.5cm@R=.7cm{
&&&0\ar@{.>}[d]&\\
&&&H_{s+t-1}(F_{s-r-1})\ar[d]^\alpha \ar[r]&\theexp{s+t-1}{s-r-1}{s-r-2}{s-r-1,t+r}\\
&H_{s+t}(F_{s-1})\ar[d]^\gamma&&H_{s+t-1}(F_{s-r})\ar@{.>}[d] \ar[r]^{g'\ \ }&\theexp{s+t-1}{s-r}{s-r-1}{s-r,t+r-1}\\
%&&&H_{s+t-1}(F_{s-2}) \ar[d]\ar[r]&\theexp{s+t-1}{s-2}{s-3}{s-2,t+1}\\
%the bendy arrow was:\ar@/^2pc/[rruu]^(.3){\text{``$d_r$''}}
\theexp{s+t+1}{s+1}{s}{s+1,t}\ar[r]&H_{s+t}(F_s)\ar[r]^{g\ \ }\ar@{.>}[d]&
\theexp{s+t}{s}{s-1}{s,t}\ar[r]_\partial\ar[rru]^(.4){\text{``$d_r$''}}
&H_{s+t-1}(F_{s-1}) \ar[r]&\theexp{s+t-1}{s-1}{s-2}{s-1,t}\\
%\theexp{s+t+1}{s+2}{s+1}{s+2,t-1}\ar[r]&H_{s+t}(F_{s+1})\ar@{.>}[d]\\
\theexp{s+t+1}{s+r}{s+r-1}{s+r,t-r+2}\ar[r]_{\ \ \partial'}\ar[rru]^(.4){\text{``$d_r$''}}&H_{s+t}(F_{s+r-1})\ar[d]^{\beta}\\
\theexp{s+t+1}{s+r+1}{s+r}{s+r,t-r+1}\ar[r]&H_{s+t}(F_{s+r})\ar@{.>}[d]
&&\makebox[0cm]{
{\small {(Transcribed from a lecture  by Mark Behrens, 29/3/11.)}}
}
\\
&H_{s+t}(C_*)
}\]
\begin{alignat*}{2}
\text{Define:\qquad } E^r_{s,t}&:=Z^r_{s,t}/B^r_{s,t}\text{, where:}\\
Z^r_{s,t}&:=\partial^{-1}(\im(H_{s+t-1}(F_{s-r})\to H_{s+t-1}(F_{s-1})))\subseteq E^1_{s,t}\\
B^r_{s,t}&:=g(\ker(H_{s+t}(F_{s})\to H_{s+t}(F_{s+r-1})))\subseteq E^1_{s,t}
\end{alignat*}
Given an element $x\in Z^r_{s,t}$, there is an element $a\in H_{s+t-1}(F_{s-r})$ such that $x$ and $a$ have the same image in $H_{s+t-1}(F_{s-1})$. Then $g'(a)$ is an element of $Z^r_{s-r,t+r-1}$. Different choices for $a$ differ by elements of $\ker(H_{s+t-1}(F_{s-r})\to H_{s+t-1}(F_{s-1}))$, so that the class of $g'(a)$ in $E^r_{s-r,t+r-1}$ is well defined. Then the map $\partial_r:E^r_{s,t}\to E^r_{s-r,t+r-1}$ is defined via this process, and $\partial_r^2=0$.

Now the elements of $E^1_{s,t}$ which represent an element of the kernel of $d_r$ are exactly the elements of $Z^{r+1}_{s,t}$, since $\ker(g')=\im(\alpha)$. Similarly, the elements of $E^1_{s,t}$ which represent an element of the image of $d_r$ are exactly the elements of $B^{r+1}_{s,t}$, since $\ker(\beta)=\im(\partial')$. Thus $H_{s,t}(E^r_{*,*},\partial_r)\simeq E^{r+1}_{s,t}$ as desired.

Finally, we should find an isomorphism $E^\infty_{s,t}\to F_s(H_{s+t}(C_*))/F_{s-1}(H_{s+t}(C_*))$. For this, note that $Z^\infty_{s,t}=\ker\partial=\im(g)$ and $B^\infty_{s,t}=g(\ker(H_{s+t}(F_s)\to H_{s+t}(C_*)))$. So given $x=g(y)\in Z^\infty_{s,t}$, $y$ maps via the vertical arrows to an element of $F_s(H_{s+t}(C_*))$. As $\ker(g)=\im(\gamma)$, this is well defined up to an element of $F_{s-1}(H_{s+t}(C_*))$, so we have defined a map $Z^\infty_{s,t}\to F_s(H_{s+t}(C_*))/F_{s-1}(H_{s+t}(C_*))$. A brief diagram chase reveals that the kernel is $B^\infty_{s,t}$ and that the map is onto.
%
%\begin{flushright}
 %{\small Transcribed  by Michael Donovan from a lecture of Mark Behrens, 29 March, 2011.}
%\end{flushright}

\myheading{A Derivation of the Leray-Serre-Atiyah-Hirzebruch Spectral Sequence}
Suppose that $\pi:E\to B$ is a Hurewicz fibration, with fiber $F$, where $B$ is a (finite?) connected CW-complex. Let $B^n$ be the $n$-skeleton of $B$, and define $E^n:=\pi^{-1}B^n$. Let $h_*$ be an unreduced homology theory. The long exact sequences for the pairs $(E^p,E^{p-1})$ can be written as in the following diagram. Here, wavy arrows indicate a map with degree $-1$, and each triangle is exact.
\[\xymatrix@C=.5cm{
0\ar[rr]|{\ \cdot\ \cdot\ \cdot\ }&&h_*(E^{p-1})\ar[rr]^i\ar[ld]_\rho&&h_*(E^{p})\ar[rr]^i \ar[ld]_\rho&&h_*(E^{p+1})\ar[ld]_\rho
\ar[rr]|{\ \cdot\ \cdot\ \cdot\ }&&h_*(E)\\
%&\cdots\ar[r]&h_*(E)\\
&\ \ \ \ \shrt{h_*(E^{p-1},E^{p-2})}\phantom{\binom{5}{3}}&&
\shrt{h_*(E^{p},E^{p-1})}\phantom{\binom{5}{3}}\ar@{~>}[lu]_\partial&&
\shrt{h_*(E^{p+1},E^{p})}\phantom{\binom{5}{3}}\ar@{~>}[lu]_\partial&&
\shrt{h_*(E^{p+2},E^{p+1})}\phantom{\binom{5}{3}}\ar@{~>}[lu]_\partial
}\]
Define, for $r\geq0$:
\begin{alignat*}{2}
Z_{pq}^r:=&\left\{x\in h_{p+q}(E^p,E^{p-1})\ \middle|\ \partial x\in\im(i^{r})\right\}\\
=&\left\{\text{relative classes $x$ whose boundary comes from $h_{p+q-1}(E^{p-r-1})$}\right\}.\\
B_{pq}^r:=&\left.\rho(\ker(i^r))\right.\\
=&\left\{\rho(y)\ \middle|\ y\in h_{p+q}(E^p),\ i^r(y)=0\in h_{p+q}(E^{p+r})\right\}\\
=&\left\{\text{restrictions $\rho(y)$ of classes $y\in h_{p+q}(E^p)$ which are nullhomologous in $E^{p+r}$}\right\}.\\
E_{pq}^{r+1}:=&\left.Z_{pq}^r/B_{pq}^r.\right.%\textbf{ (is this $E_{pq}^r$?)}
\end{alignat*}
As each triangle is exact, $B_{pq}^r\subseteq E_{pq}^r$ for all $p,q,r$, so that the definition of $E_{pq}^{r+1}$ makes sense.
Note that $Z_{pq}^0=h_{p+q}(E^p,E^{p-1})$ and $B_{pq}^0=0$, so that $E_{pq}^1=h_{p+q}(E^p,E^{p-1})$.

For each $p,q\geq0$, let $i_{pq}:h_{p+q}(E^p)\to h_{p+q}(E)$ be the map on homology induced by the inclusion. Then there is an increasing filtration on $h_{p+q}(E)$ defined by $F_{p}h_{p+q}(E):=\im(i_{pq})$. Let $\Gr_{pq}$ be the $p^\text{th}$ subquotient $F_{p}h_{p+q}(E)/F_{p-1}h_{p+q}(E)$. Also, define $Z^\infty_{pq}$ and $B^\infty_{pq}$ as follows:
\begin{alignat*}{2}
Z_{pq}^\infty:=&\left.\bigcap_r Z_{pq}^r\right.=\left\{x\in h_{p+q}(E^p,E^{p-1})\ \middle|\ \partial x=0\right\}\\
%=&\left.\im(\rho:h_{p+q}(E^p)\to h_{p+q}(E^p,E^{p-1}))\right.\\
=&\left.\rho(h_{p+q}(E^p)).\right.\\
B_{pq}^\infty:=&\left.\bigcup_r B_{pq}^r\right.=\left\{\rho(y)\ \middle|\ y\in h_{p+q}(E^p),\ i_{pq}(y)=0\in h_{p+q}(E)\right\}\\
=&\left.\rho(\ker (i_{pq})).\right.\\
\Gr_{pq}=&\left.\im\bigl(h_{p+q}(E^p)\rightarrow h_{p+q}(E)\bigr)/\im\bigl(h_{p+q}(E^{p-1})\rightarrow h_{p+q}(E)\bigr).\right.
\end{alignat*}

Define an isomorphism $E^\infty_{pq}:=Z_{pq}^\infty/B_{pq}^\infty\to \Gr_{pq}$
by $[\rho(y)]\mapsto[i_{pq}(y)]$, for $y\in h_{p+q}(E^p)$. A diagram chase reveals that this is well defined and an isomorphism.

Finally, we can define differentials $d_{r+1}:E^{r+1}_{pq}\to E^{r+1}_{p-r-1,q+r}$ by the recipe $[x]\mapsto [\rho i^{-r}\partial(x)]$, for $x\in Z_{pq}^{r}$. A rather larger diagram chase reveals that this gives a differential on the groups $E^{r+1}_{pq}$ of bidegree $(-r-1,r)$, whose homology at $E^{r+1}_{pq}$ is $E^{r+2}_{pq}$, so that we have defined a spectral sequence converging to $h_{p+q}(E^p)$.



\myheading{Principal \texorpdfstring{$G$}{G}-bundles on \texorpdfstring{$\Sigma A$}{SA} --- clutching v.\ classifying}
Let $A$ be a pointed space, and $G$ a topological group. Suppose that $\beta:A\to \Omega BG$ and $\gamma:\Sigma A\to BG$ are adjoint maps. We can produce a principal $G$-bundle on $\Sigma A$ by either using a clutching construction with $\beta$, or pulling back $EG$ along $\gamma$. This note shows that the two bundles obtained are isomorphic.

Firstly, use the HLP to construct the map $L$ below (where $\star$ is the constant map to the basepoint of $EG$, and $\widetilde\epsilon$ is evaluation $(t,\sigma)\mapsto \sigma(t)$):
\[\xymatrix{
\{0\}\times\Omega BG\ar[r]^{\ \ \ \ \star}\ar[d]&EG\ar[d]^{\pi}\\
I\times\Omega BG\ar[r]^{\ \ \ \ \widetilde\epsilon}\ar@{-->}[ru]^L&BG
}\]
Then the equivalence $\phi:\Omega BG\to G$ is given by $\sigma\mapsto L(1,\sigma)$, where $G$ is identified with the fiber of $\pi$. Now define:
%\[E_cG:=G\times C(\Omega BG)\sqcup G / (g,1,\sigma)\sim gL(1,\sigma).\]
%There is a map $E_cG\to \Sigma\Omega BG$ defined by sending $(g,t,\sigma)\mapsto(t,\sigma)$. Moreover, there is a map $E_cG\to EG$ defined by $(g,t,\sigma)\mapsto gL(t,\sigma)$. Thus we have a morphism of principal $G$-bundles lying over the counit $\epsilon_{BG}$:
%\[\xymatrix{
%E_cG\ar[r]\ar[d]&EG\ar[d]\\
%\Sigma\Omega BG\ar[r]^{\ \ \epsilon_{BG}}&BG
%}\]%\text{\ \ which implies that }\]
%Thus $E_cG\simeq\epsilon_{BG}^*(EG)$. Now, let $E_c\beta$ be the space:
%\[E_c\beta:=G\times C(A)\sqcup G / (g,1,a)\sim gL(1,\beta(a)).\]
%Then $E_c\beta$ maps to $\Sigma A$ via $(g,t,a)\mapsto(t,a)$. Moreover, there is a map $E_c\beta\to E_cG$ defined by $(g,t,a)\mapsto (g,t,\beta(a))$.
\[E_c\beta:=G\times C(A)\sqcup G / (g,1,a)\sim gL(1,\beta(a)).\]
Then $E_c\beta$ maps to $\Sigma A$ via $(g,t,a)\mapsto(t,a)$. Moreover, there is a map $E_c\beta\to EG$ defined by $(g,t,a)\mapsto gL(t,\beta(a))$, which makes the following diagram commute (as is checked): 
\[\xymatrix{
E_c\beta\ar[rr]\ar[d]&&EG\ar[d]&
(g,t,a)\ar@{|->}[rr]\ar@{|->}[d]&&gL(t,\beta(a))\ar@{|->}[d]\\
\Sigma A\ar[r]^{\Sigma\beta}&\Sigma\Omega BG\ar[r]^{\epsilon_{BG}}&BG&
(t,a)\ar@{|->}[r]&(t,\beta(a))\ar@{|->}[r]&\beta(a)(t)
}\]
As $\gamma=\epsilon_{BG}\circ\Sigma\beta$, this shows that $E_cB$ (obtained from $\beta$ by clutching) is isomorphic to $\gamma^*EG$.


\myheading{The Projective Bundle Theorem}
Suppose that $\xi\downarrow B$ is a complex $n$-plane bundle. Let $\PP(\xi)\downarrow B$ be the associated $\PP^{n-1}$-bundle. Then $H^*(\PP(\xi))$ is a free $H^*(B)$-module on generators $1,e,e^2,\ldots,e^{n-1}$, where $e\in H^*(\PP(\xi))$ is the Euler class of the tautologous line bundle $L\downarrow \PP(\xi)$.

For each $x\in B$, let $F_x$ be the fiber above $x$, and let $L_x$ be the restriction of $L$ to that fiber. Thus $L_x$ is the tautologous line bundle over $F_x$, and $H^*(F_x)$ is generated by the euler class $e(L_x)=e|_{F_x}$. Thus the coefficient system is trivial. Moreover, the homomorphism $H^*(\PP(\xi))\to H^*(F)$ is surjective, where $F$ is the fiber over the basepoint of $B$.

Consider now the fibration $F \rightarrow\PP(\xi)\downarrow B$. The transgression is defined on all of $H^*(F)$, as we have the following diagram which describes the transgression:
\[\xymatrix{
H^*(\PP(\xi))\ar@{->>}[r]&H^*(F)\ar[r]^{0\ \ \ \ \ }&H^{*+1}(\PP(\xi),F)&E_\infty^{*+1,0}\\
&E_\infty^{0*}\ar@{^{(}->}[u]\ar@{.>}[rur]&H^{*+1}(B,*)\ar[u]\ar[r]&H^{*+1}(B)\ar@{->>}[u]
}\]
Moreover, this shows that $H^*(F)$ consists only of permanent cycles, so the Serre Spectral Sequence collapses at $E_2$. Thus the $E_\infty$ is a free $H^*(B)$-module, compatibly with the filtering on $B$, so that $H^*(\PP(\xi))$ is a free $H^*(B)$-module.

%To see this, c We should check first that the coefficient system $H^*(\PP(\xi)_x)$ on $B$ is trivial. It is enough to show that $\pi_1(B)$ acts trivially on $H^2(\PP(\xi))$, as each coefficient group is generated by $H^2$.



\myheading{A couple of applications of the Steenrod squares}
\textbf{Application 1:} we show that $\eta^2:S^2\to S^0$ is not stably null,
where $\eta$ is the Hopf fibration. Whenever we have a homotopy commuting
square, we can complete it to a larger grid with rows and columns cofiber
sequences. Note that we need to use the same choice of homotopy to induce the
two squiggly maps:
\[\xymatrix{
S^2\ar[r]^{\Sigma\eta}\ar[d]&S^1\ar[r]\ar[d]^\eta&\Sigma C\eta\ar@{~>}[d]\\
\text{$*$}\ar[r]\ar[d]&S^0\ar[r]\ar[d]&S^0\ar[d]\\
S^3\ar@{~>}[r]&C\eta\ar[r]^\beta&X\ar[d]^\gamma\\
&&\Sigma^2C\eta
}\]
Now it can be checked that $X$ has a cell in dimensions $0,2,4$. Moreover,
$\beta$ induces an isomorphism on $H^*(\DASH;\Z_2)$ for $*=0,2$, and gamma does
so for $*=2,4$. Thus if $\phi_0,\phi_2,\phi_4$ are the various generators, we
have $\Squ^2\phi_0=\phi_2$ and $\Squ^2\phi_2=\phi_4$. This contradicts the Adem
relation $\Squ^{22}=\Squ^{31}$.

\textbf{Application 2:}  let $M$ be the cofiber of the map $2:S^0\to S^0$ (of
spectra). We would like to see that $2\id_M:M\to M$ is not null. For this,
suppose that it is in fact null. Then, as $2\id_M=2\wedge\id_M$, we have
$C(2\id_M)=M\wedge M$.

Thus, to solve our problem, it is enough to check that $M\wedge M$ and $M\vee
\Sigma M$ have different $H^*(\DASH;\Z_2)$ (as $\Steen$-algebras). We calculate
first that $H^*(M;\Z_2)$ is $\Z_2$ in $*=0,1$. Thus $\Squ^2$ acts as zero on the
cohomology of $M\vee \Sigma M$. On the other hand, we can calculate directly
that $\Squ^2$ is nonzero on the base class in $M\wedge M$.



\myheading{The existence of an \texorpdfstring{$A$}{A}-Adams resolution}
In this note we indicate why $A$-Adams resolutions exist. The context is the
paper ``On relations between Adams spectral sequences'' by Haynes Miller, page
289.

Suppose that we have a chosen $A$-resolution $*\to X\to I^0\to I^1\to\cdots$ of
$X$. Suppose by induction on $s$ that we have a partial $A$-Adams resolution of
length $s$:
\[\xymatrix@C=.1cm{
&X^{s-2}\ar[dr]&&X^{s-1}\ar[dr]\ar[ll]&&X^s\ar[ll]\\
&&\Sigma^{s-2}I^{s-2}\ar@{-->}[rr]\ar@{-->}[ur]
&&\Sigma^{s-1}I^{s-1}\ar@{-->}[rr]\ar@{-->}[ur]&&\Sigma^{s}I^{s}
}\]
The dashed maps lower degree by one, in the sense that their target is the
desuspension of what is shown in the diagram. The bottom row should be the
resolution of $X$ (and $X=X_0\to I^0$ should be the initial map in the
resolution). Moreover, the sequences $*\to X^i\to\Sigma^iI^i\to\Sigma
X^{i+1}\to*$ should be $A$-exact, and of course, the top triangles must be
extended (co)-fiber sequences, and the bottom triangles should commute.

It is enough to show that there is a map $X^s\to \Sigma^sI^s$ making the
rightmost triangle commute, and to demonstrate that this map is $A$-monic. For
then, by lemma 1.5, we can define $X^{s+1}$ to be the fiber of this map. For
existence, we do a little diagram chasing:
\[\xymatrix{
\bullet\ar[rd]_5\ar[rrrrrd]_3&&\bullet\ar[rrrd]^1\ar[ll]_4&&\bullet\\
&\bullet\ar[ru]_2\ar@/_.31pc/[rrrr]^(.3){6}&&\bullet&&\bullet
}\]
The map exists iff the composite $1$ is null, by exactness in the upper right
triangle. Now $1\circ2$ is null, so that there exists a map $3$ such that
$1=3\circ4$. The map $5$ is $A$-monic, and the target is $A$-injective, so that
there exists a map $6$ such that $3=6\circ5$. Then $1=6\circ5\circ4$, and
$5\circ4$ is null.

To check that the map is $A$-monic, now that it is known to exist, we map
everything into an arbitrary $A$-injective object $I$, giving the following
purely algebraic situation (where numbers represent homsets), in which the
bottom row is exact, both triangles commute, and the middle vertical map is
injective:
\[\xymatrix{
&&&2\ar[lldl]_0\ar@{^{(}->}[ld]\\
3&&\ar[ll]4&&1\ar[ll]\ar[lu]_{\text{epi?}}
}\]
Now anything in $2$ maps to zero in 3, so $\im(2\to4)\subseteq\im(1\to4)$ by
exactness of the bottom row. Yet then, as $2\to4$ is monic, $1\to2$ is epic.



\myheading{The definition of an abelian category}
\noindent A category is \emph{additive} if:
\begin{itemise}
\itm the homsets are abelian groups, and composition is biadditive;
\itm there is a zero object; and
\itm finite biproducts exist.
\end{itemise}
A category is \emph{pre-abelian} if:
\begin{itemise}
\itm it is additive; and
\itm every morphism has a kernel and a cokernel
\end{itemise}
A category is \emph{abelian} if:
\begin{itemise}
\itm it is pre-abelian; and
\itm every monomorphism is normal and every epimorphism is conormal. That is,
every monomorphism is a kernel, and every epimorphism is a cokernel. This agrees
with the meaning of the term `normal subgroup'.
\end{itemise}
\myheading{\texorpdfstring{$\Q$ and $\C$ are flat $\Z$-modules}%
{Q and C are flat Z-modules}}
Alternative definition: a flat $R$-module is an $R$-module $M$ such that for
every finitely generated ideal $I\subseteq R$, the induced morphism $I\otimes_R
M\to R\otimes_R M=M$ is injective.

If $R=\Z$ and $M=\Q$, we need to check $I=n\Z$ for any $n\in\Z$. If $n\neq\pm1$,
the induced morphism is $0\to\Q$, otherwise it is $\Q\to\Q$. Thus $\Q$ is flat.
To tensor with $\C$ over $\Z$, we may first tensor with $\Q$ over $\Z$ then with
$\C$ over $\Q$. As $\C$ is a free $\Q$-module, it is flat over $\Q$. As 
$A\otimes_{\Z}\C=A\otimes_{\Z}\Q\otimes_{\Q}\C$, $\C$ is flat over $\Z$.

%\myheading{\texorpdfstring{$\Z$}{Z} is not algebraically compact} Suppose that
%$\Z$ were topologised as a compact topological group. Then the sequences
%$\{n\}$ and $\{n+1\}$ would have limit points $k$ and $k+1$

\myheading{\texorpdfstring{$K(\pi,n)$ represents $H^n(\DASH;\pi)$}%
{Eilenberg-MacLane spaces represent ordinary cohomology}}
By Brown representability, $H^n(\DASH;\pi)$ is representable by some space $K$.
Since $\pi_i(K)=[S^i,K]=H^n(S^i;\pi)$, $K$ is a $K(\pi,n)$.
\end{document}













