% !TEX root = z_output/_PRLieAlgs.tex
\documentclass[10pt]{article}
\newcommand{\NOFULLPAGE}{\relax}
\input{../../Dropbox/logbook/_LOGBOOK/macros.tex}
\excludeversion{Omitted}
%\excludeversion{SkippableProofs}


\excludeversion{AdamsDerivation}
%\def\excludeversion#1{\includeversion{#1}}
\excludeversion{Frontmatters}
\excludeversion{Endmatter}
\excludeversion{SteenrodAlgebrasAndTheirKoszulDuals}
\includeversion{CategoriesOfInterest}
\excludeversion{DiagramOfFunctors}
\excludeversion{GrothendieckSpectralSequences}
\excludeversion{KoszulComplexes2plus}
\excludeversion{KoszulComplexes1}
\excludeversion{DerivedFunctorsLowDimension}
\excludeversion{PRlieKoszulComplexCalculation}
\excludeversion{LieLambdaStructureOnKoszul}
\excludeversion{SequenceOfSequencesIntro}
\excludeversion{KoszulSequenceCombinatorics}
\excludeversion{CalculatingRepeatedKoszul}
\excludeversion{DimZeroPart}
\excludeversion{VanishingLines}
\excludeversion{TotalisationInSAlg}

\newcommand{\GS}[1]{\scrE^{#1}}
\newcommand{\GpS}[1]{\scrE^{#1}_\star}
\renewcommand{\Set}{Set}

\newcommand{\RestLie}[1]{\mathsf{r}{\scrL}^{#1}}%{{\mu\scrL}^{#1}}
\newcommand{\GoodLie}[1]{\mathsf{g}{\scrL}^{#1}}%{{\mu\scrL}^{#1}}
\newcommand{\BadLie}[1]{\mathsf{b}{\scrL}^{#1}}%{{\mu\scrL}^{#1}}
\newcommand{\PRLie}[1]{\scrR^{#1}}%{{\xi\scrL}^{#1}}

\newcommand{\LL}[1]{{\scrK}^{#1}}%{{\mu\scrL}^{#1}}
\newcommand{\GR}[1]{\scrV^{#1}}%{\mathsf{gr}^{#1}}
\newcommand{\nontop}[1]{\scrU^{#1}}%{\mu_{\mathsf{nt}}^{#1}}
\newcommand{\PiAlg}[1]{#1\textup{-$\Pi$-alg}}
\newcommand{\produces}[3]{{#1}{#3}{#2}}

\newcommand{\admis}[1]{\mathrm{adm}(#1)}%{{\mu\scrL}^{#1}}

\newcommand{\iteratedrestn}[2]{\xi^{#2}{#1}}
\newcommand{\Ind}[2][]{\mathbf{I}{#2}_{#1}}%[internal indices]{category name}
\newcommand{\forget}{\mathrm{fg}}
\newcommand{\Fr}[2][]{\ifblank{#1}{#2}{#2_{#1}}}
\newcommand{\restn}[2][]{\ifblank{#1}{\xi{#2}}{\xi_{#1}{#2}}}%{\xi{#1}}



\newcommand{\derived}{\mathbb{L}}
%\newcommand{\LambdaOp}{Q}
\renewcommand{\Q}{Q}
\newcommand{\SqShift}{\Sq_{+}}
\newcommand{\Sq}{\mathrm{Sq}}
\newcommand{\Comm}{\calC}
\newcommand{\LieSteen}{\calA(\calL)}
\newcommand{\CommSteen}{\calA(\Comm)}
\newcommand{\deltaAlgebra}{\Delta}
\newcommand{\DyerLashov}{R}

\newcommand{\minDim}{m}
\newcommand{\minDimP}{\overline{m}}
\newcommand{\BarMonomial}[3]{\textup{mon}_{#1,#2,#3}}

\newcommand{\Shuffles}[2]{\textup{Sh}_{#1#2}}
\newcommand{\HalfShuffles}[2]{\textup{Sh}_{#1#2}/2}

\renewcommand{\produces}[3]{
{
\def\labelstyle{\scriptstyle}
\xymatrix@C=2em@1{
{#1}
\ar@{-}[r]|-{{\,#3\,}}
&%r1c1
{#2}%r1c2
}}}





\bibliography{../../Dropbox/logbook/_LOGBOOK/papers}
\begin{document}
\begin{Frontmatters}
\tableofcontents\newpage
\end{Frontmatters}


\begin{AdamsDerivation}
\section{The Adams Spectral sequence for commutative $\F_2$-algebras}
Let $\Comm$ be the category of augmented commutative $\F_2$-algebras. For $X\in \Comm$, one defines:
\[IX:=\ker(\epsilon:X\to\F_2)\subset X\textup{\quad and\quad }QX:=IX/(IX)^2.\]
Then the functor $Q:\Comm\to\Vect$ admits a right adjoint $K:\Vect\to\Comm$ defined by $V\mapsto \F_2\oplus V$, with multiplication characterised by $V^2=0$.

An analysis (see \cite[\S4]{MR1089001}) of the category of abelian objects in $s\Comm$ reveals that the abelian objects of are precisely the image of $K$, and the prolongation $Q:s\Comm\rightleftarrows s\Vect:K$ of the above adjunction models the adjunction between `abelianization' and `the inclusion of the abelian objects'. Thus we define the Quillen homology $H_*^Q(X_{\bullet})$ of $X_{\bullet}\in s\Comm$ to be $\mathbb{L}_*Q(X_{\bullet}):=\pi_*Q(cX_\bullet)$, where $c$ denotes a cofibrant replacement in $s\Comm$.





\subsection{A Bousfield-Kan construction in $s\Comm$}
In \cite{MR0365573}, Bousfield and Kan construct, for a space (i.e.\ simplicial set) $X$, the $\F_2$-completion $\check X$ to be the totalisation of the cosimplicial resolution of $X$ arising from the monad of the adjunction $\F_2:s\Set_*\rightleftarrows s\Vect:\forget$. By virtue of $\check X$ having been constructed as a totalisation, there is a totalisation spectral sequence converging to $\pi_*(\check X)$. This is known as the unstable Adams spectral sequence for $X$.

As pointed out by Blumberg and Riehl in \cite{BlumRiehlResolutions.pdf}, this process is aided by the fact that the construction of $\check X$ is homotopically well behaved --- in $s\Set_*$, all objects are cofibrant, and in $s\Vect$, all objects are fibrant, so that the monad of the adjunction preserves weak equivalences, and fortunately, the Bousfield-Kan tower is already Reedy fibrant.

In our context, the right adjoint in $Q:s\Comm\rightleftarrows s\Vect:K$ fails to land in the subcategory of cofibrant simplicial algebras. In order to remedy this, Blumberg and Riehl show how to mix appropriate cofibrant replacements into the iteration of the monad\footnote{As every object of $s\Vect$ is fibrant, we need not mention a monadic fibrant replacement on that category, although there is no such asymmetry in the treatment of \cite{BlumRiehlResolutions.pdf}.}. That is, they show that if one can choose a functorial cofibrant replacement $c$ on $\ensuremath{s\calA}$ which additionally has structure of a homotopical comonad, then one can give a homotopically correct cosimplicial resolution of the type we desire. Writing $\overline{Q}$ for $Qc:s\Comm\to s\Vect$, their resolution takes the form:
\[
\vcenter{
\def\labelstyle{\scriptstyle}
\xymatrix@C=1.5cm@1{
cX_\bullet\,
\ar[r]
&
\,cK\overline{Q}X_\bullet\,
\ar[r];[]
&
\,c(K\overline{Q})^2X_\bullet\,
\ar@<-1ex>[l];[]
\ar@<+1ex>[l];[]
\ar@<+1ex>[r];[]
\ar@<-1ex>[r];[]
&
\,c(K\overline{Q})^3X_\bullet\,
\ar[l];[]
\ar@<-2ex>[l];[]
\ar@<+2ex>[l];[]
\ar[r];[]
\ar@<+2ex>[r];[]
\ar@<-2ex>[r];[]
&
\,c(K\overline{Q})^4X_\bullet\,\makebox[0cm][l]{\,$\cdots $}
\ar@<-3ex>[l];[]
\ar@<-1ex>[l];[]
\ar@<+1ex>[l];[]
\ar@<+3ex>[l];[]
}}\]
%For $X\in\Comm$, write $\underline{X}_\bullet^\bullet$ for the cosimplicial object $c(K\overline{Q})^\bullet A$.
The Blumberg-Riehl approach augments Bousfield's work on cosimplicial resolutions \cite{BousCosimpResnHtpySS.pdf},  allowing us to define a homotopical `derived completion' endofunctor on $\Comm$ by $X_\bullet\mapsto\hat X_\bullet:=\textup{Tot}((c(K\overline{Q})^\bullet X_\bullet)^{\textup{rf}})$, where `$\textup{rf}$' denotes a Reedy fibrant replacement.

Bousfield shows how to obtain a spectral sequence $\pi^s\pi_t(\underline{X}^\bullet;S^0)\Rightarrow\pi_{t-s}(\hat X;S^0)$ by applying the well established Bousfield-Kan spectral sequence to the evident cosimplicial space of Dwyer-Kan mapping complexes. It serves our purposes best to dualize, and rewrite:
\[\pi_s\pi^t((I(c(K\overline{Q})^\bullet X)^{\textup{rf}})^*)\Rightarrow \pi^{t-s}((I\hat X)^*)\]
A complete derivation would at this point include a detailed examination of the dual Hurewicz homomorphism $H^*_Q(X)\to \pi^*((IX)^*)$, in particular when $X$ is an abelian object. One shows that:
\begin{prop*}
When $H^*_Q(X)$ is of finite type (for example when $X$ is connected and of finite type) the spectral sequence has $E_2^{st}=(\mathbb{L}_s\textup{Ind}_\calW)(H_Q^*X)^t=(\Ext^s_{\calW}(H_Q^*X,H_Q^*S^t))^*$.
\end{prop*}


\end{AdamsDerivation}

\begin{SteenrodAlgebrasAndTheirKoszulDuals}
\section{Some homogeneous Koszul algebras}
In what follows, we will make heavy use of four algebras, each of which is a `homogeneous Koszul algebra' in the sense of \cite{PriddyKoszul.pdf}. The algebras of interest are the following:
\begin{enumerate}\squishlist
\setlength{\parindent}{.25in}
\item The Steenrod algebra for simplicial commutative algebras, $\CommSteen$, with generators $P^i$ for $i\geq2$, subject to relations:
\[P^iP^jx=\sum_{s=i-j+1}^{i+j-2}{2s-i-1\choose s-j}P^{i+j-s}P^sx\textup{ for $i\geq2j$}.\]
That this is in fact a description of $\CommSteen$ follows from Goerss' determination \cite[p.14]{MR1089001} of the cohomology of Eilenberg-Mac Lane objects in simplicial augmented commutative $\F_2$-algebras.

\item The ``$\Delta$-algebra'' $\deltaAlgebra$, with generators $\delta_i$ for $i\geq2$, subject to relations:
\[\delta_i\delta_j:=\sum_{s=(i+1)/2}^{(i+j)/3}{j+s-i-1\choose j-s}\delta_{i+j-s}\delta_s\textup{ for $i<2j$.}\]
\item The Steenrod algebra for simplicial restricted Lie algebras, $\LieSteen$, with generators $\SqShift^i$ for $i\geq0$, subject to relations:
\[\SqShift^i\SqShift^j=\sum_{k=0}^{(i-1)/2}{j-k-1\choose i-2k-1}\SqShift^{i+j-k}\SqShift^k\textup{\ for $i\leq2j$.}\]
According to \cite[\S7]{PriddySimplicialLie.pdf}, $\LieSteen$ is the quotient of the standard Steenrod algebra by the two-sided ideal generated by $\Sq^0$, and our description follows after introducing the notation $\SqShift^i:=\Sq^{i+1}$.
%
%This algebra acts on the Andr\'e-Quillen cohomology of restricted Lie algebras, as follows. For $\frakg$ a simplicial Lie algebra,

\item The Dyer-Lashov algebra $\DyerLashov$, with generators $\Q^i$ for $i\geq0$, subject to relations:
\[\Q^i\Q^j=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}\textup{\ for $i>2j$.}\]
This algebra is the opposite of the $\Lambda$-algebra, under an anti-isomorphism defined by $Q^i\longleftrightarrow \lambda_i$.
\end{enumerate}
\subsection{Unstable actions on homotopy and Quillen cohomology}
In what follows, let $A$ be a simplicial augmented commutative $\F_2$-algebra $A$, and let $\frakg$ be a simplicial restricted Lie algebra over $\F_2$.

\subsubsection{$\CommSteen$ acting on the cohomology of $\F_2$-algebras}
%The Andr\'e-Quillen cohomology groups $H^*_Q(A)$ of a simplicial $\F_2$-algebra $A$ support the following structure:
\begin{enumerate}\squishlist
\setlength{\parindent}{.25in}
\item $H^*_Q(A)$ is a (bad) Lie algebra, under a bracket $H^i_Q(A)\otimes H^j_Q(A)\to H^{i+j+1}_Q(A)$; the structure is restricted in dimension zero (via $\beta:H^0_Q(A)\to H^1_Q(A)$), good in dimension 1, and bad otherwise;
\item $H^*_Q(A)$ is a graded left $\CommSteen$-module, so that there are operations $P^i:H^n_Q(A)\to H^{n+i+1}_Q(A)$, defined for all $n\geq0$ and $i\geq2$, but zero when $i>n$. These operations satisfy the $P$-Adem relations.
\item Every operation $P^i$ is linear, including the top operation $P^n:H^n_Q(A)\to H^{2n+1}_Q(A)$, which equals the self-bracket:  $P^nx=[x,x]$ if $|x|=n$.
\item The $P$ operations satisfy the following Cartan formula:
$[x,P^iy]=0$.
\end{enumerate}

\subsubsection{$\LieSteen$ acting on the cohomology of restricted Lie algebras}
%The Andr\'e-Quillen cohomology groups $H^*_Q(\frakg)$ of $\frakg$ support the following structure:
\begin{enumerate}\squishlist
\setlength{\parindent}{.25in}
\item $H^*_Q(\frakg)$ is a commutative algebra without unit, under a cup product $H^i_Q(\frakg)\otimes H^j_Q(\frakg)\to H^{i+j+1}_Q(\frakg)$;
\item $H^*_Q(\frakg)$ is a graded left $\LieSteen$-module, so that there are operations $\SqShift^i:H^n_Q(\frakg)\to H^{n+i+1}_Q(\frakg)$, defined for all $n\geq0$ and $i\geq0$, but zero when $i>n$. These operations satisfy the $\SqShift$-Adem relations.
\item Every operation $\SqShift^i$ is linear, including the top operation $\SqShift^n:H^n_Q(A)\to H^{2n+1}_Q(A)$, which equals the squaring operation:  $\SqShift^nx=x^2$ if $|x|=n$.
\item The $\SqShift$ operations satisfy the following Cartan formula:
\[\SqShift^k(x\cdot y)=\sum_{k'+k''=k-1}\SqShift^{k'}(x)\cdot \SqShift^{k''}(y).\]
\end{enumerate}

\subsubsection{$\Delta$ operations on the homotopy of $\F_2$-algebras}
%The homotopy groups $\pi_*(A)$ of $A$ support the following structure:
\begin{enumerate}\squishlist
\setlength{\parindent}{.25in}
\item $\pi_*(A)$ is a commutative algebra under a product $\pi_i(A)\otimes \pi_j(A)\to \pi_{i+j}(A)$; it is exterior in dimension 1, and it is a divided power algebra in dimensions 2 and above;
\item there are operations $\delta_i:\pi_n(A)\to \pi_{n+i}(A)$, defined only for $2\leq i\leq n$. 
As the operations $\delta_i$ are only partially defined, $\pi_*(A)$ does \emph{not} become a left module over the $\Delta$-algebra.
 However, when these operations are written on the left, they satisfy the $\delta$-Adem relations whenever one can be applied.
\item The non-top operations, $\delta_i:\pi_n(A)\to \pi_{n+i}(A)$ for $i<n$, are linear. The top operation, $\delta_n:\pi_n(A)\to \pi_{2n}(A)$ equals the divided square, and is thus quadratic:
\[\textup{if $|x|=|y|=n\geq2$, then }\delta_n(x)=\gamma_2(x)\textup{ and }\delta_n(x+y)=\delta_n(x)+\delta_n(y)+xy.\]
\item The $\delta$ operations satisfy the following Cartan formula:
\[\delta_i(xy)=\begin{cases}
x^2\delta_i(y),&\textup{if }|x|=0\textup{ and }|y|\geq2;\\
y^2\delta_i(x),&\textup{if }|y|=0\textup{ and }|x|\geq2;\\
0,&\textup{otherwise}.
%\\,&\textup{if }
\end{cases}
\]
\end{enumerate}
\subsubsection{$\Q$ operations on the homotopy of restricted Lie algebras}
%The homotopy groups $\pi_*(\frakg)$ of $\frakg$ support the following structure:
\begin{enumerate}\squishlist
\setlength{\parindent}{.25in}
\item $\pi_*(\frakg)$ is a restricted Lie algebra under a bracket $\pi_i(\frakg)\otimes \pi_j(\frakg)\to \pi_{i+j}(\frakg)$;
\item there are operations $\Q^i:\pi_n(\frakg)\to \pi_{n+i}(\frakg)$, defined only for $0\leq i\leq n$. As the operations $\Q^i$ are only partially defined, $\pi_*(\frakg)$ does \emph{not} become a left module over the Dyer-Lashov algebra. However, when these operations are written on the left, they satisfy the $\Q$-Adem relations whenever one can be applied.
\item The non-top operations, $\Q^i:\pi_n(\frakg)\to \pi_{n+i}(\frakg)$ for $i<n$, are linear. The top operation, $\Q^n:\pi_n(\frakg)\to \pi_{2n}(\frakg)$ equals the restriction, and is thus quadratic:
\[\textup{if $|x|=|y|=n\geq0$, then }\Q^n(x)=\restn{x}\textup{ and }\Q^n(x+y)=\Q^n(x)+\Q^n(y)+[x,y].\]
\item The $\Q$ operations satisfy the following Cartan formula. For $|x|\leq |y|$:
\[[\Q^i(x),y]=\begin{cases}
[x,[x,y]],&\textup{if }i=|x|;\\
0,&\textup{otherwise}.
%\\,&\textup{if }
\end{cases}
\]
\end{enumerate}

Note that it is not immediately obvious that the $\delta$-Adem ($\Q$-Adem) relations are well defined when viewed as relations that hold between operations on the homotopy of commuatative algebras (Lie algebras). That is, we are supposed to have $\Q^i\Q^jx=\cdots $ whenever $i>2j$ and $\Q^i\Q^jx$ is defined, but we haven't checked that every term in the right hand side is defined. This does indeed happen, by a lemma to follow. 

\subsection{The combinatorics of admissible sequences}

Now each of these algebras, being homogeneous, is bigraded%footnote:
\footnote{I'm not sure what the point is in bigrading things, really, but there's some cool stuff happening. For example, if you make $P$ act on something that's only singly graded, it makes sense to demand that degrees change via the associtated singly graded algebra, in which $|P^i|=i+1$, and viewing $P$ as bigraded makes the unstable condition seem more natural. Moreover, whenever you see a $\delta_j$ in this context, it does change internal degree by $i$, and homological degree by $1$. What it does to deeper degrees is just spooky. I guess the same thing holds for $\SqShift^i$, which is intense, given that it equals $\Sq^{i+1}$! I don't know.}, setting (\textbf{I guess}) 
\[\|P^i\|=\|\delta_i\|=\|\SqShift^i\|=\|\Q^i\|=(1,i).\]
Now let $b$ be any of the symbols $P$, $\delta$, $\SqShift$, or $\Q$. For a sequence $I=(i_{\ell},\ldots,i_1)$ of positive integers (with $i_j\geq2$ if $b$ is $P$ or $\delta$), write $b^I$ for the product $b^{i_\ell}\cdots b^{i_1}$. Say that $I$ is $b$-admissible if no $b$-Adem relations can be applied directly to $b^I$, so that one of the four evident inequalities hold between adjacent indices in $I$.
\begin{lem*}
All of the Adem relations listed above express the inadmissible length 2 sequence on the left hand side as a sum of admissible length 2 sequences. All four of the algebras are homogeneous Koszul algebras. The algebras $\CommSteen$ and $\Delta$ are Koszul dual, under $P^i\longleftrightarrow\delta_i$. The algebras $\LieSteen$ and $R$ are Koszul dual, under $\SqShift^i\longleftrightarrow\Q^i$. In particular, for length 2 sequences $K$ and $L$:
\[\produces{K}{L}{P}\iff\produces{L}{K}{\delta}\textup{ \ and \ }\produces{K}{L}{\SqShift}\iff\produces{L}{K}{\Q}\]

\end{lem*}
\begin{proof}
The first statement is checked manually from the Adem relations in each case.

Priddy's PBW stuff, along with the fact that none of the above Adem relations do any more than expected, shows that everything is Koszul. To check that the algebras are indeed Koszul dual to each other, one just looks closely at the Adem relations and checks the above `$\iff$' statements
\end{proof}
Thus, for all four of these algebras, the $b$-Adem relations can be used iteratively to write any expression as a sum of terms $b^I$ with $I$ $b$-admissible. We'll write $\produces{I}{J}{b}$ if $I\neq J$, and when $b^I$ is written as a sum of $b$-admissible expressions, $b^J$ appears therein (an odd number of times). Trivially, if $\produces{I}{J}{b}$, then $J$ is $b$-admissible, and $I$ is $b$-inadmissible.

It will be important to have a criterion for when $\delta_Ix$ is defined for an element $x\in\pi_*(A)$, or when $P^Ix$ can be nonzero, for $x\in H^*_Q(A)$, etc.
To answer such questions, we make the following two definitions. For $I=(i_\ell,\ldots,i_1)$ a sequence of nonnegative integers, we define
\[\minDim(I):=\begin{cases}
-\infty,&\textup{if }I=\emptyset;\\
\max\{(i_1),\,(i_2-i_1),\,\ldots,\,(i_{\ell}-i_{\ell-1}-\cdots -i_1)\},&\textup{otherwise};
%\\,&\textup{if }
\end{cases}
\]
\[\minDimP(I):=\begin{cases}
-\infty,&\textup{if }I=\emptyset;\\
\max\{(i_1),\,(i_2-i_1-1),\,(i_3-i_2-i_1-2),\,\ldots,\,(i_{\ell}-\cdots-i_1-\ell+1)\},&\textup{otherwise}.
%\\,&\textup{if }
\end{cases}
\]
If $I=(i_{\ell},\ldots,i_1)$ with all $i_j\geq2$, then:
\begin{itemize}
\setlength{\parindent}{.25in}
\item $P^Ix$ can be nonzero for $x\in H^n_Q(A)$ iff $\minDimP(I)\leq n$
\item $\delta_Ix$ is defined for $x\in \pi_n(A)$ iff $\minDim(I)\leq n$
\end{itemize}
If $I=(i_{\ell},\ldots,i_1)$ with all $i_j\geq0$, then:
\begin{itemize}
\setlength{\parindent}{.25in}
\item $\SqShift^Ix$ can be nonzero for $x\in H^n_Q(\frakg)$ iff $\minDimP(I)\leq n$
\item $\delta_Ix$ is defined for $x\in \pi_n(\frakg)$ iff $\minDim(I)\leq n$
\end{itemize}

%With this notation in hand, we may finally discuss whether or not the Adem relations that the $\delta$ operations and and $\Delta$ are well defined.
\begin{lem*}
In the following statements, $K$ and $L$ are each length 2 sequences:%, with entries nonnegative in cases (i) and (ii), and entries at least 2 in cases (iii) and (iv).
%
%In the following statements, $K=(i,j)$ and $L=(i',j')$ are to be two length 2 sequences, with entries nonnegative in cases (i) and (ii), and entries at least 2 in cases (iii) and (iv).
\begin{enumerate}[i)]
\setlength{\parindent}{.25in}
\item Suppose that $\produces{K}{L}{\Q}$. Then $\minDim(L)<\minDim(K)$, and $L$ has positive entries.
%\item Suppose that $\produces{K}{L}{\SqShift}$. Then $\minDim(L)>\minDim(K)$, and $K$ has positive entries. (shrug)
\item Suppose that $\produces{K}{L}{P}$. Then $\minDimP(L) > \minDimP(K)$.
%\item Suppose that $\produces{K}{L}{\delta}$. Then $\minDimP(L) < \minDimP(K)$. (shrug)
\end{enumerate}
In (ii), the entries of $K$ and $L$ should be at least 2.
\end{lem*}
\begin{proof}
In both of the proofs, let $K=(i,j)$ and $L=(i',j')$.

For (i), we wish to show that $\max\{j',i'-j'\}<\max\{j,i-j\}$, but we must have that $i'\leq 2j'$, and $i>2j$. Thus, we need only show that $j'<i-j$, but this is immediate from the indexing of the Adem relation. That $L$ has positive entries is also immediate.

For (ii), we wish to show that $\max\{j',i'-j'-1\}>\max\{j,i-j-1\}$, but we must have that $i'> 2j'$, and $i\geq2j$. Thus $\max\{j,i-j-1\}$ at most $i-j$ (which happens when $i=2j$). Thus, we need only show that $j'>i-j$; again, easy.
\end{proof}
%\begin{lem*}
%Suppose that %$i>2j$, and 
%$\produces{(i,j)}{(i',j')}{\Q}$. Then $\minDim(i,j)>
%\minDim(i',j')$, and $i',j'>0$.
%
%In particular, if $\Q^i\Q^jx$ is defined, and $i>2j$, it can be rewritten as a sum of terms $\Q^{i'}\Q^{j'}x$ in which neither of the $\Q^{i'}$ and $\Q^{j'}$ that appear are top operations.
%\end{lem*}
%\begin{proof}
%It must be that $(i,j)$ is $\Q$-inadmissible, so that $i>2j$. Then,
%by inspection, $i>j+i/2\geq i'\geq2j+1$, and $i-j-1\geq j'\geq i/2>j$. These inequalities demonstrate (i). For (ii), note that (i) shows that we needn't worry about $\Q^0$ failing to be defined, as it won't appear. Our only concern is that either $i'$ or $j'$ will be too large. Suppose then that $\Q^i\Q^j$ is defined on an $n$-dimensional class, so that $j\leq n$ and $i\leq n+j$. Then one notes that $j'\leq i-j-1\leq n-1$, and $i'-j'\leq (j+i/2)-(i/2)<i/2\leq(n+j)/2\leq n$. The first chain gives $j'\leq n-1$, and the second $i'\leq n-1+j'$, as the quantities involved are integers. These inequalities demonstrate (ii) and the final comment.
%\end{proof}
%
%\begin{lem*}
%Suppose that $\produces{(i,j)}{(i',j')}{P}$. Then $\minDimP(i',j') > \minDimP(i,j)$.
%\end{lem*}
%\begin{proof}
%Since $i\geq2j$, 
%$j'\geq i-j+1=
%j+(i-2j+1)=
%i-j-1+(2)
%$, so that $j'>\max\{j,i-j-1\}$.
%\end{proof}


%
%\subsection{The Steenrod algebra for simplicial Lie algebras and its Koszul dual}
%Let  $\LieSteen$ be the Steenrod algebra for simplicial restricted Lie algebras \cite[\S7]{PriddySimplicialLie.pdf}. This is the quotient of the standard Steenrod algebra by the two-sided ideal generated by $\Sq^0$. We'll introduce the notation $\SqShift^i:=\Sq^{i+1}$, so that $\LieSteen$ is generated by $\SqShift^i$ for $i\geq-1$, subject to relations:
%\[\SqShift^{-1}=0\textup{ and }\SqShift^i\SqShift^j=\sum_{k=0}^{(i-1)/2}{j-k-1\choose i-2k-1}\SqShift^{i+j-k}\SqShift^k\textup{\ for $i\leq2j$.}\]
%This is a homogeneous Koszul algebra in the sense of \cite{PriddyKoszul.pdf}. Its cohomology algebra $H^*\LieSteen:=\Ext_{\LieSteen}^{**}(\F_2,\F_2)$ is also a homogeneous Koszul algebra, generated by the $\Q^i$ for $i\geq0$, where $\Q^i$ is dual to $\SqShift^i$ \cite[\S8]{PriddySimplicialLie.pdf}. These classes satisfy their own Adem relations%footnote:
%\footnote{Compare with \cite[p.143]{Miller-infDeloopSS.pdf}, and May-Cohen-Lada page 9.}:
%\[\Q^i\Q^j=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}\textup{\ for $i>2j$.}\]
%Importantly, $H^*\LieSteen$ is isomorphic to the opposite of the $\Lambda$-algebra, and $\Q^i\longleftrightarrow\lambda_i$ under this anti-isomorphism. While it is not precisely true that the $\Lambda$-algebra has an unstable right action on the homotopy of any simplicial Lie algebra, there are various $\lambda$ operators acting thereupon, satisfying the Adem relations in the $\Lambda$-algebra when written on the right \cite[Prop 8.6]{CurtisSimplicialHtpy.pdf}. We prefer to think of this as a left action of various $\Q$ operators, in order to simplify notation. Details to follow.
%
%\subsection{The Steenrod algebra for simplicial commutative algebras and its Koszul dual}
%It follows from Goerss' determination \cite[p.14]{MR1089001} of the cohomology of Eilenberg-Mac Lane objects in simplicial augmented commutative $\F_2$-algebras that the corresponding Steenrod algebra, $\CommSteen$ may be described thus.
%Let $\CommSteen$ be the algebra generated by $P^i$ for $i\geq0$ subject to relations:
%\[P^0=0,\ P^1=0\textup{ and }P^iP^jx=\sum_{s=i-j+1}^{i+j-2}{2s-i-1\choose s-j}P^{i+j-s}P^sx\textup{ for $i\geq2j$}.\]
%The Quillen cohomology of a simplicial augmented $\F_2$-algebra has an unstable left action of this algebra. This is also a homogeneous Koszul algebra, as is its cohomology algebra $H^*\CommSteen=\deltaAlgebra$. The algebra $\Delta$ is generated by classes $\delta_i$ dual to $P^i$ for $i\geq 2$. These classes satisfy the following $\delta$-Adem relation:
%\[\delta_i\delta_j:=\sum_{s=(i+1)/2}^{(i+j)/3}{j+s-i-1\choose j-s}\delta_{i+j-s}\delta_s\textup{ for $i<2j$.}\]
%It is again not precisely true that $\deltaAlgebra$ acts on the homotopy of simplicial commutative algebras. There are, however, various $\delta$ operations acting on the homotopy of a simplicial commutative algebra, and they satisfy the $\delta$-Adem relation wherever it makes sense.
\end{SteenrodAlgebrasAndTheirKoszulDuals}

\begin{CategoriesOfInterest}
\section{Categories of interest}
In the following subsections we detail a number of algebraic categories relevant to our study.
\subsection{Categories of graded sets and vector spaces}
\begin{itemize}
\setlength{\parindent}{.25in}
\item For $n\geq1$, let $\GpS{n}$ be the category of $n$-times non-negatively graded pointed sets%footnote:
\footnote{The question `what should be the domain category for our free/forget adjunctions' is probably only relevant when using Dold to prove something about PR Lie homology. Once you've done PBW you're fine, and can show that U preserves weak equivalences.} $X$ whose graded part $X_{a_n,\ldots,a_1}$ is a single point whenever $a_1=0$. That is, an object $X\in\GpS{n}$ is a collection $X_{a_n,\ldots,a_1}$ of pointed sets, one for each $n$-tuple $(a_n,\ldots,a_1)$ of non-negative integers, such that $X_{a_n,\ldots,a_2,0}=\{\star\}$ for all $a_n,\ldots,a_2$. For $x\in X_{a_n,\ldots,a_1}$, we write $|x|:=a_n$.
\item For $n\geq1$, let $\GS{n}$ be the category of $n$-times non-negatively graded sets $X$ whose graded part $X_{a_n,\ldots,a_1}$ is empty whenever $a_1=0$. For $x\in X_{a_n,\ldots,a_1}$, we write $|x|:=a_n$.

\item For $n\geq1$, let $\GR{n}$ be the category of $n$-times non-negatively graded $\F_2$-vector spaces $V$ such that $V_{a_n,\ldots,a_1}=0$ whenever $a_1=0$.  For a nonzero homogeneous element $v\in V_{a_n,\ldots,a_1}$, write $|v|:=a_n$.
\end{itemize}
All the categories $\mathsf{C}=\mathsf{C}^n$ to be defined below will consist of objects $X$ of $\GR{n}$ enriched with certain extra structure. For $y\in Y_{a_n,\ldots,a_1}$ a non-zero homogeneous element of $Y$, we will continue to write $|y|:=a_n$ in each of the following contexts.
Moreover, for any of the following categories there are free/forget adjunctions $\GS{n} \rightleftarrows \mathsf{C}$ and $\GpS{n} \rightleftarrows \mathsf{C}$. We'll denote either of these free functors simply by $X\mapsto\Fr{\mathsf{C}}(X)$.


\subsection{Categories of graded Lie algebras}

\begin{itemize}
\setlength{\parindent}{.25in}
\item For $n\geq1$, let $\BadLie{n}$ be the following category of $n$-graded Lie algebras over $\F_2$. An object of $\BadLie{n}$ is to be an object $L$ of $\GR{n}$ with (skew-)symmetric maps
\[[\DASH,\DASH]:L_{a_n,\ldots,a_1}\otimes L_{b_n,\ldots,b_1}\to L_{a_n+b_n,\ldots,a_2+b_2,a_1+b_1+1}\]
satisfying the Jacobi identity. Note that this Lie bracket has degree $(0,\ldots,0,1)$. As the ground field has characteristic 2, the concepts of symmetry and skew-symmetry coincide. More importantly, skew-symmetry does not imply the `alternating' relation, so that there may be $x\in L$ with $[x,x]$ nonzero. This explains the $\mathsf{b}$ in the notation --- we refer to such Lie algebras as \emph{bad} Lie algebras.

\item For $n\geq1$, let $\GoodLie{n}$ be the full subcategory of $\BadLie{n}$ consisting of those Lie algebras which are \emph{good}. That is, those $L\in\BadLie{n}$ for which $[x,x]=0$ for all $x\in L$.
\item For $n\geq1$, let $\RestLie{n}$ be the category of restricted Lie algebras in $\GoodLie{n}$. That is, an object of $\RestLie{n}$ is an object $L\in\GoodLie{n}$ along with `restriction' operations
\[\restn{}:L_{a_n,\ldots,a_1}\to L_{2a_n,2a_{n-1},\ldots,2a_2,2a_1+1}\]
which satisfy, for $x,y\in L_{a_n,\ldots,a_1}$ and $z\in L$: \[\restn{(x+y)}=\restn{(x)}+\restn{(y)}+[x,y]\textup{ and }[\restn{x},z]=[x,[x,z]].\]
\item For $n\geq1$, let $\PRLie{n}$ be the following category of partially restricted $n$-graded \emph{good} Lie algebras. An object of $\PRLie{n}$ consists is an object $L$ of $\GoodLie{n}$
%For $n\geq1$, let $\PRLie{n}$ be the following category of partially restricted $n$-graded Lie algebras. An object of $\PRLie{n}$ is a good Lie algebra $L=\bigoplus L_{a_n,\ldots,a_1}$, under a $(0,\ldots,0,1)$-shifted bracket as above
admitting restriction operations
\[\restn{}:L_{a_n,\ldots,a_1}\to L_{2a_n,2a_{n-1},\ldots,2a_2,2a_1+1}\]
defined whenever not all of $a_n,\ldots,a_{2}$ are zero. %The graded part $L_{a_n,\ldots,a_1}$ is assumed to be zero whenever $a_1=0$, and we write $|x|$ as above. 
For $x,y\in L_{a_n,\ldots,a_1}$ and $z\in L$ the restriction operations satisfy \[\restn{(x+y)}=\restn{(x)}+\restn{(y)}+[x,y]\textup{ and }[\restn{x},z]=[x,[x,z]].\]
Note that when $n=1$ the restriction is not defined anywhere.
\end{itemize}
We have defined the bracket and restrictions on homogeneous elements only, but there is no problem extending these operations definition to non-homogeneous elements using the bilinearity of the bracket and the above formula for the restriction of a sum.
%We can define $\restn{}$ on the the direct sum of those $L_{a_n,\ldots,a_1}$ for which not all of $a_n,\ldots,a_2$ are zero, using the above formula for $\restn{(x+y)}$. Then both of the above two formulae will still hold for non-homogeneous $x,y,z$. Thus, we could equally have defined $\PRLie{n}$ by giving a restriction on this entire ideal.
%\begin{prop*}
%If $X\in\GS{n}$ a graded set, the `Hall basis' of $\Fr{\GoodLie{n}}(X)$ \cite{MR0038336} consists of certain `standard monomials' $b$ in the elements of $X$. Then $\Fr{\BadLie{n}}(X)$ has a basis $\{b\}\cup\{[b,b]\}$.
%\end{prop*}

If $X\in\GS{n}$ a graded set, one may choose a `Hall basis' of $\Fr{\GoodLie{n}}(X)$ \cite{MR0038336} consisting of certain `standard monomials' $b$ in the elements of $X$.
\begin{prop*}
Let $X\in\GS{n}$ be a graded set, and let $B$ be a Hall basis for $\Fr{\GoodLie{n}}(X)$ derived from $X$. Note that $B\subset \Fr{\GoodLie{n}}(X)$ is actually a graded set. Then:
\begin{enumerate}[i)]\squishlist
\setlength{\parindent}{.25in}
\item $\Fr{\BadLie{n}}(X)$ has a basis $B\cup\{[b,b]\,:\,b\in B\}$;
\item $\Fr{\RestLie{n}}(X)$ has a basis $\{\iteratedrestn{b}{n}\,:\,b\in B,\,n\geq0\}$; and
\item $\Fr{\PRLie{n}}(X)$ has a basis $B\cup \{\iteratedrestn{b}{n}\,:\,b\in B_{a_{n},\ldots,a_1},\,n\geq1,\textup{ not all of $a_n,\ldots,a_2$ are zero}\}$.
\end{enumerate}
\end{prop*}
\begin{proof}
Part (ii) is standard and can be found in \cite[Proposition 14, p.66]{MR886063}.
For part (i), note that the Jacobi identity implies that $[x,[y,y]]$ is identically zero in any bad Lie algebra.
%For part (i), note that in any Lie algebra in characteristic 2, $[x,[y,y]]$ is zero, by anti-symmetry in odd or zero characteristic, and by the Jacobi identity in characteristic 2. 
In particular, the proposed basis must span $\Fr{\BadLie{n}}(X)$. On the other hand, as one easily defines a Lie algebra structure on the vector space spanned by the symbols $B\cup\{[b,b]\}$, they must be linearly independent in $\Fr{\BadLie{n}}(X)$, proving (i).

For (iii), the proposed basis again must span $\Fr{\PRLie{n}}(X)$, and can be seen to be linearly independent by considering the map $\Fr{\PRLie{n}}(X)\to \Fr{\RestLie{n}}(X)$ of partially restricted Lie algebras.
\end{proof}


\subsection{Homotopy operations for simplicial Lie algebras}
The goal of this section is to determine the natural operations on the homotopy of a simplicial object in the category $\mathsf{C}$, for $\mathsf{C}=\mathsf{C}^n$ any of the above categories of graded Lie algebras. This is equivalent to calculating the homotopy of `wedges of spheres'.

That is, suppose that $X\in\GS{n+1}$ is a graded set. Then one can form a simplicial pointed graded set $S(X)\in s\GpS{n}$ by the formula
\[(S(X))_{a_n,\ldots,a_1}=\bigvee_{x\in X_{d,a_n,\ldots,a_1}}S^d_{a_n,\ldots,a_1}\]
Here, $S^d_{a_n,\ldots,a_1}$ is the standard simplicial $d$-sphere $\Delta^d/\partial\Delta^n$ living in the $a_n,\ldots,a_1$ grading.
Then $\Fr{\mathsf{C}}S(X)\in s\mathsf{C}$ represents the following functor $s\mathsf{C}\to\AbGp$
\[C\mapsto \prod_{x\in X_{d,a_n,\ldots,a_1}}\pi_d(C)_{a_n,\ldots,a_1}\]
where $\pi_d(C)_{a_n,\ldots,a_1}$ is the grading $a_n,\ldots,a_1$ part of $\pi_d(C)$. In particular, by Yoneda's lemma:
\[\left\{\prod_{x\in X_{d,a_n,\ldots,a_1}}\pi_d(\DASH)_{a_n,\ldots,a_1}\overset{\textup{nat}}{\to}\pi_D(\DASH)_{A_n,\ldots,A_1}\right\}\cong\pi_D\left(\Fr{\mathsf{C}}S(X)\right)_{A_n,\ldots,A_1}\]
Thus we're interested in the homotopy groups of $\mathsf{C}S(X)$. These are well known when $\mathsf{C}$ is $\GoodLie{n}$ or $\RestLie{n}$, and from these calculations we will deduce the result when $\mathsf{C}=\PRLie{n}$. Before stating the results, we recall certain well known operations on the homotopy of good and restricted Lie algebras, as discussed in \cite[Thm 7.12, Prop 8.8]{CurtisSimplicialHtpy.pdf}:
\begin{prop*}
For $X$ a simplicial object either in $\GoodLie{n}$ or $\RestLie{n}$, $\pi_{*}(X)$ naturally becomes a good Lie algebra (in $\GoodLie{n+1}$) under a bracket induced by the shuffle map. Moreover, $\pi_{*}(X)$ has natural operations
\[\Q^i:\pi_{a_{n+1}}(X)_{a_n,\ldots,a_1}\to \pi_{a_{n+1}+i}(X)_{2a_n,\ldots,2a_2,2a_1+1}
\]
defined whenever $0<i\leq a_{n+1}$ and when $i=0$ if $X\in\RestLie{n}$. The following relations hold between the various operations (whenever the left hand side of each relation is defined).
%\[\textup{for $i>2j,$\ \ }\Q^i\Q^jx=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}x.\]
%\[\Q^i{(x+y)}=\Q^i{x}+\Q^i{y}\textup{ and }[\Q^i{x},z]=0\textup{ for $i<|x|=|y|$ and any $z$}\]
%\[\Q^i(x+y)=\Q^ix+\Q^iy+[x,y]\textup{ and }[\Q^{i}x,z]=[x,[x,z]]\textup{ for $i=|x|=|y|$ and any $z$}.\]
The $\Q$ operations satisfy the $\Q$-Adem relations:%, so that if $i>2j$, and $\Q^i\Q^jx$ is defined, then:
\[\Q^i\Q^jx=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}x\textup{ for }i>2j.\]
The non-top operations are linear and are killed by the bracket.
That is, for $x,y\in \pi_{a_{n+1}}(X)_{a_n,\ldots,a_1}$, $z\in \pi_*(X)$ and $i<a_{n+1}$: \[\Q^i{(x+y)}=\Q^i{x}+\Q^i{y}\textup{ and }[\Q^i{x},z]=0.\]
On the other hand, the top $\Q$ operation, 
acts as a (partially defined) restriction, so that, for $x,y\in \pi_i(X)_{ a_{n},\ldots,a_1}$ and $z\in \pi_*(X)$,
\[\Q^i(x+y)=\Q^ix+\Q^iy+[x,y]\textup{ and }[\Q^{i}x,z]=[x,[x,z]].\]

%
%
%
%
% The top $\Q^i$ acts as a restriction operation, so that $\Q^{|x|}(x)=\restn(x)$ whenever both sides are defined. The non-top operations are linear and are killed by the bracket.
%That is, for $x,y\in L_{a_n,\ldots,a_1}$, $i<a_n$ (with not all of $i,a_{n-1},\ldots,a_{2}$ being zero) and $z\in L$: \[\Q^i{(x+y)}=\Q^i{x}+\Q^i{y}\textup{ and }[\Q^i{x},z]=0.\]
%Finally, the $\Q$ operations are assumed to satisfy the following $\Q$-Adem relations wherever they make sense. If $i>2j$, and $\Q^i\Q^jx$ is defined (i.e.\ $j\leq|x|$, not all of $j,a_{n-1},\ldots,a_2$ are zero, and $i\leq|x|+j$):
%\[\Q^i\Q^jx=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}x.\]
\end{prop*}

\noindent Again, it is not immediately obvious that $\Q$-Adem relations are well defined, but this follows from the same lemma as previously, even with the restrictions on $\Q^0$. 
%\begin{lem*}
%Suppose that %$i>2j$, and 
%$\produces{(i,j)}{(i',j')}{\Q}$. Then
%\begin{enumerate}[i)]\squishlist
%\setlength{\parindent}{.25in}
%\item Both $i'$ and $j'$ are nonzero.
%\item If $\Q^i\Q^j$ is defined on a class in $\pi_n (L)$ for $L$ a simplicial Lie algebra, then $\Q^{i'}\Q^{j'}$ is defined on all of $\pi_{n-1}(L)$, which is to say that $\minDim(i',j')<
%\minDim(i,j)$.
%\end{enumerate}
%In particular, if $\Q^i\Q^jx$ is defined, and $i>2j$, it can be rewritten as a sum of terms $\Q^{i'}\Q^{j'}x$ in which neither of the $\Q^{i'}$ and $\Q^{j'}$ that appear are top operations.
%\end{lem*}
With these operations in hand, we can express the homotopy groups of spheres as follows:





\begin{prop*}
Suppose that $X\in\GS{n+1}$ is a graded set. Let $B$ be a Hall basis for
the free good Lie algebra $\Fr{\GoodLie{n+1}}(X)$ derived from $X$. Note
that $B\subset \Fr{\GoodLie{n}}(X)$ is in particular a graded set.
\begin{alignat*}{2}
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X)$}][c]{$\Fr{\GoodLie{n}}S(X)$})
&=
\left\langle \Q^Ib\,:\,b\in
B,\,I\in\admis{\Q},\ i_1\leq|b|,\ I\textup{ doesn't contain zero}\right\rangle%
\\
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X)$}][c]{$\Fr{\RestLie{n}}S(X)$})
&=
\left\langle \Q^Ib\,:\,b\in
B,\,I\in\admis{\Q},\ i_1\leq|b|\right\rangle\textup{, \ and}%
\\
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X)$}][c]{$\Fr{\PRLie{n}}S(X)$})
&=
\left\langle \Q^Ib\,:\,\genfrac{}{}{0pt}{}{b\in B,\,I\in\admis{\Q},\ i_1\leq|b|,}{\textup{if }a_{n}=\cdots=a_2=0\textup{ then $I$ doesn't contain 0}}\right\rangle,%
\end{alignat*}
where by $a_n,\ldots,a_2$ we mean all but the outermost indices in $\|b\|=(a_{n+1},\ldots,a_1)$, by $i_1$ we mean the rightmost entry of $I=(i_\ell,\ldots,i_1)$, and we ignore the condition on $i_1$ when $I$ is empty.
%\begin{enumerate}[i)]\squishlist
%\setlength{\parindent}{.25in}
%\item $\pi_*(\Fr{\GoodLie{n}}S(X))$ has basis $\{\Q^Ib\,:\,b\in
%B,\,I\in\admis{\Q},\ i_1\leq|b|,\ I\textup{ doesn't contain zero}\}$;
%\item $\pi_*(\Fr{\RestLie{n}}S(X))$ has basis $\{\Q^Ib\,:\,b\in
%B,\,I\in\admis{\Q},\ i_1\leq|b|\}$; and
%\item $\pi_*(\Fr{\PRLie{n}}S(X))$ has basis
%\[\left\{\Q^Ib\,:\,\genfrac{}{}{0pt}{}{b\in B_{a_{n+1},\ldots,a_1},\,I\in\admis{\Q},\ i_1\leq|b|=a_{n+1},}{\textup{if }a_{n}=\cdots=a_2=0\textup{ then $I$ doesn't contain 0}}\right\}\]
%\end{enumerate}
%We always allow $I$ to be the empty sequence in the above bases, in which case the condition on $i_{1}$ is to be ignored. If $I$ is nonempty, we mean that $i_{1}$ is the rightmost entry of $I=(i_\ell,\ldots,i_1)$.
\end{prop*}
The first two parts assert that the natural homotopy operations in the
homotopy of a simplicial good or restricted Lie algebra are generated by
the operations of the previous proposition, and are subject only to those
relations stated. Part (iii) asserts that the natural homotopy operations
for partially restricted Lie algebras interpolate between those for good
and those for restricted Lie algebras in the obvious way. This demonstrates
that $\PiAlg{\PRLie{n}}$, the natural target category for the functor
$\pi_*$ on $s\PRLie{n}$, is in fact the category $\LL{n+1}$ that we'll
define in the next section.
\newpage
\begin{proof}
See
\cite[Thm 8.8 and proof]{CurtisSimplicialHtpy.pdf} for the proof of parts
(i) and (ii).

For any set $Y\in\GpS{n}$, write $Y^\textup{z}\in\GpS{n}$ for the object
defined by
\[(Y^\textup{z})_{a_n,\ldots,a_1}=\begin{cases}
Y_{0,\ldots,0,a_1},&\textup{if }a_n=\cdots =a_2=0;\\
\{\star\},&\textup{otherwise}.
%\\,&\textup{if }
\end{cases}
\]
This assignment is functorial in $Y$, and there is a natural surjection
of restricted Lie
algebras $\gamma:\Fr{\RestLie{n}}(Y)\to\Fr{\RestLie{n}}(Y^\textup{z})$. 
Moreover, there is a natural surjection $\rho:\Fr{\RestLie{n}}(Y^\textup{z})\to \Fr{\RestLie{n}}(Y^\textup{z})/\Fr{\GoodLie{n}}(Y^\textup{z})$.
The above calculation of bases for the free constructions in
$\GoodLie{n}$, $\RestLie{n}$ and $\PRLie{n}$, shows that the kernel of the
composite
$\rho\gamma$
is precisely $\Fr{\PRLie{n}}(Y)$, so that we have two short exact sequences of simplicial vector spaces, and a commuting triangle:
\[\xymatrix@R=-2mm{
0
\ar[r]
&%r1c1
\Fr{\PRLie{n}}S(X)
\ar[r]^{\alpha}
&%r1c2
\Fr{\RestLie{n}}S(X)
\ar[dr]^-(.4){\rho\gamma}\ar[dd]^-{\gamma}
&%r1c3
%\Fr{\RestLie{n}}S(X)/\Fr{\PRLie{n}}S(X)
%\ar[r]
%\ar[d]^-{\cong}
%&%r1c4
\\%r1c5
&&&\frac{\displaystyle \Fr{\RestLie{n}}S(X^\textup{z})}{\displaystyle \Fr{\GoodLie{n}}S(X^\textup{z})}
\ar[r]
&
0
\\
0
\ar[r]
&%r1c1
\Fr{\GoodLie{n}}S(X^\textup{z})
\ar[r]^{\beta}
&%r1c2
\Fr{\RestLie{n}}S(X^\textup{z})
\ar[ru]^-(.4){\rho}&%r1c3
%\Fr{\RestLie{n}}S(X^\textup{z})/\Fr{\GoodLie{n}}S(X^\textup{z})
%\ar[r]
%&%r1c4
%0
}\]
Now using parts (i) and (ii) we can describe the maps $\beta_*$ and $\gamma_*$ as the evident inclusion and projection between
\begin{alignat*}{2}
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X^\textup{z})$}][c]{$\Fr{\GoodLie{n}}S(X^\textup{z})$})
&=
\langle \Q^Ib\,:\,a_{n}=\cdots =a_2=0,\, i_1\leq|b|,\, 0\notin I\rangle.%
\\
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X^\textup{z})$}][c]{$\Fr{\RestLie{n}}S(X^\textup{z})$})
&=
\langle \Q^Ib\,:\,a_{n}=\cdots =a_2=0,\, i_1\leq|b|\rangle\textup{, \ and}%
\\
\pi_*(\makebox[\widthof{$\Fr{\GoodLie{n}}S(X^\textup{z})$}][c]{$\Fr{\RestLie{n}}S(X)$})
&=
\langle \Q^Ib\,:\,i_1\leq|b|\rangle,%
\end{alignat*}
where in each of the above specifications we have omitted that $b\in B_{a_{n+1},\ldots,a_1}$ and $I\in\admis{\Q}$.
As $\beta_*$ is injective, $\rho_*$ is surjective, thus $(\rho\gamma)_*$ is surjective, and $\alpha_*$ is injective. The resulting identification of $\pi_*(\Fr{\PRLie{n}}S(X))$ with $(\gamma_*)^{-1}(\im(\beta_*))$ gives (iii).
\end{proof}
\subsection{Categories of graded Lie algebras with unstable operations}
\begin{itemize}
\setlength{\parindent}{.25in}
%\item Let $\LL{1}$ be the full subcategory of connected objects in $\calW$. We already have the definition for these in Goerss' book, but I'll spell this out here, to emphasise certain interesting aspects of the character of $\LL{1}$.
%An object of $\LL{1}$ is a (potentially bad) graded Lie algebra $L$ in $\BadLie{1}$ with an unstable (linear) action of $\CommSteen$.
%That is, $L$ admits $P$ operations
%\[P^i:L_{a_1}\to L_{a_1+i+1}\]
%which are \emph{always} defined for $i\geq0$, but \emph{equal zero} unless $2\leq i\leq a_n$.
%%By `bad' Lie algebra, we mean that the bracket satisfies the Jacobi identity, and is skew symmetric (``$[x,y]=[y,x]$ for all $x,y$'').
%%The graded part $L_{0}$ is assumed to be zero, and for $x\in L_{a_1}$ we write $|x|:=a_1$. 
%The $P$ operations are assumed to satisfy the following $P$-Adem relations. If $i\geq 2j$:
%\[P^iP^jx=\sum_{s=i-j+1}^{i+j-2}{2s-i-1\choose s-j}P^{i+j-s}P^sx.\]
%Every $P$ operation is assumed linear, and $[x,P^iy]=0$ for all $i,x,y$. Additionally, the top $P$ operation is the `self-square': for $x\in L_{i}$, $P^{i}x=[x,x]$.
\item Let $\LL{1}$ be the following category of graded bad Lie algebras which are also unstable left $\Q$-modules.
An object of $\LL{1}$ is a (potentially) bad graded Lie algebra $L$ in $\BadLie{1}$ %with an unstable (linear) action of $\CommSteen$.
admitting linear operations
\[P^i:L_{a_1}\to L_{a_1+i+1}\]
which are \emph{always} defined for $i\geq0$, but \emph{equal zero} unless $2\leq i\leq a_n$. They satisfy the $P$-Adem operations when written on the left. Finally, $[x,P^iy]=0$ for all $i,x,y$, and the top $P$ operation is the `self-square': for $x\in L_{i}$, $P^{i}x=[x,x]$.

Note that this is just the full subcategory of connected objects in Goerss' category $\calW$. See \cite[p.14]{MR1089001}. \textbf{I might make them only defined for $i\geq2$ and stick $[x,x]=0$ on for $|x|=1$.}

\item Let $\nontop{1}$ be the following category of graded unstable $P$-modules. An object of $\nontop{1}$ is a graded vector space $M$ in $\GR{1}$,
admitting linear operations
\[P^i:M_{a_1}\to M_{a_1+i+1}\]
which are always defined, but are zero unless $2\leq i\leq a_n$.
%The graded part $M_{0}$ is assumed to be zero, and for $x\in M_{a_n,\ldots,a_1}$ we write $|x|:=a_n$. 
The $P$ operations are assumed to satisfy the same $P$-Adem relations as in $\LL{1}$. %Every operation $P^i$ is assumed linear.
\item For $n\geq2$, let $\LL{n}$ be the following category of $n$-graded partially restricted Lie algebras with unstable $\Q$ operators acting from the left. An object of $\LL{n}$ consists of an object $L$ of $\PRLie{n}$ 
admitting $\Q$ operations
\[\Q^i:L_{a_n,\ldots,a_1}\to L_{a_n+i,2a_{n-1},\ldots,2a_2,2a_1+1}\]
defined whenever $i\leq a_n$ and not all of $i,a_{n-1},\ldots,a_{2}$ are zero. The top $\Q^i$ \emph{equals} the restriction operation, so that $\Q^{|x|}(x)=\restn(x)$ whenever both sides are defined. The non-top operations are linear and are killed by the bracket.
That is, for $x,y\in L_{a_n,\ldots,a_1}$, $i<a_n$ (with not all of $i,a_{n-1},\ldots,a_{2}$ being zero) and $z\in L$: \[\Q^i{(x+y)}=\Q^i{x}+\Q^i{y}\textup{ and }[\Q^i{x},z]=0.\]
Finally, the $\Q$ operations are assumed to satisfy the following $\Q$-Adem relations wherever they make sense. If $i>2j$, and $\Q^i\Q^jx$ is defined (i.e.\ $j\leq|x|$, not all of $j,a_{n-1},\ldots,a_2$ are zero, and $i\leq|x|+j$):
\[\Q^i\Q^jx=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}x.\]
%\item For $n\geq2$, let $\LL{n}$ be the following category of $n$-graded \emph{good} Lie algebras with unstable $\Q$ operators acting from the left. An object of $\LL{n}$ consists of an object $L$ of $\GoodLie{n}$
%%, under a $(0,\ldots,0,1)$-shifted bracket:
%%\[[\DASH,\DASH]:L_{a_n,\ldots,a_1}\otimes L_{b_n,\ldots,b_1}\to L_{a_n+b_n,\ldots,a_2+b_2,a_1+b_1+1}\]
%admitting $\Q$ operations
%\[\Q^i:L_{a_n,\ldots,a_1}\to L_{a_n+i,2a_{n-1},\ldots,2a_2,2a_1+1}\]
%defined whenever $i\leq a_n$ and not all of $i,a_{n-1},\ldots,a_{2}$ are zero. %By `good' Lie algebra, we mean that the bracket satisfies the Jacobi identity, and is alternating (``$[x,x]=0$ for all $x$'').
%%The graded part $L_{a_n,\ldots,a_1}$ is assumed to be zero whenever $a_1=0$, and for $x\in L_{a_n,\ldots,a_1}$ we write $|x|:=a_n$.
%The $\Q$ operations are assumed to satisfy the following $\Q$-Adem relations wherever they make sense. If $i>2j$, and $\Q^i\Q^jx$ is defined (i.e.\ $j\leq|x|$, not all of $j,a_{n-1},\ldots,a_2$ are zero, and $i\leq|x|+j$):
%\[\Q^i\Q^jx=\sum_{k=0}^{(i-2j)/2-1}{i-2j-2-k\choose k}\Q^{2j+1+k}\Q^{i-j-1-k}x.\]
%The non-top operations are linear and are killed by the bracket.
%That is, for $x,y\in L_{a_n,\ldots,a_1}$ and $z\in L$: \[\Q^i{(x+y)}=\Q^i{x}+\Q^i{y}\textup{ and }[\Q^i{x},z]=0.\]
%On the other hand, the top operation, 
%\[\Q^i:L_{i, a_{n-1},\ldots,a_1}\to L_{2i, 2a_{n-1},\ldots,2a_2,2a_1+1}\]
%acts as a partially defined restriction for $L$, satsfying, for $x,y\in L_{i, a_{n-1},\ldots,a_1}$ and $z\in L$,
%\[\Q^i(x+y)=\Q^ix+\Q^iy+[x,y]\textup{ and }[\Q^{i}x,z]=[x,[x,z]].\]

\item For $n\geq2$, let $\nontop{n}$ be the following category of $n$-graded vector spaces with unstable $\Q$ operators acting from the left. An object of $\nontop{n}$ is an $n$-graded vector space $M$ in $\GR{n}$,
admitting linear operations
\[\Q^i:M_{a_n,\ldots,a_1}\to M_{a_n+i,2a_{n-1},\ldots,2a_2,2a_1+1}\]
defined whenever $i< a_n$ (note the strict inequality) and not all of $i,a_{n-1},\ldots,a_{2}$ are zero.
%The graded part $M_{a_n,\ldots,a_1}$ is assumed to be zero whenever $a_1=0$, and for $x\in M_{a_n,\ldots,a_1}$ we write $|x|:=a_n$. 
The $\Q$ operations are assumed to satisfy the same $\Q$-Adem relations as in $\LL{n}$, wherever they make sense in $\nontop{n}$. %The same discussion shows that this too is a meaningful definition. %Every operation $\Q^i$ is assumed linear.
\end{itemize}


\begin{prop*}
Let $X\in\GS{n}$ be a graded set, and let $B$ be a Hall basis for $\Fr{\GoodLie{n}}(X)$ derived from $X$. Note that $B\subset \Fr{\GoodLie{n}}(X)$ is in particular a graded set. Then when $n=1$:
\begin{enumerate}[i)]\squishlist
\setlength{\parindent}{.25in}
\item $\Fr{\LL{1}}(X)$ has basis $\{P^Ib\,:\,b\in B,\,I\in\admis{P}\textup{ with }i_1\leq|b| \}$;
\item $\Fr{\nontop{1}}(X)$ has basis $\{P^Ix\,:\,x\in X,\,I\in\admis{P}\textup{ with }i_1\leq|x| \}$;
\end{enumerate}
and when $n\geq2$:
\begin{enumerate}[i)]\squishlist
\setlength{\parindent}{.25in}
\item[iii)] $\Fr{\LL{n}}(X)$ has basis $\{\Q^Ib\,:\,b\in B_{a_{n},\ldots,a_1},\,I\in\admis{\Q},\ i_1\leq|b|,\ i_1,a_{n-1},\ldots,a_2\textup{ not all zero}\}$;
\item[iv)] $\Fr{\nontop{n}}(X)$ has basis $\{\Q^Ix\,:\,x\in X_{a_{n},\ldots,a_1},\,I\in\admis{\Q},\ i_1<|b|,\ i_1,a_{n-1},\ldots,a_2\textup{ not all zero}\}$.
\end{enumerate}
We always allow $I$ to be the empty sequence in the above bases, in which case the condition on $i_{1}$ is to be ignored. If $I$ is nonempty, we mean that $I=(i_\ell,\ldots,i_1)$, so that $i_{1}$ is the rightmost entry of $I$.
Note that the inequalities involved differ according to whether $n=1$ or $n\geq2$.
\end{prop*}
%\begin{prop*}
%If I ever use this, I'll swap the `i_ell's
%For $n\geq2$, for $X\in\GS{n}$ a graded set, $\Fr{\LL{n}}(X)$ has basis the compositions $\Q^{I}b$, where $b$ runs over a homogeneous Hall basis for the free (unrestricted, good) Lie algebra $\Fr{\GoodLie{n}}(X)$, and $I=(i_1,\ldots,i_\ell)$ is a $\Q$-admissible sequence with $i_\ell\leq|b|$ and not all of $i_{\ell},a_{n-1},\ldots,a_2$ are zero if $b$ has grading $(a_n,\ldots,a_1)$. 
%
%$\Fr{\nontop{n}}(X)$ has basis the compositions $\Q^{I}x$ where $x\in X$ and $I=(i_1,\ldots,i_\ell)$ is a $\Q$-admissible sequence with $i_\ell<|x|$ and not all of $i_{\ell},a_{n-1},\ldots,a_2$ are zero if $x$ has grading $(a_n,\ldots,a_1)$.
%%Here, $L^uX$ is an object of $\GoodLie{n}$ if we stipulate that the bracket shifts degrees as appropriate.
%\end{prop*}
\begin{proof}
Part (i) is \cite[Thm F, p.15]{MR1089001}.
In each of the remaining three cases, it is clear that the proposed bases span the free constructions. It remains to show that the elements are linearly independent.
The proposed basis in part (ii) is seen to be linearly independent using the map $\Fr{\nontop{1}}(X)\to \Fr{\LL{1}}(X)$. Part (iv) follows from (iii) similarly.

For part (iii), note that we have calculated the object $\pi_*(\Fr{\PRLie{n-1}}S(X))\in\PiAlg{\PRLie{n-1}}=\LL{n}$, and that the elements of our proposed basis of $\Fr{\LL{n}}(X)$ map to a basis of $\pi_*(\Fr{\PRLie{n-1}}S(X))$ under the natural map. This proves the linear independence statement we require.
%sequences I here are back to front again
%For part (iii), choose a simplicial object of $\GR{n-1}$, say $V\in s(\GR{n-1})$, such that $\pi_{*}V=\Fr{\GR{n}}(X)$. Then \cite[Thm 8.6, Thm 8.8]{CurtisSimplicialHtpy.pdf} shows that $\pi_*(\Fr{\RestLie{n}}(V))$ is an element of $\LL{n}$, and has a basis consisting of tensors $\Q^{I}\otimes b$, for $b\in B$, and $I\in\admis{\Q}$ with $i_\ell\leq|b|$. The `not all zero' condition is dropped here, so that $\pi_*(\Fr{\RestLie{n}}(V))$ is larger than our proposed $\LL{n}(X)$.
%
%Consider then the morphism $\Fr{\LL{n}}(X)\to \pi_*(\Fr{\RestLie{n}}(V))$ induced by the universal property of the free construction. The images of the proposed basis for $\Fr{\LL{n}}(X)$ map to linearly independent elements in $\pi_*(\Fr{\RestLie{n}}(V))$, showing that $\Fr{\LL{n}}(X)$ is as described. The same argument will prove (iv), this time viewing $\pi_*(\Fr{\RestLie{n}}(V))$ as an element of $\nontop{n}$.
\end{proof}
\begin{cor*}
For all $n\geq 1$, the forgetful functor $\forget:\LL{n}\to\nontop{n}$ preserves free objects.
\end{cor*}
\begin{proof}
When $n=1$, $\Fr{\LL{1}}(X)$ is free on $B$ as an object of $\nontop{n}$. For $n\geq2$, $\Fr{\LL{n}}(X)$  is free on $B\cup \{\iteratedrestn{b}{n}\,:\,b\in B_{a_{n},\ldots,a_1},\,n\geq1,\textup{ not all of $a_n,\ldots,a_2$ are zero}\}$ as an object of $\nontop{n}$, since
\[\iteratedrestn{b}{n}=\Q^{(2^{n-1}|b|)}\cdots \Q^{(2|b|)}\Q^{|b|}b.\qedhere\]
\end{proof}
\end{CategoriesOfInterest}





\begin{DiagramOfFunctors}
\section{Grothendieck spectral sequences}
\subsection{A diagram of functors}
Now for each category $\mathsf{C}$ amongst $\LL{n}$, $\PRLie{n}$ and $\nontop{n}$, there is a functor $\Ind{\mathsf{C}}:\mathsf{C\overset{}{\to}\GR{n}}$, which takes the quotient of the underlying vector space by the subspace spanned by the image of all of the structure maps. These provide the solid horizontal arrows in the following diagram, while the vertical maps are the evident forgetful functors: %There are also free/forget adjunctions $\GS{n} \rightleftarrows \mathsf{C}$. %Finally, there's a forgetful functor $\forget:\LL{n}\to\nontop{n}$, which, importantly, preserves  free objects%footnote:
%\footnote{I think that the adjunction does need to come from graded pointed sets, but that that's no problem for Blanc-Stover. The only thing that matters is that $\forget$ preserves frees, but it does --- frees in $\nontop{n}$ are easy to describe.}. These functors give the solid maps in the following diagram:
\[\xymatrix@R=8mm@C=15mm@!C{
\LL{n}
\ar@/^1.5em/[rr]^-{\Ind{\LL{n}}}
\ar[d]_-{\forget}
\ar@{-->}[r]_-{}%\Ind{\nontop{n}}}
&%r1c1
\PRLie{n}
\ar[d]^-{\forget}
\ar[r]_-{\Ind{\PRLie{n}}}
&%r1c2
\GR{n}
\\%r1c3
\nontop{n}
\ar[r]_-{\Ind{\nontop{n}}}
&%r2c1
\GR{n}
&%r2c2
%r2c3
}\]
\begin{prop*}
For all $n\geq1$ there exists a functor $\LL{n}\to\PRLie{n}$ which preserves free objects, and completing the diagram above to a commuting square and triangle.
\end{prop*}
\begin{proof}
For all $n$, the bracket and restrictions that are required to define an object of $\nontop{n}$ are well defined after quotienting out the image of the operations in $\Ind{\nontop{n}}$.

When $n=1$ we are to quotient by the image of all of the $P$ operations. There are no restriction operations to be defined, and the bracket is well defined due to the axiom ``$[x,P^iy]=0$''. Although we started with a bad Lie algebra, the axiom ``$P^{|x|}x=[x,x]$'' shows that the quotient is a good lie algebra, as required.

When $n\geq2$  we are to quotient by the image of all of the non-top $\Q$ operations. Again, the bracket is well defined on the quotient as brackets kill non-top $\Q$ operations. To see that the restriction is well defined on the quotient, %we must check the following fact: for homogeneous $x,y\in L$, and $0\leq i<|y|$ such that $\Q^iy$ is defined and $i+|y|=|x|$, $\restn{(x)}$ and $\restn(x+\Q^iy)$ differ by a sum of images of nontop $\Q$ operations. This follows from the fact that $\Q$-Adem relations do not produce top $\Q$ operations, since \[\restn{(x+\Q^iy)}=\restn{(x)}+\restn{(\Q^iy)}+[x,\Q^iy]=\restn{(x)}+\Q^{|y|+i}\Q^iy+0,\] and $|x|=i+|y|>2i$, so that there's an Adem relation to apply to $\Q^{|x|}\Q^iy$.
suppose that $\Q^iy$ is the image of a well-defined non-top operation, so that $i<|y|$. Then
\[\restn{(x+\Q^iy)}=\restn{(x)}+\restn{(\Q^iy)}+[x,\Q^iy]=\restn{(x)}+\Q^{|y|+i}\Q^iy.\]
The rightmost term admits the application of an Adem relation, as $|y|+i>2i$, but we have seen that Adem relations never return top $\Q$ operations.

These arguments have shown that the quotient supports the structure of partially restricted Lie algebra. The assignment is clearly functorial, and makes the whole diagram commute. 
By examining our results on the bases of the various free constructions, one sees that $\Ind{\nontop{n}}$ sends $\Fr{\LL{n}}(X)$ to $\Fr{\PRLie{n}}(X)$, both when $n=1$ and when $n\geq2$.
\end{proof}
\noindent It should cause no confusion when we denote the functor of this proposition $\Ind{\nontop{n}}:\LL{n}\to \PRLie{n}$ as well, giving a commuting diagram
\[\xymatrix@R=8mm@C=15mm@!C{
\LL{n}
\ar@/^1.5em/[rr]^-{\Ind{\LL{n}}}
\ar[d]_-{\forget}
\ar@{->}[r]_-{\Ind{\nontop{n}}}
&%r1c1
\PRLie{n}
\ar[d]^-{\forget}
\ar[r]_-{\Ind{\PRLie{n}}}
&%r1c2
\GR{n}
\\%r1c3
\nontop{n}
\ar[r]_-{\Ind{\nontop{n}}}
&%r2c1
\GR{n}
&%r2c2
%r2c3
}\]
in which the functors $\forget$ and $\Ind{\nontop{n}}$ with domain $\LL{n}$ both preserve free objects.
%The point is that there is a functor $\LL{n}\to\PRLie{n}$ which completes this diagram to a commuting square and triangle, which we also name $\Ind{\nontop{n}}$. It will be important to note that $\Ind{\nontop{n}}$ sends free objects in $\LL{n}$ to free objects in $\PRLie{n}$.
%
%When $n=1$, $\Ind{\nontop{n}}$ quotients the underlying vector space by the images of all of the $P$ operations. The result inherits the structure of an element of $\PRLie{n}$ from the bracket in $\LL{1}$. This is well defined due to the axioms ``$[x,P^iy]=0$'' and ``$P^{|x|}x=[x,x]$''. 
%
%When $n\geq2$, $\Ind{\nontop{n}}$ quotients the underlying vector space by the images of all of the non-top $\Q$ operations. That is, by the span of the $\Q^ix$ for $i<|x|$. The result inherits the structure of an element of $\PRLie{n}$ as follows. The Lie bracket is induced by that in $\LL{n}$; well defined by the axiom ``$[\Q^i{x},z]=0$ for $i<|x|$''. The restriction is induced by the top $\Q$ operations, being defined by the formula $\restn{x}:=\Q^{|x|}x$. It is a little less obvious that this is in fact well defined. One must check, for homogeneous $x,y\in L$, and $0\leq i<|y|$ such that $\Q^iy$ is defined and $i+|y|=|x|$, that $\Q^{|x|}x$ and $\Q^{|x|}(x+\Q^iy)$ differ by a sum of images of non-top $\Q$ operations. But\[\Q^{|x|}(x+\Q^iy)-\Q^{|x|}x=\Q^{|x|}(\Q^iy)+[x,\Q^iy]=\Q^{|x|}\Q^iy,\]and the above calcuation regarding indices in the $\Q$-Adem relations shows that $\Q^{|x|}\Q^iy$ can be rewritten without the appearance of a top $\Q$.
\end{DiagramOfFunctors}
\begin{GrothendieckSpectralSequences}
\subsection{Grothendieck spectral sequences}
We are interested in the derived functors $(\derived\Ind{\LL{n}})X\in\GR{n+1}$ for $X\in\LL{n}$. It is convenient for us to omit the customary asterisk in $\derived_*$, and to think of the derived functors as a single object with a one more grading than $X$ has. We always write the new grading to the left of the previous gradings, as is customary. To study $(\derived\Ind{\LL{n}})(X)$ we use the Grothendieck spectral sequence derived in \cite{Blanc_Stover-Groth_SS.pdf}. The spectral sequence takes the form:
\[E^2_{st}=(\derived_s(\overline{\Ind{\PRLie{n}}}_t))(\derived\Ind{\nontop{n}})X\implies(\derived_{s+t}\Ind{\LL{n}})X\textup{ with }d^{r}:E_{st}\to E_{s-r,t+r-1}.\]
To explain this, note that $\derived\Ind{\nontop{n}}\in\PiAlg{\PRLie{n}}$, and $\overline{\Ind{\PRLie{n}}}$ is the functor $\PiAlg{\PRLie{n}}\to\GR{n+1}$ induced by $\Ind{\PRLie{n}}$. The $t$ subscript picks out the part with (new) grading $t$. It might be simpler to write:
\[E^2=(\derived\overline{\Ind{\PRLie{n}}})(\derived\Ind{\nontop{n}})X\implies(\derived\Ind{\LL{n}})X\textup{ with }\deg(d^r)=(-r,r-1,0,\ldots,0).\]
Here, each $E^r$ is $(n+2)$-graded, while $(\derived\Ind{\LL{n}})X$ is $(n+1)$-graded. Each page $E^r$ has two homological degrees in addition to the $n$ internal degrees of $X$, and these extra two degrees on $E^\infty$ sum to the single homological degree in $(\derived\Ind{\LL{n}})X$.
\begin{prop*}
There's a commuting diagram of functors:
\[\xymatrix@R=0mm@C=14mm{
\PiAlg{\PRLie{n}}
\ar[dr]^-{\overline{\Ind{\PRLie{n}}}}
\ar[dd]_-{\cong}
&%r1c1
\\%r1c2
&%r2c1
\GR{n+1}\\%r2c2
\LL{n+1}
\ar[ur]_-{\Ind{\LL{n+1}}}
&%r3c1
%r3c2
}\]
%Under the isomorphism $\PiAlg{\PRLie{n}}\cong\LL{n+1}$, the functor $\overline{\Ind{\PRLie{n}}}:\PiAlg{\PRLie{n}}\to \GR{n+1}$ is identified with 
\end{prop*}
\begin{proof}
As $\overline{\Ind{\PRLie{n}}}$ is a $0^\textup{th}$ left derived functor, and $\Ind{\LL{n+1}}$ preserves colimits, it is enough to check that this diagram commutes on free objects in $\PiAlg{\PRLie{n}}$. All such objects are of the form $\pi_*(\Fr{\PRLie{n}}SX)$ for some $X\in\GS{n+1}$, and
\[\overline{\Ind{\PRLie{n}}}(\pi_*(\Fr{\PRLie{n}}SX)):=\pi_*(\Ind{\PRLie{n}}(\Fr{\PRLie{n}}SX))=\pi_*(SX)=X=\Ind{\LL{n+1}}(\pi_*(\Fr{\PRLie{n}}SX)).\qedhere\]
%The functor $\overline{\Ind{\PRLie{n}}}$ is the $0^\textup{th}$ left derived functor of the functor $\textup{free}(\PiAlg{\PRLie{n}})\to\GR{n+1}$ defined by $\pi_*(\Fr{\PRLie{n}}SX)\mapsto \pi_*(\Ind{\PRLie{n}}(\Fr{\PRLie{n}}SX))$ for $X\in\GS{n+1}$. One calculates $\pi_*(\Ind{\PRLie{n}}(\Fr{\PRLie{n}}SX))=\pi_*(SX)=X$
\end{proof}
%Finally, we should recall that $\PiAlg{\PRLie{n}}\simeq\LL{n+1}$, and under this isomorphism, $\overline{\Ind{\PRLie{n}}}$ is identified with $\Ind{\LL{n+1}}$. 
\begin{cor*}
For $n\geq1$, and any $X\in\LL{n}$, there is a spectral sequence:
\[E^2=(\derived{\Ind{\LL{n+1}}})(\derived\Ind{\nontop{n}})X\implies(\derived\Ind{\LL{n}})X.\]
\begin{itemise}
\setlength{\parindent}{.25in}
\item For $r\leq\infty$, the $E^r$ page is an object of $\GR{n+2}$.
\item For $r<\infty$, $d^r:E^r\to E^r$ has degree $(-r,r-1,0,\ldots,0)$.
\item The target, $(\derived\Ind{\LL{n}})X$, is an object of $\GR{n+1}$.
\item There is an increasing filtration $F$ on $(\derived\Ind{\LL{n}})X$ such that
\[E^\infty_{a_{n+2},\ldots,a_1}=(F_{a_{n+2}}/F_{a_{n+2}-1})((\derived\Ind{\LL{n}})X)_{a_{n+2}+a_{n+1},a_n,\ldots,a_1}.\]
\end{itemise}
%The pages $E^r$ ($r\leq\infty$) are $(n+2)$-graded, with $\deg(d^r)=(-r,r-1,0,\ldots,0)$. The term $E^\infty_{a_{n+2},\ldots,a_1}$ is a subquotient of the degree $(a_{n+2}+a_{n+1},a_n,\ldots,a_1)$ part of the target.
\end{cor*}
%Thus, we may write the spectral sequence as:
%\[\fbox{$E^2=(\derived{\Ind{\LL{n+1}}})(\derived\Ind{\nontop{n}})X\implies(\derived\Ind{\LL{n}})X.$}\]
The following observation explains why there's little danger in having two functors named $\Ind{\nontop{n}}$.
\begin{lem*}
For $n\geq1$, and any $X\in\LL{n}$, there's an isomorphism of vector spaces
\[(\derived{\Ind{\nontop{n}}})X\cong(\derived{\Ind{\nontop{n}}})(\forget(X)),\]
induced by the evident inclusion $B_\bullet(\forget,\Fr{\nontop{n}},\forget(X))\to B_\bullet(\PRLie{n},\Fr{\LL{n}},X)$.
\end{lem*}
\noindent In light of this result, we write $(\derived{\Ind{\nontop{n}}})X$ for either $(\derived{\Ind{\nontop{n}}})X$ or $(\derived{\Ind{\nontop{n}}})\forget(X)$, without ambiguity. DISCUSS the meaning of the fg and Rn in the bar construction.
\begin{proof}
As $\forget:\LL{n}\to\nontop{n}$ preserves free objects and weak equivalences, there's a one-line Grothendieck spectral sequence producing the isomorphism, but this argument does not show that the isomorphism is induced by the inclusion of bar constructions. If $\forget(B_\bullet(\LL{n},\LL{n},X))$ were almost free in $s\nontop{n}$, the map ${B}_\bullet(\nontop{n},\nontop{n},\forget(X))\to{B}_\bullet(\LL{n},\LL{n},X)$ would be a map of cofibrant replacements of $\forget(X)$ in $s\nontop{n}$, and thus 

Or should I say: ``the obvious inclusion map $\overline{B}_*(\nontop{n},\nontop{n},X)\to\overline{B}_*(\LL{n},\LL{n},X)$ is a map of almost free objects realising the identity on $X$''? Is the latter actually almost free in $s\nontop{n}$?
\end{proof}
\begin{lem*}
For any $X$ in $s\LL{n}$, $(\derived{\Ind{\nontop{n}}})(\forget(X))$ may be calculated as the homotopy of the object 
\[\forget(\Ind{\nontop{n}}(B_\bullet(\Fr{\LL{n}},\Fr{\LL{n}},X)))=\forget(B_\bullet(\Fr{\PRLie{n}},\Fr{\LL{n}},X))\in s\GR{n}.\]
\end{lem*}
\begin{proof}
Although $B:=B_\bullet(\Fr{\LL{n}},\Fr{\LL{n}},X)$ is an acyclic levelwise free object in $s\nontop{n}$, with $\pi_0(B)=X$, it may fail to be `almost free'. The point here is that $B$ can be used to calculate the derived functors of $\Ind{\nontop{n}}$ anyway. To see this, consider the bisimplicial object $A:=\Ind{\nontop{n}}(B_\bullet(\Fr{\nontop{n}},\Fr{\nontop{n}},B))$ formed by applying $\Ind{\nontop{n}}$ to the levelwise bar construction on $B$, so that
\[A_{s,t}=(\Ind{\nontop{n}})((\Fr{\nontop{n}})^{s+1})B_t\cong (\Fr{\nontop{n}})^sB_t.\]
Now there are two first-quadrant spectral sequences converging to $\pi_*(\Delta A)$, one with ${E}^{2,I}=\pi_s\pi^e_tA$ and one with $E^{2,II}=\pi_t\pi^i_sA$. We'll show that they are both one-line spectral sequences by $E^2$, with ${E}^{2,I}_{s,0}=(\derived_s\Ind{\nontop{n}})\forget(X)$, and ${E}^{2,II}_{0,t}=\pi_t(\Ind{\nontop{n}}B)$, proving the result.


To identify ${E}^{2,I}_{s,t}$, write $A_{s,\bullet}$ for the singly simplicial object obtained by fixing the inner coordinate in $A$. Then by the lemma, $A_{s,\bullet}$ is acyclic, with $\pi_0 A_{s,\bullet}=(\Fr{\nontop{n}})^s\pi_0(B_\bullet)= (\Fr{\nontop{n}})^sX$. Now $\pi_0 A_{s,\bullet}$ is simplicial in $s$, and can be identified with the bar construction computing $(\derived_s{\Ind{\nontop{n}}})\forget(X)$.

On the other hand, for fixed $t$, $A_{\bullet,t}$ is simply the bar construction calculating $(\derived\Ind{\nontop{n}})B_t$. As $B_t$ is free for each $t$, $(\derived_0\Ind{\nontop{n}})B_t=\Ind{\nontop{n}}(B_t)$, and the higher derived functors vanish, identifying $E^{2,II}$.
\end{proof}
\begin{lem*}
Suppose that $W\in s\nontop{n}$ is acyclic. Then for each $s\geq0$,  $(\Fr{\nontop{n}})^sW\in s\nontop{n}$ is acyclic, with $\pi_0((\Fr{\nontop{n}})^sW)=(\Fr{\nontop{n}})^s(\pi_0(W))$.
\end{lem*}
\begin{proof}
By induction on $s$ it is enough to prove the statement when $s=1$. The calculation of $\pi_0$ is immediate from the fact that $\Fr{\nontop{n}}$, being a left adjoint, preserves colimits.

To approach the acyclicity question, we'll use unreduced chain complexes, writing $\partial:W_r\to W_{r-1}$ for the sum of the face maps. Now suppose that $a\in(\Fr{\nontop{n}}W)_r$ is a cycle. Without loss of generality, we may write
$a:=\sum_j Q^{I_j}x_j$
where all of the $I_j$ are distinct, and the $x_j$ are (potentially inhomogeneous) elements of $W_r$ (such that $Q^{I_j}x_j$ is defined). Then $\partial (a)=\sum Q^{I_j}\partial(x_j)=0$, which implies that each $\partial(x_j)$ is zero, so that $x_j=\partial(y_j)$ for some $y_j\in W_{r+1}$. Note that the internal dimensions of the homogeneous summands of $y_j$ may be taken to be the same as those of $x_j$, in which case $\sum Q^{I_j}y_j$ is defined in $\Fr{\nontop{n}}W_{r+1}$, and has boundary $a$.
\end{proof}
\end{GrothendieckSpectralSequences}


\begin{KoszulComplexes2plus}
\section{Unstable Koszul complexes and Priddy's algorithm}
\subsection{Koszul complexes for $\derived\Ind{\nontop{n}}$ for $n\geq2$}
We will define Koszul complexes calculating $\derived\Ind{\nontop{n}}$ for all $n$. The techniques we will use originate in \cite{PriddyKoszul.pdf}. It will be useful to record here a customized version of Priddy's arguments, for three reasons: his results do not apply to our situation without minor modification to accomodate unstable conditions; we will require a technique from his proof of \cite[Thm 5.3]{PriddyKoszul.pdf} in what follows; we prefer to work with the Koszul complex, not the coKoszul complex.
%We Due to the fact that we are working with categories of unstable modules, there are straightforward changes to be made to Priddy's exposition. We make these changes here. The other benefit to covering this material is that we will
%Moreover, for certain calculations to follow we will need to refer to certain techniques found in the proof of \cite[Thm 5.3]{PriddyKoszul.pdf}. In order that our reader may understand these techniques, we 

%\textbf{remove }For $I=(i_\ell,\ldots,i_1)$ a sequence of nonnegative integers, define
%\[\minDim(I):=\begin{cases}
%-\infty,&\textup{if }I=\emptyset;\\
%\max\{(i_1),\,(i_2-i_1),\,\ldots,\,(i_{\ell}-i_{\ell-1}-\cdots i_1)\},&\textup{otherwise}.
%%\\,&\textup{if }
%\end{cases}
%\]
%Thus, for $n\geq2$:
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item  for $I\neq\emptyset$, $\minDim(I)$ is the lowest dimension $d\geq0$ such that $\Q^I$ may act on a $d$-dimensional element of an object in $\LL{n}$, if we ignore the extra restrictions on $\Q^0$; and
%\item $\minDim(I)$ is the unique element of $\{-\infty,0,1,2,\ldots\}$ such that for any $X\in\nontop{n}$ and any $x\in X$, $\Q^Ix$ is defined if and only if $\minDim(I)<|x|$, if we ignore the extra restrictions on $\Q^0$.
%\end{itemise}

%\subsubsection{The unstable bar construction and Koszul complex for $\nontop{n}$, $n\geq2$}
For any object $X\in\nontop{n}$, the bar construction ${B}_\bullet(\Fr{\nontop{n}},\Fr{\nontop{n}},X)=(\Fr{\nontop{n}})^{\bullet+1}X$ is a free simplicial resolution of $X$. Now there is an isomorphism of graded vector spaces $\Ind{\nontop{n}}(\Fr{\nontop{n}}(X))\cong\forget(X)$. Thus $(\derived\Ind{\nontop{n}})X$ may be calculated as the homotopy of the bar construction $B_\bullet(\forget,\Fr{\nontop{n}},X)=(\Fr{\nontop{n}})^\bullet X$. Normalizing this complex by taking the quotient by degenerate simplices, one obtains the reduced Bar construction $\overline{B}_*(\forget,\Fr{\nontop{n}},X)$, a chain complex calculating $(\derived\Ind{\nontop{n}})X$, which we now describe.
\begin{prop*}
As a vector space each $\overline{B}_r$ is graded, with $\overline{B}_{r,\ell}$
%For $r\geq0$, $\overline{B}_r(\forget,\Fr{\nontop{n}},X)$ is 
spanned by monomials
\[\BarMonomial{I}{\textbf{k}}{x}:=\left[\Q^{i_{k_r+\cdots +k_1}}\cdots \Q^{i_{k_{r-1}+\cdots +k_1+1}}
\middle|\cdots 
\middle|\Q^{i_{k_2+k_1}}\cdots \Q^{i_{k_1+1}}
\middle|\Q^{i_{k_1}}\cdots \Q^{i_1}\right]
x\]
where:
\begin{itemize}
\setlength{\parindent}{.25in}
\item $x\in X_{a_n,\ldots,a_1}$ is a homogeneous element of $X$;
\item $\textbf{k}=(k_r,k_{r-1},\ldots,k_{1})$ is a sequence of positive integers with sum $\ell$;
%\item $0<k_1<k_2<\cdots <k_{r-1}<\ell$ is increasing, so that each bar is nonempty;
\item $I=(i_\ell,\ldots,i_1)$ is a sequence of nonnegative integers with $\minDim(I)<a_n$; and
\item if all of $a_{n-1},\ldots,a_2$ equal zero, $0$ does not appear in $I$.
\end{itemize}
As Adem relations may be applied between each pair of bars, a basis of $\overline{B}_r(\forget,\Fr{\nontop{n}},X)$ consists of all the above monomials in which each of the $r$ subsequences of $I$ is $\Q$-admissible, as $x$ runs through a homogeneous basis for $X$. The formula for the differential is the standard one, making %under the $\ell$ grading on each $\overline{B}_r$ makes
 $\overline{B}_*$ a chain complex with increasing filtration, $F_p\overline{B}_r=\bigoplus_{\ell\geq p}\overline{B}_{r,\ell}$. 
\end{prop*}
\noindent We'll say that a monomial $\BarMonomial{I}{\textbf{k}}{x}\in\overline{B}_r$ is bar-admissible if each of the evident $r$ subsequences of $I$ are $\Q$-admissible. Thus a basis for $\overline{B}_{r,\ell}$ consists of the bar-admissible monomials on a basis of $X$. Note that for any fixed element $x$ and any fixed internal grading $\ell$, the condition on $\minDim(I)$ implies that there are only finitely many monomials of the form $\BarMonomial{I}{\textbf{k}}{x}$ in $\overline{B}_{r,\ell}$.
\begin{prop*}
Any cycle in $\overline{B}_{r,\ell}$, for $\ell>r$ is homologous to a cycle in $\overline{B}_{r,r}$.
\end{prop*}
\begin{proof}
First, a construction. For any bar-admissible monomial $\BarMonomial{I}{\textbf{k}}{x}\in\overline{B}_{r,\ell}$ with $\ell>r$, choose the unique integer $e$ such that $k_r=k_{r-1}=\cdots =k_{r-e+1}=1<k_{r-e}$, so that
\[\BarMonomial{I}{\textbf{k}}{x}=\left[\Q^{i_\ell}\middle|\Q^{i_{\ell-1}} \middle|\Q^{i_{\ell-2}}\middle|\cdots \middle|\Q^{i_{\ell-e+1}}\middle|\Q^{i_{\ell-e}}\Q^{i_{\ell-e-1}}\cdots \middle|\cdots \right]x.\]
That is, we've identified the longest initial segment of length one bars. Then we define
\[\Psi(\BarMonomial{I}{\textbf{k}}{x})=\begin{cases}
0,\textup{ if }(i_{\ell},\ldots,i_{\ell-e})\textup{ is not $\SqShift$-admissible};\\
\left[\Q^{i_\ell}\middle|\Q^{i_{\ell-1}} \middle|\Q^{i_{\ell-2}}\middle|\cdots \middle|\Q^{i_{\ell-e+1}}\middle|\Q^{i_{\ell-e}}\middle|\Q^{i_{\ell-e-1}}\cdots \middle|\cdots \right]x,\textup{ otherwise}.
%\\,&\textup{if }
\end{cases}
\]
Thus $\Psi$ either returns zero or adds a single bar to produce a bar-admissible monomial in $\overline{B}_{r+1,\ell}$. One may extend $\Psi$ by linearity to produce linear operators $\Psi:\overline{B}_{r,\ell}\to\overline{B}_{r+1,\ell}$, for $\ell>r$, and extend $\Psi$ by zero on $\overline{B}_{r,r}$, to produce $\Psi:\overline{B}_{r}\to\overline{B}_{r+1}$.


Put a total preorder on the bar-admissible monomials by saying that
\[\BarMonomial{I}{\textbf{k}}{x}\gtrsim \BarMonomial{I'}{\textbf{k}'}{x'}\textup{ if either } \ell>\ell'\textup{ or }\ell=\ell'\textup{ and }I\geq I'\textup{ lexicographically}.\]
Then, as remarked in \cite[proof of thm 5.3]{PriddyKoszul.pdf}, a straightforward verification shows that for any bar-admissible monomial $m\in\overline{B}_{r,\ell}$ with $r>\ell$, $\partial\Psi(m)+\Psi\partial(m)\equiv m$ modulo strictly lesser monomials.
%Now any element of $\overline{B}_r$ can be written in the form $z=\sum_{j=1}^N \BarMonomial{I^{(j)}}{\textbf{k}^{(j)}}{x^{(j)}}$ for some nonincreasing sequence $\left\{\BarMonomial{I^{(j)}}{\textbf{k}^{(j)}}{x^{(j)}}\right\}$ of monomials. Choose the largest $M$ such that $$

Now suppose that $z\in Z\overline{B}_r$ is a cycle which is not already in $\overline{B}_{r,r}$. Then write 
$z=\sum_i a_i + \sum_j b_j$ where the $a_i$ and $b_j$ are bar-admissible monomials, all of the $a_i$ are equivalent under $\gtrsim$, but $a_i\gnsim b_j$ for all $i$ and $j$. Then $z+\sum_i\partial\Psi(a_i)$ is a homologous cycle in which every monomial appearing (when written as a sum of bar-admissibles) is strictly less than the $a_i$. We may iterate this process, reducing the largest equivalence class of monomials appearing in $z$ at each step. As there are only finitely many possible sequences $I$ appearing, eventually a cycle in $\overline{B}_{r,r}$ is reached.
\end{proof}

\begin{prop*}
Suppose that $X\in\nontop{n}$ is trivial, so that all of the $\Q$ operations act as zero. Then %the differential $\partial $ of $\overline{B}_r$ respects the $\ell$ grading, so that 
$(\derived_r\Ind{\nontop{n}})X$ has a basis $\{\Q(I)x\}$, where
\begin{itemize}
\setlength{\parindent}{.25in}
\item $x\in X_{a_n,\ldots,a_1}$ is an element of a chosen homogeneous basis of $X$;
\item $I=(i_r,\ldots,i_1)$ is a $\SqShift$-admissible sequence with $\minDim(I)<a_n$; and
\item if all of $a_{n-1},\ldots,a_2$ equal zero, $0$ does not appear in $I$.
\end{itemize}
That is, the sequences involved are those $\SqShift$-admissible $I$ such that $Q^Ix$ is defined in $X\in\nontop{n}$.
These classes are defined by the following sum taken over certain non-negative integer sequences $J=(j_{r},\ldots,j_1)$:
\[\Q(I)x:=\left[\Q^{i_r}\middle|\cdots\middle|\Q^{i_1} \right]x+\sum_{\produces{J}{I}{\SqShift}}\left[\Q^{j_r} \middle|\cdots\middle|\Q^{j_1} \right]x.\]%\textup{ (sum over nonnegative sequences $J=(j_{r},\ldots,j_1)$)}\]
\end{prop*}
\noindent Note that if $\produces{J}{I}{\SqShift}$, then $\minDim(J)<\minDim(I)$, and also that if $0$ appears in $I$, it must also appear in $J$ [these facts are Koszul dual to those described in the lemma above for $\Q$]. Thus, all the terms in the definition of $\Q(I)x$ are indeed valid in the bar construction.
\begin{proof}
As $X$ is trivial, the differential of $\overline{B}_r$ respects the $\ell$ grading, so that even the derived functors $(\derived_r\Ind{\nontop{n}})X$ have the extra $\ell$ grading. By the previous proposition, they are concentrated along the diagonal $r=\ell$.

It appears to be easier at this stage to work with the duals $\overline{C}^{r,\ell}$ of the $\overline{B}_{r,\ell}$, and determine the cokernel of $\delta:\overline{C}^{r-1,r}\to\overline{C}^{r,r}$. There is no danger in dualizing twice: $X$, being trivial, is the union of its finite dimensional subobjects, so that we may assume that $X$ is finite dimensional. Fix a basis $\{x\}$ of $X$. %, inducing a dual basis $\{x^*\}$ of $X^*$. 
Then, we have a basis $\{\BarMonomial{I}{\textbf{k}}{x}^*\}$ for $\overline{C}^{*,*}$ dual to the above basis for $\overline{B}_{*,*}$.

Now $\delta:\overline{C}^{r-1,r}\to\overline{C}^{r,r}$ may be described as follows. A basis for $\overline{C}^{r-1,r}$ is given by elements of the form
\[\left(\left[\Q^{i_r}\middle|\cdots\middle|\Q^{i_{m+2}}  \middle|\Q^{i_{m+1}}\Q^{i_m}\middle|\Q^{i_{m-1}}\middle|\cdots \middle|\Q^{i_1} \right]x\right)^*\]
which are duals of bar-admissible monomials. The image under $\delta$ of this class is
\[
\left(\left[\Q^{i_r}\middle|\cdots \middle|\Q^{i_1} \right]x\right)^*
+
\sum_{\produces{(\alpha,\beta)}{(i_{m+1},i_m)}{\Q}}\left(\left[\Q^{i_r}\middle|\cdots\middle|\Q^{i_{m+2}}  \middle|\Q^{\alpha}\middle|\Q^{\beta}\middle|\Q^{i_{m-1}}\middle|\cdots \middle|\Q^{i_1} \right]x\right)^*\]
We are working in the cobar construction, which is naturally viewed as the \emph{quotient} of the standard cobar construction $C(\F_2,\DyerLashov,X)$ by those cobars not satisfying our unstable condition. Thus, in the right hand side of the above expression, any summands with $\minDim(I)\geq|x|$ or which fail the condition on $\Q^0$ are taken to be zero.
%
%Where, if $x\in X_{a_n,\ldots,a_1}$:
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item we omit those summands in which $\minDim(i_{r},\ldots,i_1)\geq a_n$; and
%\item if all of $a_{n-1},\ldots,a_2$ are zero, we omit any summands with $i_m=0$ or $i_{m+1}=0$.
%\end{itemise}
The term with $(i_{m+1},i_m)=(\alpha,\beta)$ is not omitted. Moreover, for length 2 sequences $K$ and $L$, as $\Q$ and $\SqShift$ are Koszul dual, $\produces{K}{L}{\Q}$ if and only if $\produces{L}{K}{\SqShift}$. Thus, we obtain a relation:
\[\left(\left[\Q^{i_r}\middle|\cdots \middle|\Q^{i_1} \right]x\right)^*
=
\sum_{\produces{(i_{m+1},i_m)}{(\alpha,\beta)}{\SqShift}}\left(\left[\Q^{i_r}\middle|\cdots\middle|\Q^{i_{m+2}}  \middle|\Q^{\alpha}\middle|\Q^{\beta}\middle|\Q^{i_{m-1}}\middle|\cdots \middle|\Q^{i_1} \right]x\right)^*\]
where we make the same omissions on the right hand side. Thus, the relation here is simply the $\SqShift$-Adem relation.
Using this relation, we see that a basis of $H^{r,r}\overline{C}$ is represented by the cocycles $\BarMonomial{I}{\textbf{k}}{x}^*$, where $I$, and $x$ are as in the statement of of this proposition (and $\textbf{k}=(1,\ldots,1)$).

As long as each $\Q(I)x$ is a cycle, they will form the dual basis for $H_{rr}\overline{B}$, as in the sum defining $\Q(I)x$, the only $\SqShift$-admissible $J$ appearing is $J=I$. In order to check that each $\Q(I)x$ is a cycle, it only remains to check that they pair to zero with each relation in the dual. But that is not hard to see. On $\overline{C}^{r,r}$, by definition of $\Q(I)x$, the operation `pair with $\Q(I)x$' \emph{equals} the operation `reduce to $\SqShift$-admissible form using $\SqShift$-Adem relations, and take the coefficient of $(\left[\Q^{i_\ell}\middle|\cdots\middle|\Q^{i_1} \right]x)^*$'. This second operation obviously returns zero on Adem relations, and these are precisely the image of $\delta$.
\end{proof}
\begin{prop*}
Suppose instead that $X$ is any object in $\nontop{n}$, the Koszul complex $\overline{K}_*X$ is the subcomplex of $\overline{B}_*(\forget,\Fr{\nontop{n}},X)$ with basis the classes $\Q(I)x$ (for the same $I$ and $x$ as above). The inclusion of $\overline{K}_*X$ into $\overline{B}_*(\forget,\Fr{\nontop{n}},X)$ is a homology equivalence, the restriction of the differential to $\overline{K}_*X$ is given by the following formula:
\[\partial(\Q(I)x)=\Q((i_{\ell},\ldots,i_2))(\Q^{i_1}x)+\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\sum_{\substack{\produces{J}{I}{\SqShift}\\(j_{\ell},\ldots,j_2)\in\admis{\SqShift}}}\!\!\!\!\!\!\!\!\!\!\!\! \Q((j_{\ell},\ldots,j_2))(\Q^{j_1}x),\]
where the sum is taken over those $J=(j_{\ell},\ldots,j_1)$ such that $(j_{\ell},\ldots,j_2)$ is $\SqShift$-admissible.
\end{prop*}
\begin{proof}
The spectral sequence associated to the filtered complex has $E^0_{r,\ell}=\overline{B}_{r,\ell}(\forget,\Fr{\nontop{n}},X^\textup{Triv})$, where $X^\textup{Triv}$ is a trivial object of $\nontop{n}$ on the same underlying vector space as $X$. The differential $d^0$ implements the differential on this reduced bar construction, so that $E^1_{r,\ell}=(\derived_{r,\ell}\Ind{\nontop{n}})X$. This is concentrated on $r=\ell$, so that $d^1$ is the last nonzero differential, after which the spectral sequence collapses.

The formula for $d^1:E^1_{r,r}\to E^1_{r-1,r-1}$ is simply:
\[\sum_j \left[\Q^{i_r^{(j)}}\middle|\cdots \middle|\Q^{i_1^{(j)}}\right]x^{(j)}
\mapsto
\sum_j \left[\Q^{i_r^{(j)}}\middle|\cdots \middle|\Q^{i_2^{(j)}}\right]\left(\Q^{i_1^{(j)}}x^{(j)}\right)\]
Now as $E^1_{r,r}\subseteq E^0_{r,r}$, in order to write this in terms of the $\Q(I)x$ we need only focus on the terms involving $\SqShift$-admissible sequences, and the formula for $\partial$ follows.
\end{proof}


\end{KoszulComplexes2plus}


\begin{KoszulComplexes1}
\subsection{Koszul complexes for $\derived\Ind{\nontop{1}}$}
We'll record here the necessary changes to the previous theory required when $n=1$.

%\textbf{remove} For $I=(i_\ell,\ldots,i_1)$ a sequence of integers with each $i_j\geq2$, define
%\[\minDimP(I):=\begin{cases}
%-\infty,&\textup{if }I=\emptyset;\\
%\max\{(i_1),\,(i_2-i_1-1)\,(i_3-i_2-i_1-2),\,\ldots,\,(i_{\ell}-i_{\ell-1}-\cdots i_1-\ell+1)\},&\textup{otherwise}.
%%\\,&\textup{if }
%\end{cases}
%\]
%Thus, for $I\neq\emptyset$, $\minDimP(I)$ is the lowest dimension $d\geq0$ such that $P^Ix$ may be nonzero, for $x$ a $d$-dimensional element of an object in either $\LL{1}$ or $\nontop{1}$.

%\subsubsection{The unstable bar construction and Koszul complex for $\nontop{1}$}
We are again interested in the reduced Bar construction $\overline{B}_*(\forget,\Fr{\nontop{1}},X)$, which computes $(\derived\Ind{\nontop{1}})X$.

%\begin{lem*}
%Suppose that $i\geq2j$, and $\produces{(i,j)}{(i',j')}{P}$. Then $\minDimP(i',j') > \minDimP(i,j)$.
%\end{lem*}
%\begin{proof}
%$j'\geq i-j+1=
%j+(i-2j+1)=
%i-j-1+(2)
%$, so that $j'>\max\{j,i-j-1\}$.
%\end{proof}

\begin{prop*}
As a vector space each $\overline{B}_r$ is graded, with $\overline{B}_{r,\ell}$
%For $r\geq0$, $\overline{B}_r(\forget,\Fr{\nontop{n}},X)$ is 
spanned by monomials
\[\BarMonomial{I}{\textbf{k}}{x}:=\left[P^{i_{k_r+\cdots +k_1}}\cdots P^{i_{k_{r-1}+\cdots +k_1+1}}
\middle|\cdots 
\middle|P^{i_{k_2+k_1}}\cdots P^{i_{k_1+1}}
\middle|P^{i_{k_1}}\cdots P^{i_1}\right]
x\]
where:
\begin{itemize}
\setlength{\parindent}{.25in}
\item $x\in X_{a_1}$ is a homogeneous element of $X$;
\item $\textbf{k}=(k_r,k_{r-1},\ldots,k_{1})$ is a sequence of positive integers with sum $\ell$; and
\item $I=(i_\ell,\ldots,i_1)$ is a sequence of integers with $i_j\geq2$ and $\minDimP(I)<a_1$;
\end{itemize}
As Adem relations may be applied between each pair of bars, a basis of $\overline{B}_r(\forget,\Fr{\nontop{1}},X)$ consists of all the above monomials in which each of the $r$ subsequences of $I$ is $P$-admissible, as $x$ runs through a homogeneous basis for $X$. The formula for the differential is the standard one, making %under the $\ell$ grading on each $\overline{B}_r$ makes
 $\overline{B}_*$ a chain complex with increasing filtration, $F_p\overline{B}_r=\bigoplus_{\ell\geq p}\overline{B}_{r,\ell}$. 
\end{prop*}


\begin{prop*}
Suppose that $X$ is any object in $\nontop{1}$, the Koszul complex $\overline{K}_*X$ is the subcomplex of $\overline{B}_*(\forget,\Fr{\nontop{1}},X)$ with basis the classes $P(I)x$, where 
\begin{itemize}
\setlength{\parindent}{.25in}
\item $x\in X_{a_1}$ is an element of a chosen homogeneous basis of $X$;  and
\item $I=(i_r,\ldots,i_1)$ a $\delta$-admissible sequence with $i_j\geq2$ and $\minDimP(I)\leq a_1$.
\end{itemize}
and where 
\[P(I)x:=\left[P^{i_r} \middle|\cdots\middle|P^{i_1} \right]x+\sum_{\substack{\produces{J}{I}{\delta} \\ \minDimP(J)\leq|x|}}\left[P^{j_r} \middle|\cdots\middle|P^{j_1} \right]x.\]
The inclusion of $\overline{K}_*X$ into $\overline{B}_*(\forget,\Fr{\nontop{1}},X)$ is a homology equivalence, the restriction of the differential to $\overline{K}_*X$ is given by the following formula:
\[\partial(P(I)x)=P((i_{\ell},\ldots,i_2))(P^{i_1}x)+\sum_{\substack{\produces{J}{I}{\delta} \\ \minDimP(J)\leq|x|}} P((j_{\ell},\ldots,j_2))(P^{j_1}x),\]
where the sum is taken over those $J=(j_{\ell},\ldots,j_1)$ such that $(j_{\ell},\ldots,j_2)$ is $\delta$-admissible.
\end{prop*}
\begin{proof}
The proof of this proposition is the same as the proof of the corresponding propositions in the $n\geq2$ case. We use the same algorithm to compress to the diagonal, and the same spectral sequence. There are two main differences between the two cases:

In the $n\geq2$ case, the structure of an element of $\nontop{n}$ only has non-top $\Q$ operations, so that the various constraints on $\minDim(I)$ were strict. On the other hand, elements of $\nontop{1}$ support all the $P$ operations, so that the inequalities are not strict.

In the $n\geq2$ case, the bar construction was the subobject of a stable bar construction, and the cobar was a quotient. Thus, our final formula didn't contain any extraneous terms, but our interim calculation with the cobar construction did. When $n=1$, this situation is reversed, so that our results land in a quotient, and certain summands therein are zero.
%
%Note that in the $n=1$ case, there are no summands to omit in the formula for $\delta:\overline{C}^{r-1,r}\to\overline{C}^{r,r}$. [Really, in the $n\geq2$ case, the formula for $\delta$ lands in the quotient by inadmissible terms, while in the $n=1$ case, $\delta$ lands in the subcomplex of admissible terms. This is, of course, dual to the situation in the Bar construction or in the free $\nontop{n}$ construction.] For example, in the $n=1$ case, if $\produces{J}{I}{\delta}$, then $\minDimP(J)\geq\minDimP(I)$, which is the opposite to the inequality in the $n\geq2$ case. However, all of the above summands are defined, even those with $\minDimP(J)>|x|$ --- it's just that those summands are zero, due to the unstable condition for $P$. Thus, when in the above, we include a second subscript on the sums, it's just that the sum would contain extra terms, all automatically zero, if we didn't.
\end{proof}
\end{KoszulComplexes1}


\begin{DerivedFunctorsLowDimension}
\section{Lie algebra homology and low dimensional calculations}
\subsection{Calculating $\derived\Ind{\LL{n}}$ in internal dimension zero}
Suppose that $n\geq2$. Then the dimension zero part of an object $X$ of $\LL{n}$ is a partially restricted Lie algebra, in $\PRLie{n-1}$. That is: 
\begin{lem*}
There is a `zeroth part' functor $\LL{n}\to\PRLie{n-1}$, written $X\mapsto X_0$, where $X_0\in\PRLie{n-1}$ by
\[(X_0)_{a_{n-1},\ldots,a_1}:=X_{0,a_{n-1},\ldots,a_1}\]
with bracket inherited from the on $X$, and restriction $\restn{}$ given by $\Q^0$. Moreover, taking zeroth parts commutes with the two free constructions, which is to say that for $S\in\GS{n}$, we have $(\Fr{\LL{n}}S)_0\cong\Fr{\PRLie{n-1}}(S_0)$, writing $S_0\in\GS{n-1}$ for the zeroth part of $S$.
\end{lem*}
\begin{proof}
As objects of $\LL{n}$ are themselves objects of $\PRLie{n}$, with restriction given by $\Q^0$ in dimension zero, it's enough just to check that $\Q^0$ is defined on $X_{0,a_{n-1},\ldots,a_1}$ whenever $\restn{}$ is supposed to be defined on a dimension $(a_{n-1},\ldots,a_1)$ element of an object of $\PRLie{n-1}$. This follows from the definition.

Now to check that the free constructions agree, recall that  $\Fr{\LL{n}}S$ has basis 
\[\{\Q^Ib\,:\,b\in B_{a_{n},\ldots,a_1},\,I\in\admis{\Q},\ i_1\leq|b|,\ i_1,a_{n-1},\ldots,a_2\textup{ not all zero}\}\]
where $b$ runs over a homogeneous Hall basis. The only basis elements in the zeroth part are those where $b$ is zero dimensional and in which $I$ only contains zeros, and these classes are exactly a basis for $\Fr{\PRLie{n-1}}(S_0)$.
\end{proof}
\begin{prop*}
There is a natural isomorphism
\[((\derived_{p}\Ind{\LL{n}})X)_{0,a_{n-1},\ldots,a_1}\cong ((\derived_p\Ind{\PRLie{n-1}})X_0)_{a_{n-1},\ldots,a_1}\]
\begin{proof}
Consider the bar construction used to define $((\derived_{p}\Ind{\LL{n}})X)_{0,a_{n-1},\ldots,a_1}$, constructed by repeated application of the free ${\LL{n}}$ functor. In dimension zero, this amounts to repeated application of the free $\PRLie{n-1}$ functor, and we obtain the bar construction for $X_0$ as an object of $\PRLie{n-1}$.
\end{proof}
\end{prop*}
%\subsubsection{$\derived\Ind{\LL{1}}$}
\begin{shaded}
Choose $n\geq 1$, and define 
\[d=\begin{cases}
4,&\textup{if }n=1;\\
1,&\textup{if }n=2;
\\0,&\textup{if }n\geq3.
\end{cases}
\]
We will here present a method to calculate the object $(\derived\Ind{\LL{n}})X=((\derived\Ind{\LL{n}})X)_{a_{n+1},\ldots,a_1}$ in dimensions with $a_n\leq d$. Consider the diagram:
\[\xymatrix@R=2mm@C=13mm{
&%r1c1
\ar[dd]^-{\Ind{\nontop{n}}}
\ar@<.5ex>[dl]%^-{\forget}
\LL{n}\\%r1c2
\ar@<.5ex>[ur]^-{\LL{n}}
\ar@<.5ex>[dr]^-{\PRLie{n}}
\GR{n}&%r2c1
\\%r2c2
&%r3c1
\PRLie{n}
\ar@<.5ex>[ul]%^-{\forget}
%r3c2
}\]
In this diagram, $\Ind{\nontop{n}}$ does not change the underlying vector space in dimensions $(a_n,\ldots,a_1)$ with $a_n\leq d$. Moreover, the free constructions $\Fr{\LL{n}}$ and $\Fr{\PRLie{n}}$ agree in these dimensions, as do the structure maps of the free/forget adjunctions. Thus, there is an isomorphism between $(\derived\Ind{\LL{n}})(X)$ and $(\derived\Ind{\PRLie{n}})(\Ind{\nontop{n}}(X))$ in dimensions with $a_n\leq d$. [Note that these are objects of $\GR{n+1}$, and so have gradings $a_{n+1},\ldots,a_1$ --- our inequality involves $a_n$, the outermost grading of an object of $\LL{n}$.]
\end{shaded}

There is a complex that computes $\derived\Ind{\PRLie{n}}$ --- it interpolates between the Cartan-Eilenberg resolution for the homology of good Lie algebras, and May's $\overline{X}$ complex for  restricted Lie algebra homology.
\end{DerivedFunctorsLowDimension}

\begin{PRlieKoszulComplexCalculation}

\subsection{The Cartan-Eilenberg-May complex for partially restricted Lie algebra homology}
The PBW theorem states that $E^0VL=A(L^u)\otimes E(L^r)$, and the homology of this algebra (see \cite[\S7]{PriddyKoszul.pdf}) is thus $E(L^u)\otimes \Gamma(L^r)$. We'll think of this as the sub-coalgebra of $\Gamma(L)$ in which there are no $\gamma_i$ for $i>1$ applied to unrestrictable elements. It's the shuffle product that produces representatives in $\overline{B}(E^0V(L))$ for classes in $E(L^u)\otimes \Gamma(L^r)$, and in order to calculate with these representatives, we first introduce some notation.
\begin{itemize}
\setlength{\parindent}{.25in}
\item $\Z^n:=\{\textbf{z}=(z_1,\ldots,z_n);\ z_i\in\Z\}$
\item $r_i:\Z^n\to\Z^n$ given by $(z_1,\ldots,z_n)\mapsto(z_1,\ldots,z_i-1,\ldots,z_n)$
\item $r_{ij}:=r_i\circ r_j:\Z^n\to\Z^n$
\item $\sigma:\Z^n\to\Z$ given by summing entries
\item for $\textbf{z}\in\Z^n$ write $\calP(\textbf{z})$ for the set of permutations of the multiset $\{i^{z_i};i=1,\ldots,n\}$, written as sequences $\textbf{p}=(p_1,\ldots,p_{\sigma \textbf{z}})$. This set is empty if $\textbf{z}$ has a negative entry. For such a $\textbf{p}$, write $p\sigma_i$ for $(p_1,\ldots,p_{i-1},p_{i+1},p_{i},p_{i+2},\ldots,p_{\sigma \textbf{z}})$.
\item $d_k:\calP(\textbf{z})\to\calP((r_{p_kp_{k+1}}\textbf{z})*(1))$ (the star denotes concatenation), in which $(p_1,\ldots,p_{\sigma \textbf{z}})$ is sent to $(p_1,\ldots,p_{k-1},\ell(\textbf{z})+1,p_{k+2},\ldots,p_{\sigma \textbf{z}})$. That is, two entries are removed, and in their position we place a single entry, $\ell(\textbf{z})+1$.
\end{itemize}
\begin{prop*}
Choose $\textbf{z}\in\Z^n$, and $i$ satisfying $1\leq i\leq n$. Then as $k$ ranges from $1$ to $\sigma \textbf{z}-1$, and $\textbf{p}$ ranges through those elements of $\calP(\textbf{z})$ satisfying $(p_k,p_{k+1})=(i,i)$, then $d_kp$ assumes each value in $\calP((r_{ii}\textbf{z})*(1))$ exactly once.
\end{prop*}
\begin{prop*}
Choose $\textbf{z}\in\Z^n$, and $i\neq j$ satisfying $1\leq i,j\leq n$. Then as $k$ ranges from $1$ to $\sigma \textbf{z}-1$, and $\textbf{p}$ ranges through those elements of $\calP(\textbf{z})$ satisfying $(p_k,p_{k+1})=(i,j)$, then $d_k\textbf{p}$ assumes each value in $\calP((r_{ij}\textbf{z})*(1))$ exactly once. This occurs symmetrically in $i$ and $j$, which is to say that for such a pair $(k,\textbf{p})$, the pair $(k,\textbf{p}\sigma_k)$ works with $i$ and $j$ swapped, and we have $d_k(\textbf{p}\sigma_k)=d_k(\textbf{p})$.
\end{prop*}


We can respresent a product $\prod_{i=1}^{n}\gamma_{z_i}(x_i)$ in $E(L^u)\otimes \Gamma(L^r)$ by a class $\left\langle \textbf{z},\textbf{x}\right\rangle$ in $\overline{B}(E^0V(L))$ which we now define:

\begin{itemize}
\setlength{\parindent}{.25in}
\item $(hL)^n:=\{\textbf{x}=(x_1,\ldots,x_n);\ x_i\textup{ homogeneous in }V(L)\}$
%\item $d_{ij}:(hL)^n\to(hL)^{n+1}$ given by $\textbf{x}\mapsto\textbf{x}*(x_ix_j)$
%\item $b_{ij}:(hL)^n\to(hL)^{n+1}$ given by $\textbf{x}\mapsto\textbf{x}*([x_i,x_j])$
\item Choose $\textbf{x}\in(hL)^n$, $\textbf{z}\in\Z^n$ and $\textbf{p}\in\calP(\textbf{z}).$ Then define $\left\langle \textbf{p},\textbf{x}\right\rangle\in\overline{B}_{\sigma\textbf{z},*}(E^0V(L))$ to be the bar $[x_{p_1},\ldots,x_{p_{\sigma\textbf{z}}}]$. Then define $\left\langle \textbf{z},\textbf{x}\right\rangle:= \sum_{\textbf{p}\in\calP(\textbf{z})}\left\langle \textbf{p},\textbf{x}\right\rangle$. 
\end{itemize}
Now $\overline{K}_*(V(L)):=H_{*=*}(E^0V(L))$ is spanned by the bars $\left\langle \textbf{z},\textbf{x}\right\rangle$ where each $x_i$ is a homogeneous element of $L$, which must be restrictable if $z_i>1$ (here, $\sigma\textbf{z}$ is the homological degree). In fact, there's a basis consisting of the $\left\langle \textbf{z},\textbf{x}\right\rangle$ where $\textbf{x}$ runs over (strictly) increasing sequences of elements of an ordered basis chosen for $L$, and the same restrictability condition holds.

Finally we may calculate the differential on $\overline{K}_*(V(L))$. Here goes:
\begin{alignat*}{2}
d\left\langle \textbf{z},\textbf{x}\right\rangle
&=
\sum_{k=1}^{\sigma\textbf{z}-1} \sum_{\textbf{p}\in\calP(\textbf{z})}d_k\left\langle \textbf{p},\textbf{x}\right\rangle%
\\
%&=
%\sum_{k}\sum_{\textbf{p}}\left\langle d_k\textbf{p},d_{p_kp_{k+1}}\textbf{x}\right\rangle%
%\\
&=
\sum_{i=1}^{n}\sum_{j=1}^{n}\sum_{k}\sum_{\textbf{p}:{p_k=i\atop p_{k+1}=j}}\left\langle d_k\textbf{p},\textbf{x}*(x_{p_k}x_{p_{k+1}})\right\rangle%
\\
&=
\sum_{i}\sum_{k}\sum_{\textbf{p}:{p_k=i\atop p_{k+1}=i}}\left\langle d_k\textbf{p},\textbf{x}*(x_ix_i)\right\rangle+\sum_{i<j} \sum_{k}\sum_{\textbf{p}:{p_k=i\atop p_{k+1}=j}}\left\langle d_k\textbf{p},\textbf{x}*(x_ix_j+x_jx_i)\right\rangle%
\\
&=
\sum_{i}\sum_{k}\sum_{\textbf{p}:{p_k=i\atop p_{k+1}=i}}\left\langle d_k\textbf{p},\textbf{x}*\left(\restn{(x_i)}\right)\right\rangle+ \sum_{i<j}\sum_{k}\sum_{\textbf{p}:{p_k=i\atop p_{k+1}=j}}\left\langle d_k\textbf{p},\textbf{x}*\left([x_i,x_j]\right)\right\rangle%
\\
&=
\sum_{i}\sum_{\textbf{q}\in\calP((r_{ii}\textbf{z})*(1))}\left\langle \textbf{q},\textbf{x}*\left(\restn{(x_i)}\right)\right\rangle+\sum_{i<j} \sum_{\textbf{q}\in\calP((r_{ij}\textbf{z})*(1))}\left\langle \textbf{q},\textbf{x}*\left([x_i,x_j]\right)\right\rangle%
\\
% Left hand side
% Relation
&=
% Right hand side
\sum_{i}\left\langle (r_{ii}\textbf{z})*(1),\textbf{x}*\left(\restn{(x_i)}\right)\right\rangle+\sum_{i<j} \left\langle (r_{ij}\textbf{z})*(1),\textbf{x}*\left([x_i,x_j]\right)\right\rangle%
% Comment
\end{alignat*}
This is the obvious restriction of May's $\overline{X}$, see page 141 of ``The cohomology of restricted Lie algebras and of Hopf algebras'' (J.\ Alg.\ 3). We use the subspace with fewer $\gamma_i$, and the differential he gives makes sense on and preserves this subspace, and coincides with that here.

He writes the differential on $f=\prod_{i=1}^{n}\gamma_{z_i}(y_i)$ as
\[d(f)=\left(\sum_{i=1}^{n}f_iy_i\right)+ \sum_{i=1}^{n}f_{i,i}\gamma_1(\restn{(y_i)})+\sum_{1\leq i<j\leq n}f_{i,j}\gamma_1([y_i,y_j]).\]
Here, the parenthetical term vanishes in $\overline{K}$ --- it's there in case we're using nontrivial coefficients.
\end{PRlieKoszulComplexCalculation}

\begin{LieLambdaStructureOnKoszul}
\section{Structure on the derived functors $(\derived\Ind{\nontop{n}})X$}
\subsection{Constructions in the homotopy of simplicial Lie algebras}
We showed above that $\PiAlg{\PRLie{n}}$ is in fact $\LL{n+1}$, which is to say that the homotopy of a simplicial object of $\PRLie{n}$ in fact supports both $\Q$ operations and a Lie bracket, giving the structure of an element of $\LL{n+1}$. The chain level constructions of these operations are standard, and we record them here for convenience:

Let $\frakg$ be a simplicial Lie algebra over $\F_2$. Let $N\frakg_*$ be the Moore complex of $\frakg$, defined as
\[N\frakg_n:=\bigcap_{i=0}^{n-1}\ker(d_i:\frakg_n\to\frakg_{n-1})\textup{ with differential }\partial:=d_n|_{{N\frakg}_n}.\]
Then $N\frakg_*$ is a differential graded Lie algebra, under the map
\[N\frakg_*\otimes N\frakg_*\overset{\nabla}{\to}N(\frakg_*\otimes \frakg_*)\to N\frakg_*.\]
Here, $\Delta$ is the Eilenberg-Zilber map, or `shuffle map'. Thus, when $|z|=n$ and $|w|=m$:
\[z\otimes w\overset{\nabla}{\mapsto}\sum_{(\alpha,\beta)\in\Shuffles{p}{q}}s_\beta z\otimes s_\alpha w\mapsto \sum_{(\alpha,\beta)}[s_\beta z, s_\alpha w].\]
Here, $\Shuffles{p}{q}$ is the set of $(p,q)$-shuffles, pairs $(\alpha,\beta)$ with $\alpha=(\alpha_p,\ldots,\alpha_1)$ and $\beta=(\beta_q,\ldots,\beta_1)$ monotonically decreasing sequences that together partition the set $\{0,\ldots,p+q-1\}$.

Next, we have operations $\Q^i:N\frakg_n\to N\frakg_{n+i}$, defined for $0<i\leq n$, by the following formula:
\[z\mapsto \sum_{{(\alpha,\beta)\in\HalfShuffles{i}{i}}}[s_\beta z, s_\alpha z].\]
Here, $\HalfShuffles{i}{i}$ consists of those elements $(\alpha,\beta)$ of $\Shuffles{i}{i}$ such that $\alpha_1=0$.
One notes that as $i\leq n$, the expressions $s_\alpha z$ and $s_\beta z$ both still make sense, and that when $i=n$, this formula is one half of the formula for ``$[z,z]$'' (in $N\frakg_*$).

Finally, if $\frakg$ supports a partial restriction on a subspace $\frakg^r$, we have an operation $\Q^0:N\frakg^r_n\to N\frakg_n$, defined simply by $z\mapsto\restn(z)$.

\begin{lem*}
Choose $i\geq0$ and $\alpha=(\alpha_p,\ldots,\alpha_1)$ with $\alpha_p>\cdots >\alpha_1\geq0$.
\begin{enumerate}[i)]\squishlist
\setlength{\parindent}{.25in}
\item If neither $i$ nor $i-1$ appear in $\alpha$, then  $d_is_\alpha=s_{\alpha_p-1}\cdots s_{\alpha_{c+1}-1}s_{\alpha_c}\cdots s_{\alpha_1}d_{i-c}$; and
\item if one of $i$ and $i-1$ appears in $\alpha$, then  $d_is_\alpha=s_{\alpha_p-1}\cdots s_{\alpha_{c+1}-1}s_{\alpha_{c-1}}\cdots s_{\alpha_1}$.
\end{enumerate}
Here, $c$ is the index such that $\alpha_{c+1}>i\geq\alpha_{c}$, after setting  $\alpha_{p+1}=\infty$ and $\alpha_0=-\infty$. More crudely:
\begin{enumerate}[i)]\squishlist
\setlength{\parindent}{.25in}
\item[iii)] if neither $i$ nor $i-1$ appear in $\alpha$, then  $d_is_\alpha=s_{\alpha'}d_{i'}$ for some $\alpha'$ and $i'$; and
\item[iv)] if exactly one of $i$ and $i-1$ appears in $\alpha$, then  $d_is_\alpha$ does not depend on which of $i$ and $i-1$ appeared.
\end{enumerate}
\end{lem*}
\subsection{Chain level operations and the Koszul complex}

For this discussion, fix an object $X\in\LL{n}$.
The Koszul complex $\overline{K}_*(X)$ is a subcomplex of the bar construction $\overline{B_*}(\forget,\nontop{n},X)$. However, we would prefer to work in the Moore complex $N{B_*}(\forget,\nontop{n},X)$. That is, for any simplicial abelian group $A$, in this case $A=B(\forget,\nontop{n},X)$, there are natural weak equivalences
\[NA_*\to A_*\to (A/DA)_*\]
of which the first is an inclusion, the second is a surjection, and the composite is an isomorphism. Giving the inverse isomorphism could be a little difficult: this theorem shows that for any $z\in A_n$, there is a unique degenerate element $b$ such that $z+b\in NA_n$, but one must find this $b$.

Fortunately, it happens that the Koszul complex already maps happily into $N{B_*}(\forget,\nontop{n},X)$. To understand this, one thinks that an element of the Koszul complex is an element of the Bar construction which survives to $E^1$ in the length filtration spectral sequence for $\overline{B}_*$. However, $d^0$ implements the sum of all the face maps but one, so that a generic element of $\overline{K}_r$ is the image in $\overline{B}_{rr}$ of an expression
\[z=\sum_{j}\left[\Q^{i_{j,r}} \middle|\cdots\middle|\Q^{i_{j,1}} \right]x_j\textup{ in }B_{r}\]
such that 
\[\sum_{k=1}^{r}d_kz:=\sum_{k=1}^{r-1}\sum_{j}\left[\Q^{i_{j,r}} \middle|\cdots\middle|\Q^{i_{j,k+1}}\Q^{i_{j,k}}\middle|\cdots\middle|\Q^{i_{j,1}} \right]x_j=0\textup{ in }\overline{B}_{r-1,r}.\]
However, the fact that we quotient by degenerate elements in forming $\overline{B}$ is irrelevant to this condition, so that for $k\neq 0$, $d_kz=0$ in $B_{r-1}$, not only in $\overline{B}_{r-1}$, and $z\in NB_r$, no `$b$' required. One swaps $\Q$ for $P$ when $n=1$.

Moreover, there is a natural map \textbf{(???)} ${B_*}(\forget,\nontop{n},X)\to {B_*}(\PRLie{n},\LL{n},X)$. Let $\jmath$ be the following composite of inclusions which are homology equivalences:
\[\jmath:\left(\overline{K}_*(X)\to  NB_*(\forget,\nontop{n},X)\to N{B_*}(\PRLie{n},\LL{n},X)\right).\]

At this point we need to be explicit about the maps inside the bar construction. Moreover, we'll need notation for elements of $B(\PRLie{n},\LL{n},X)$, and the bar notation we've used so far will not suffice. The bar construction is given by the formula $B_r:=\Fr{\PRLie{n}}\left(\Fr{\LL{n}}\right)^rX$, and we'll add subscripts to the various free constructions here in order to disambiguate them in what follows, writing
\[B_r:=\Fr[out]{\PRLie{n}}\Fr[r]{\LL{n}}\cdots\Fr[1]{\LL{n}} X.\]
Here, $out$ stands for `outer'. We'll index the faces and degeneracies in the opposite order to the usual one, and inexpensive way to keep notation simple. Thus:
\begin{itemize}\squishlist
\setlength{\parindent}{.25in}
\item $d_0:B_r\to B_{r-1}$ is induced by $\Fr[1]{\LL{n}}X\to X$;
\item $d_i:B_r\to B_{r-1}$ is induced by $\Fr[i+1]{\LL{n}}\Fr[i]{\LL{n}}\to \Fr[i]{\LL{n}}$ for $0<i<r$;
\item $d_r:B_r\to B_{r-1}$ is induced by $\Fr[out]{\PRLie{n}}\Fr[r]{\LL{n}}\to \Fr[out]{\PRLie{n}}$ (which, for $n\geq2$, kills nontop $\Q^i$ terms and identifies the top $\Q$ with $\restn{}$, and when $n=1$, kills all $P$ operations);
\item $s_i:B_r\to B_{r+1}$ is induced by the unit map, after inserting another $\Fr{\LL{n}}$ between $\Fr[i+1]{\LL{n}}$ and $\Fr[i]{\LL{n}}$ , for $0\leq i\leq r$.
\end{itemize}


We'll also include the subscripts in notation for the elements of $B_r$, for example, here are two elements of $B_3$ (when $n\geq2$), if $x,y\in X$ are of sufficiently large degrees:
\[[[x,\Q^3_2y]_3,\Q^5_1x]_{out}\textup{\quad and\quad }\restn[out]{([\Q^4_2\Q^3_1x,y]_3)}.\]
%The second expression means, for $x,y\in X$, form $\Q^3_1x\in\Fr{\LL{n}}X$.....
Then we may describe $\jmath$ simply as
\[\left[\Q^{i_{r}} \middle|\cdots\middle|\Q^{i_{1}} \right]x\mapsto\Q^{i_{r}}_r\cdots \Q^{i_{1}}_1x.\]


We are then in a position to calculate the $\LL{n+1}$ structure on $(\derived\Ind{\nontop{n}})X$ in certain cases, since we can write down chain-level formulae. For $z\in Z\overline{K}_p(X)$ and $w\in Z\overline{K}_q(X)$, representing classes $\overline{z},\overline{w}\in(\derived\Ind{\nontop{n}})X$:
\begin{itemise}
\setlength{\parindent}{.25in}
\item $[\overline{z},\overline{w}]$ is represented by $\sum_{(\alpha,\beta)\in\Shuffles{p}{q}}[s_\beta(\jmath z), s_\alpha(\jmath w)]_{out}$;
\item $Q^i\overline{z}$ is represented by $\sum_{(\alpha,\beta)\in\HalfShuffles{i}{i}}[s_\beta(\jmath z), s_\alpha(\jmath z)]_{out}$ for $0<i\leq p$; and
\item $Q^0\overline{z}$ is represented by $\restn[out]{(z)}$ if not all of $a_n,\ldots,a_2$ are zero, where $\overline{z}\in((\derived_{p}\Ind{\nontop{n}})X)_{a_n,\ldots,a_1}$.
\end{itemise}
\subsection{Lie brackets on $(\derived\Ind{\nontop{n}})X$ are trivial}
\begin{prop*}
Suppose that $z\in Z\overline{K}_p(X)$ and $w\in Z\overline{K}_q(X)$ are cycles. Then on homotopy classes:% representing classes $\overline{x}$ and $\overline{y}$. Then
\[[\overline{z},\overline{w}]=\begin{cases}
\overline{[z,w]},&\textup{if }p=q=0;\\
0,&\textup{otherwise}.
%\\,&\textup{if }
\end{cases}
\]
Here, $Z\overline{K}_0(X)=X$ has the Lie bracket supplied by the $\LL{n}$ structure of $X$.
%Suppose that $p>0$ and $q>0$. Then $[\overline{x},\overline{y}]=0$ for cycles $x\in Z\overline{K}_p(X)$ and $y\in Z\overline{K}_q(X)$.
\end{prop*}
\begin{proof}
We perform the proof for $n\geq2$, but it works the same way for $n=1$, when one substitutes $\Q$ operations for $P$ operations and ignores all discussion of top and non-top operations.

Consider the following element of $B_{p+q+1}$:
\[a:=\sum_{(\alpha,\beta)\in\Shuffles{p}{q}}[s_{p+q}s_\beta(\jmath z), s_{p+q}s_\alpha(\jmath w)]_{p+q+1}\]
We'll calculate $d_ia$ for $i=0,\ldots,p+q+1$, and find that $d_ia=0$ for $i<p+q+1$ (except if $p=q=0$), and $d_{p+q+1}a$ is our formula for $[\overline{z},\overline{w}]$. Firstly, as $d_{p+q+1}$ applies $\Fr[out]{\PRLie{n}}\Fr[p+q+1]{\LL{n}}\to\Fr[out]{\PRLie{n}}$, $d_{p+q+1}a$ represents $[\overline{z},\overline{w}]$:
\[d_{p+q+1}a=\sum [d_{p+q+1}s_{p+q}s_\beta(\jmath z), d_{p+q+1}s_{p+q}s_\alpha(\jmath w)]_{out}=\sum [s_\beta(\jmath z), s_\alpha(\jmath w)]_{out}.\]
Next, we calculate $d_{p+q}a$. As $d_{p+q}$ applies $\Fr[p+q+1]{\LL{n}}\Fr[p+q]{\LL{n}}\to\Fr[p+q]{\LL{n}}$:
\[d_{p+q}a=\sum [d_{p+q}s_{p+q}s_\beta(\jmath z), d_{p+q}s_{p+q}s_\alpha(\jmath w)]_{p+q}=\sum [s_\beta(\jmath z), s_\alpha(\jmath w)]_{p+q}.\]
Now in each term of this sum, one of $s_\beta(\jmath z)$ and $s_\alpha(\jmath w)$ will have a $\Q_{p+q}^i$ term (as long as $p+q>0$). This $\Q$ operation will be non-top, due to the strict inequality on $\minDim(I)$ imposed on the basis elements, and the fact that $\SqShift$-Adem relations do not decrease $\minDim(I)$. Thus, the ``$[Q^iw,z]=0$ for $Q^i$ non-top'' axiom in $\Fr[p+q]{\LL{n}}$ implies that each term in the sum vanishes, so that $d_{p+q}a=0$. If $p=q=0$, there is only a single term, which is $[z,w]$ as calculated inside $X$.

Next, we calculate $d_{i}a$ for $0\leq i< p+q$:
\[d_{i}a=\sum [s_{p+q-1}d_{i}s_\beta(\jmath z), s_{p+q-1}d_{i}s_\alpha(\jmath w)]_{p+q}.\]
%Now consider a given shuffle $(\alpha,\beta)$. If $i$ and $i-1$ both lie in $\beta$, say, then $d_is_\alpha(\jmath y)=s_{\alpha'}d_{i'}(\jmath y)=0$, as $\jmath y$ is a cycle in $NB_*$. Thus we can ignore all summands in which $i$ and $i-1$ lie in the same half of the shuffle.
%If $i$ and $i-1$ do not lie in the same half of the shuffle, then let $(\gamma,\epsilon)$ be the shuffle obtained from $(\alpha,\beta)$ by swapping the positions of $i$ and $i-1$. But then, $d_is_\beta=d_is_{\epsilon}$, and $d_is_\alpha=d_is_{\gamma}$, so that this pair of summands cancel with each other. 
Now consider a given shuffle $(\alpha,\beta)$. If, say, $\alpha$ contains neither of $i$ and $i-1$, then $d_is_\alpha(\jmath w)=s_{\alpha'}d_{i'}(\jmath w)=0$, as $\jmath w$ is a cycle in $NB_*$. Thus we can ignore all summands in which $\alpha$ and $\beta$ do not contain one each of $i$ and $i-1$.
If $\alpha$ and $\beta$ contain one each of $i$ and $i-1$, then let $(\gamma,\epsilon)$ be the shuffle obtained from $(\alpha,\beta)$ by swapping the positions of $i$ and $i-1$. But then, $d_is_\beta=d_is_{\epsilon}$, and $d_is_\alpha=d_is_{\gamma}$, so that the summands corresponding to $(\alpha,\beta)$ and to $(\gamma,\epsilon)$ cancel with each other.
\end{proof}
\subsection{$\Q^k$ operations on $(\derived\Ind{\nontop{n}})X$ for $k\geq1$}
In the previous section, we produced an element $a\in B_{p+q+1}(\Fr{\PRLie{n}},\Fr{\LL{n}},X)$, and showed that it was actually an element of $NB_{p+q+1}$, whose boundary was represented the homotopy class we were trying to nullhomotope. In the next two sections, we will choose such an $a$ again, but in some cases, the top \emph{two} face maps will be nonzero on $a$. Thus we will move outside of the normalised complex to construct a homotopy between two nonzero elements. This makes no difference to our calculations, especially since we in the end will always map down to $\overline{K}_*$, which doesn't see the distinction anyway.
\begin{prop*}
Suppose that $z\in Z\overline{K}_p(X)_{a_n,\ldots,a_1}$. Then:
\begin{itemize}\squishlist
\setlength{\parindent}{.25in}
\item  if $n\geq2$, $\Q^k\overline{z}=0$ for $1\leq k\leq p$;
\item  if $n=1$, $\Q^k\overline{z}=0$ for $2\leq k\leq p$; and
\item if $n=1$, write $z\in Z\overline{K}_p(X)_{a_1}$ as a sum 
\[z=\sum_{j}P(I^{(j)})x^{(j)}\]
where each $I^{(j)}=(i_p^{(j)},\ldots,i_1^{(j)})$ is $\delta$-admissible with $\minDimP(I^{(j)})\leq |x^{(j)}|$. Then
\[\Q^1\overline{z}\textup{ is represented by }\sum_{j}P((a_{n},i_p^{(j)},\ldots,i_1^{(j)}))x^{(j)}.\]
%%\item  if $n=1$, and $P(I)y$ is a basis element (which is also a cycle - fix up this statement) for $\overline{K}_*X$ (so that $I=(i_\ell,\ldots,i_1)$ is $\delta$-admissible, and $\minDimP(I)\leq |y|$), with $\ell\geq1$, we have:
%%\[\LambdaOp^1(P(I)y)=P((|P^{i_\ell}\cdots P^{i_1}y|,i_{\ell},\ldots,i_1))y.\]
That is, $\Q^1$ adjoins a top $P$ operation to the left of each sequence $I^{(j)}$.
\end{itemize}
\end{prop*}
\begin{proof}
The class $\Q^k\overline{z}$ is represented by $\sum_{(\alpha,\beta)\in\HalfShuffles{k}{k}}[s_\beta(\jmath z), s_\alpha(\jmath z)]_{out}$. As in the previous proof, we use the element
\[a:=\sum_{(\alpha,\beta)\in\HalfShuffles{k}{k}}[s_{p+k}s_\beta(\jmath z), s_{p+k}s_\alpha(\jmath z)]_{p+k+1}.\]
The same argument shows that $d_{p+k+1}a$ represents $\Q^k\overline{z}$, and that $d_{p+k}a=0$. We are left to calculate $d_ia$ for $0\leq i<p+k$, where 
\[d_ia:=\sum_{(\alpha,\beta)\in\HalfShuffles{k}{k}}[s_{p+k-1}d_is_\beta(\jmath z), s_{p+k}d_is_\alpha(\jmath z)]_{p+k}\]
Now if $i\geq 2k$, at least one of $\alpha$ and $\beta$, say $\alpha$, will not include either $i$ or $i-1$, so that $d_is_\alpha(\jmath z)=s_{\alpha'}d_{i'}(\jmath z)=0$, as $\jmath z$ is a cycle. Thus, we are left to consider the cases $0\leq i< 2k$.

In the previous proof, the method in this range was to construct a fixed-point free involution (`swap $i$ and $i-1$') of the set indexing the sum, under which the summands were invariant. The same involution works here, as long as it preserves the subset $\HalfShuffles{i}{i}$ of $\Shuffles{i}{i}$, which it does when $2\leq i<2k$. The $i=0$ case is moot, as no shuffle $(\alpha,\beta)$ involves $-1$.

%Again the only nonzero summands correspond to pairs $(\alpha,\beta)$ in which each of $\alpha$ and $\beta$ contain one each of $i$ and $i-1$. If $i=0$ there are obviously no such pairs. If $i\geq2$, the same involution of the shuffles preserves the subset $\HalfShuffles{i}{i}$ of $\Shuffles{i}{i}$, and so gives the cancellation desired.

The final case is $d_1$, in which case, the involution of $\Shuffles{i}{i}$ used above does not preserve the subset $\HalfShuffles{i}{i}$. Fortunately, since our summand uses $z$ twice, not both $z$ and $w$, the summands are invariant under a new involution, `swap $\alpha$ and $\beta$'. The composite of these two involutions preserves $\HalfShuffles{i}{i}$, and is fixed-point free unless $k=1$. In case $k=1$, $\HalfShuffles{i}{i}$ contains only $((1),(2))$, and we are left with a single term:
\[d_1a=[s_{p}d_1s_0(\jmath z), s_{p}d_1s_1(\jmath z)]_{p+2}=[s_{p}(\jmath z), s_{p}(\jmath z)]_{p+1}=\begin{cases}
0,&\textup{if }n\geq2;\\
P^{a_1}_{p+1}s_{p}(\jmath z),&\textup{if }n=1,
%\\,&\textup{if }
\end{cases}
.\]
as self-squares in $\LL{n}$ are zero when $n\geq2$, and equal the top $P$ operation when $n=1$. As the top $P$ operation is linear, in the $n=1$ case $d_1a$ is then the result of adding a $P^{a_1}$ to the front of every bar involved in the sum defining $z$. Recall that this sum is not just indexed over $j$, but rather,
\[z:=\sum_j\left(\BarMonomial{I^{(j)}}{\textbf{1}}{x^{(j)}}+\sum_{\produces{K}{I^{(j)}}{\delta}}\BarMonomial{K}{\textbf{1}}{x^{(j)}}\right)\]
using the notation from the description of Priddy's algorithm, and writing $\textbf{1}:=(1,\ldots,1)$. Thus
\[d_1a:=\sum_j\left(\BarMonomial{(a_1)\star I^{(j)}}{\textbf{1}}{x^{(j)}}+\sum_{\produces{K}{I^{(j)}}{\delta}}\BarMonomial{(a_1)\star K}{\textbf{1}}{x^{(j)}}\right)\]
where $\star$ denotes concatenation. None of the $(a_1)\star K$ could hope to be $\delta$-admissible, but all of the $(a_1)\star I^{(j)}$ \emph{are} $\delta$-admissible, simply as $P^{a_1}$ is a top operation. Thus, the image of $d_1a$ in $\overline{B}_*$ can be none other than that which we propose.
%
% also over all the $J$ such that $\produces{J}{I^{(j)}}{\delta}$. After making these concatenations, the bars which are $\delta$-admissible are exactly those which are of the form 
%\[d_1a=P^{a_1}_{p+1}s_{p}(\jmath z)=\sum_{j}\sum_{\produces{K}{I^{(j)}}{\delta}}P^{a_1}_{p+1}s_{p}(\jmath z)\]
% %However, objects of $\LL{1}$ may have non-zero self-squares, and the self-square is given by the top $P$ operation. Thus a top $P$ operation is applied to $s_p(\jmath z)$ in $\Fr[p+1]{\LL{n}}$. As all $P$ operations are linear, a cycle $P(I)y$, defined by
%\[P(I)y:=\left[P^{i_r} \middle|\cdots\middle|P^{i_1} \right]y+\sum_{\substack{\produces{J}{I}{\delta} \\ \minDimP(J)\leq|y|}}\left[P^{j_r} \middle|\cdots\middle|P^{j_1} \right]y\]
%receives the same top $P$ operation as a new bar in each of the bars in the above definition. There is only the one $\delta$-admissible sequence appearing in the new sum, completing the proof. \textbf{Sometime, think about what happens here in a little more detail.}
\end{proof}

\subsection{$\Q^0$ operations on $(\derived\Ind{\nontop{n}})X$}
Assume for this section that $n\geq2$, so that objects of $\LL{n+1}$ support a $\Q^0$ operation, defined when $a_n,\ldots,a_2$ are not all zero. We'll now go some way towards calculating these operations.
\begin{lem*}
Suppose that $z\in Z\overline{K}_p(X)_{a_n,\ldots,a_1}$, where not all of $a_n,\ldots,a_2$ are zero. 
\begin{itemise}
\setlength{\parindent}{.25in}
\item If $p>0$, $Q^0\overline{z}$ is represented by the cycle $\Q^{a_n}_p\jmath z$ in the bar construction $NB_p(\Fr{\PRLie{n}},\Fr{\LL{n}},X)$.
\item If $p=0$, $Q^0\overline{z}$ is represented by the cycle $\Q^{a_n}z$, as calculated in $X=Z\overline{K}_0(X)$.% in the bar construction $NB_p(\Fr{\PRLie{n}},\Fr{\LL{n}},X)$
\end{itemise}
\end{lem*}
\begin{proof}
We use the same homotopy $a$ as in the previous cases. That is, write
$a:=\restn[p+1]{(s_{p}(\jmath z))}$. Then $d_{p+1}a=\restn[out]{(s_{p}(\jmath z))}$ represents $Q^0\overline{z}$, $d_pa=\restn[p]{(\jmath z)}$, and for $0\leq i<p$, $d_ia=0$. The result follows by recalling that the restriction in $\LL{n}$ is the top $\Q$ operation.
\end{proof}
\begin{lem*}
Suppose that $z\in Z\overline{K}_p(X)_{a_n,\ldots,a_1}$, for $p>0$, is written as a sum
\[z=\sum_{j}\left[\Q^{i^{{(j)}}_p}\middle|\cdots \middle|\Q^{i^{{(j)}}_1}\right]x^{(j)}\]
such that for all $j$, 
%such that all of the $i^{(j)}_k$ satisfy $i^{(j)}_k>d$, and 
$\Q^ix^{(j)}=0$ whenever $i\geq i^{{(j)}}_1$. Then $\Q^0\overline{z}=0$.

In particular, suppose that $I^{(j)}=(i^{(j)}_{p},\ldots,i^{(j)}_{1})$ is a collection of $\SqShift$-Admissible sequences, and $x^{(j)}$ is a sequence of homogeneous elements of $X$, such that
\[z=\sum_{j}Q(I^{(j)})x^{(j)}\]
is a cycle in $\overline{K}_p(X)$, and that for all $j$, $\Q^ix^{(j)}=0$ whenever $i\geq i^{{(j)}}_1$. Then $\Q^0\overline{z}=0$.
\end{lem*}
\begin{proof}
The second statement follows from the first, as whenever $\produces{J}{I}{\SqShift}$, the final entry of $J$ is at least as large that of $I$.

We've seen that $\Q^0\overline{z}$ is represented by the cycle
\[\sum_{j}\Q^{a_n}_p\Q^{i^{{(j)}}_p}_p\cdots \Q^{i^{{(j)}}_1}_1x^{(j)}\]
in the bar construction $N{B_*}(\PRLie{n},\LL{n},X)$. This cycle is the image of a cycle in $NB_*(\forget,\nontop{n},X)$ which, after mapping down to the quotient by degenerate simplices, we dare write as:
\[\sum_{j}\left[\Q^{a_n}\Q^{i^{{(j)}}_p}\middle|\cdots \middle|\Q^{i^{{(j)}}_1}\right]x^{(j)}\in\overline{B}_{p,p+1}.\]
Now in order to compress this into the Koszul complex, we must apply Priddy's algorithm. But one observes readily from the $\Q$-Adem relation that if $\produces{(i,j)}{(i',j')}{\Q}$, then $j'>j$, so that as we perform Priddy's algorithm, we only ever decrease the index of the final $\Q$ appearing in each bar. Then the hypothesis on the $x^{{j}}$ guarantees that as we run the algorithm, every term that ends up in $\overline{B}_{p,p}$ willl vanish. Thus Priddy's algorithm constructs a null-homotopy.
\end{proof}

\end{LieLambdaStructureOnKoszul}



\begin{SequenceOfSequencesIntro}

\section{Calculations on positive spheres}
Choose a positive integer $d$, and write $H:=H^*_Q(S^d)$ for the Andr\'e-Quillen cohomology of the $d$-dimensional sphere. It is our goal to compute $(\derived\Ind{\LL{1}})H$, the $E_2$-page for the Adams spectral sequence. For this, it might be useful to calculate, for each $N\geq1$, the derived functors
\[H^{(N)}:=(\derived\Ind{\nontop{N}})(\derived\Ind{\nontop{N-1}})\cdots (\derived\Ind{\nontop{1}})H\in\LL{N+1}.\]
This we'll do, one step at a time, but before we start, we'll take care to accurately set out the combinatorics involved in describing a basis of $H^{(n)}$.

\subsection{Sequences of admissible sequences}
To parameterize a basis of $H^{(N)}\in\LL{N+1}$ we will use sequences of $N$ admissible sequences, which we shall always write as $(I^N,\ldots,I^1)$. To further simplify notation, we'll employ the following shorthand:
\begin{itemize}
\squishlist
\setlength{\parindent}{.25in}
\item $\ell^i$ is the number of entries of $I^i$;
\item $n^i$ is the sum of the entries of $I^i$;
\item $\minDimP^1$ is $\minDimP(I^1)$, and $\minDim^i$ is $\minDim(I^i)$ for $i\geq2$.
\end{itemize}
Moreover, whenever we index a set of generators over $S=(I^N,\ldots,I^1)$, we will always impose the following conditions on $S$:
\begin{enumerate}[A)]
\squishlist
\setlength{\parindent}{.25in}
\item[\textup{(A)}] $I^1$ is $\delta$-admissible (with entries at least 2) and satisfies $\minDimP^1\leq d$;
\item[\textup{(B)}] for $i\geq2$, $I^i$ is $\SqShift$-admissible (with entries nonnegative);
\item[\textup{(C)}] $I^2$ does not contain zero, and $\minDim^i<\ell^{i-1}$ for all $i\geq2$.
\end{enumerate}
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item for $i>1$, $I^i$ does not contain zero unless one of $\ell_{i-2},\ldots,\ell_1$ is nonzero (and in particular, $I^2$ does not contain zero). Note that as $I^i$ is $\SqShift$-admissible, it can have at most one zero, which must be its rightmost entry.
%\end{itemise}
%All other restrictions on the $I^i$ will be made explicit.
A basis element corresponding to $S=(I^N,\ldots,I^1)$ will be written $\Q(I^N)\cdots \Q(I^2)P(I^1)\imath$, or $b(S)$, and will have grading%. The element $b(S)$ will have gradings $(a_{N+1},\ldots,a_1)$ equal to
%\[\left(\ell^N,\ell^{N-1}+n^N,2^{\ell^N}\!\left(\ell^{N-2}+n^{N-1}\right),2^{\ell^N+\ell^{N-1}}\!\left(\ell^{N-3}+n^{N-2}\right),\ldots,2^{\ell^N+\cdots+\ell^{3}}(\ell^1+n^2),\ a_1\ \right)\]
\begin{align*}
 (a_{N+1},\ldots,a_1) &= \left( \ell^N,\ell^{N-1}+n^N,2^{\ell^N}\!\left(\ell^{N-2}+n^{N-1}\right),2^{\ell^N+\ell^{N-1}}\!\left(\ell^{N-3}+n^{N-2}\right),\ldots \right.\\
 &\qquad \left.{}\ldots,2^{\ell^N+\cdots+\ell^{4}}(\ell^2+n^3),2^{\ell^N+\cdots+\ell^{3}}(\ell^1+n^2),2^{\ell^N+\cdots+\ell^{2}}(d+n^1+\ell^1+1)-1 \right).
\end{align*}
The formula for $a_1$ is a little different to those for the other $a_i$ due to the $+1$-shift.
%where this pattern continues up until the final grading $a_1$, at which point the $+1$-shift muddies the water. 
We note some immediate consequences of the conditions just imposed on the $I^i$, after defining:
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item Suppose that $\ell^i=0$, then $0=\ell^{i+1}=\ell^{i+2}=\ell^{i+3}=\cdots $;
%\item if $\ell^N>0$ for $N\geq3$, then both $a_N=\ell^{N-1}+n^N\neq0$ and $a_{N-1}=2^{\ell^N}\!\left(\ell^{N-2}+n^{N-1}\right)\neq0$.
%\end{itemise}
%\begin{lem*}
%The conditions we have put on the $I^i$ in $\Q(I^N)\cdots \Q(I^2)P(I^1)\imath$ are equivalent to the following requirements:
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item[i)] $I^1$ is $\delta$-admissible (with entries at least 2) and satisfies $\minDimP^1\leq d$;
%%\item for $i>1$, $I^i$ is $\SqShift$-admissible (with entries nonnegative) and satisfies $\minDim^i<\ell^{i-1}$; and
%%\item $I^1$ is $\delta$-admissible (with entries at least 2) and for $i>1$, $I^i$ is $\SqShift$-admissible (with entries nonnegative);
%%\item there exists an object $X$ of $\LL{1}$, and an element $x\in X$ with $|x|=d$, such that $P^{I^1}x$ is nonzero;
%\item[ii)] for each $i$ satisfying $2\leq i\leq N$, $I^i$ is $\SqShift$-admissible (with entries nonnegative), and the operation $\Q^{I^i}$ is defined on classes of dimension $\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|$ in objects of $\nontop{i}$.
%%
%% there exists an object $X$ of $\LL{i}$, and an element $x\in X$ with $\|x\|=\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|$, such that $\Q^{I^i}x$ is defined, and none of the $\Q$ in this expression act as a top operation.
%\end{itemise}
%\end{lem*}
\begin{enumerate}[A)]
\squishlist
%%%%%%%%%%%%% A2 is a silly misconception! Don't put it in here. \item[(A2)] \textbf{WRONG}for some $X\in\nontop{1}$ (or equivalently $\LL{1}$) and some element $x\in X_d$, $P^{I^1}x$ is nonzero.
\item[(C2)] for each $i$ satisfying $2\leq i\leq N$, and each object $X\in\nontop{i}$ the operation $\Q^{I^i}$ is defined on classes of dimension $\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|$ in $X$.
\end{enumerate}
\begin{lem*}
Suppose that $N\geq1$ and that $S=(I^N,\ldots,I^1)$. Write $\left\|b(S)\right\|=(a_{N+1},\ldots,a_1)$. Then
\begin{itemise}
%\setlength{\parindent}{.25in}
\item[i)]  If $S$ satisfies \textup{(A)}-\textup{(C)}, and if $\ell^i=0$, then $\ell^{i+1}=\ell^{i+2}=\cdots=\ell^{N}=0$;
\item[ii)]  If $S$ satisfies \textup{(A)}-\textup{(C)}, then $\ell^i\neq0$ iff $a_{i+1}\neq0$ iff none of $a_{i+1},\ldots,a_1$ are zero; %the final $i+1$ gradings of $\Q(I^{N})\cdots \Q(I^2)P(I^1)\imath$ are all nonzero;%both $a_N=\ell^{N-1}+n^N\neq0$ and $a_{N-1}=2^{\ell^N}\!\left(\ell^{N-2}+n^{N-1}\right)\neq0$.
\item[iii)] If $S$ satisfies \textup{(A)} and \textup{(B)}, then $S$ satisfies \textup{(C)} iff $S$ satisfies \textup{(C2)}.
\end{itemise}
\end{lem*}
\noindent Statement (iii) would be obvious if \textup{(C)} contained appropriate conditions on the appearance of zeros in $I^i$ for $i\geq3$. The point then is that \textup{(A)}-\textup{(C)} together make these conditions redundant.
%
%\noindent The point of the final statement is that we do not need an extra condition on when the $I^i$, for $i\geq3$, can contain zero, in order that the second statement of the lemma holds --- this is already wrapped up in the condition $m^i<\ell^{i-1}$ and the condition that $I^2$ doesn't contain zero.
%
%\begin{proof}
%The first condition is common to the two sets of conditions we are comparing, so can be ignored.
%The case $i=2$ is easy, as no $\Q^0$ operations are ever defined in $\nontop{2}$, leaving us those cases with $i\geq3$. Now in order that $\Q^{I^i}$ is defined on classes of dimension $\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|$ in objects of $\nontop{i}$, we must have $\minDim^i<|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)|=\ell^{i-1}$. Finally we must check that the conditions $\minDim^j<\ell^{j-1}$ for all $j$ imply that there is no zero appearing in $\Q^{I^i}$, for $i\geq3$, is erroneous. But if $I^i$ contains a zero, then $\ell^i>0$, so that $\ell^{i-1},\ell^{i-2}>0$, and writing $\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|=(a_i,\ldots,a_1)$, we have that $a_{i}=\ell^{i-1}>0$ and $a_{i-1}=\ell^{i-2}+n^{i-1}>0$, so that $\Q^0$ is indeed defined on such classes.
%\end{proof}

\begin{proof}
To prove (i), note that if $\ell^i=0$, then $\minDim^{i+1}<\ell^i=0$, which can only occur if $I^{i+1}=\emptyset$. (ii) follows immediately from (i). Thus we are to show that, when \textup{(A)} and \textup{(B)} hold, \textup{(C)} and (iii) are equivalent. In what follows, write $(a'_i,\ldots,a'_1)=\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|$.

%The $i=2$ part is easy, as no $\Q^0$ operations are ever defined in $\nontop{2}$, leaving us those cases with $i\geq3$. 
Consider statement (iii). Evidently, \textup{(C2)} implies \textup{(C)}, as in  order that $\Q^{I^i}$ is defined on classes of dimension $(a'_i,\ldots,a'_1)$ in objects of $\nontop{i}$, we must have $\minDim^i<a'_i=\ell^{i-1}$.

To check that \textup{(C)} implies \textup{(C2)}, recall that there are two conditions to be checked in order that $\Q^{I^i}$ can act. Firstly, there is the condition on $\minDim(I^i)$, which is present in \textup{(C)}. The other condition required is that $I^i$ contains no zero unless one of $a'_{i-1},\ldots,a'_{2}$ is nonzero.
%concerns the appearance of zeros in $I^i$. 
When $i=2$, trivially, none of this empty collection of integers is nonzero, and correspondingly, \textup{(C)} explicitly forbids zeros in $I^2$. Thus, we restrict attention to when $i\geq3$. %Now as $I^i$ is $\SqShift$-admissible, all of the zeros therein appear at the right, so the question comes down to whether a \emph{single} $\Q^0$ can appear.
Now if $I^i$ contains a zero, then $\ell^i>0$, so $\ell^{i-1}>0$, and all $i$ entries of $(a'_i,\ldots,a'_1)$ are nonzero. As $i\geq3$, this means that $\Q^0$ is indeed defined on such classes in $\nontop{i}$.
%
% Finally we must check that the conditions $\minDim^j<\ell^{j-1}$ for all $j$ imply that there is no zero appearing in $\Q^{I^i}$, for $i\geq3$, is erroneous. But if $I^i$ contains a zero, then $\ell^i>0$, so that $\ell^{i-1},\ell^{i-2}>0$, and writing $\|\Q(I^{i-1})\cdots \Q(I^2)P(I^1)\imath\|=(a_i,\ldots,a_1)$, we have that $a_{i}=\ell^{i-1}>0$ and $a_{i-1}=\ell^{i-2}+n^{i-1}>0$, so that $\Q^0$ is indeed defined on such classes.
\end{proof}

Before we go on, it is convenient to introduce two more conditions that $S=(I^N,\ldots,I^1)$ may satisfy, for $N\geq2$. These will appear unmotivated until later:
\begin{itemise}
\setlength{\parindent}{.25in}
\item[D)] $I^2$ doesn't contain 1.
\item[E)] $I^2$ doesn't contain 1 or 2, $I^1\in\im(t_d)$, and $\ell^1>2$.
\end{itemise}
Here, $t_d$ is the function which adds a top $P$ operation to a \emph{nonempty} $\delta$-admissible sequence:
\begin{lem*}
Consider the operation $t_d$ which sends a nonempty sequence  $I^1$ to $(d+n^1+\ell^1)\star I^1$. Then $t_dI^1$ satisfies \textup{(A)} if and only if $I^1$ satisfies \textup{(A)}.
\end{lem*}
\begin{proof}
The only if part is immediate, as removing the leftmost entry of a sequence only makes it more likely to be admissible, and cannot increase $\minDimP$. Assume then that $I^1=(i_{\ell^1},\ldots,i_1)$ satisfies \textup{(A)}, with $\ell^1\geq1$. Then:%Now by definition of $\minDimP$,
\[\minDimP(t_dI)=\max\{\minDimP(I),(d+n^1+\ell^1-i_{\ell^1}-\cdots -i_1-\ell^1)\}=\max\{\minDimP(I),d\}=d.\]
We should check that $t_dI^1$ is $\delta$-admissible. We only need to check that $d+n^1+\ell^1\geq2i_{\ell^1}$, or $d+1\geq2i_{\ell^1}-n^1-\ell^1+1$, but the right hand side of this inequality is one of the terms in the max defining $d$, so this last inequality holds (even strictly).
\end{proof}
\end{SequenceOfSequencesIntro}


\begin{KoszulSequenceCombinatorics}
\subsection{Combinatorics of  the sequences $(I^N,\ldots,I^1)$}
\begin{Omitted}
Suppose that $k\geq2$, and that we've already chosen $(I^{k-1},\ldots,I^1)$ satisfying \textup{(A)}-\textup{(C)}. One may ask the question ``which sequences $I^k$ can we choose so that \textup{(A)}-\textup{(C)} hold for $(I^{k},\ldots,I^1)$?''
\begin{prop*}
Suppose that $S=(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)}. Then the sequence $(\ell^N,\ell^{N-1},\ldots,\ell^1)$ is nondecreasing, and $I^k=(\ldots,7,3,1,0)$ whenever $\ell^k=\ell^{k-1}$.%, it must be that $I^k=(\ldots,7,3,1,0)$.
\end{prop*}
\begin{proof}
To investigate this question, for a given choice $I^k$ with $\ell^{k}>0$, we define the following two quantities:
%We define the following two quantities, for $k\geq2$, which relate to the question ``which sequences $I^k$ are permitted given that $I^{k-1}$ has already been chosen?'' under constraints \textup{(A)}-\textup{(C)} as always. Define the following two quantities when $\ell^k>0$:
\begin{itemise}
\setlength{\parindent}{.25in}
\item Let $\widetilde{e}^k=\minDim^k-\ell^{k}+1$. This is a nonnegative integer, as if we write $I^k=(i_{\ell^k},\ldots,i_1)$, then, as $I^k$ is $\SqShift$-admissible, $\minDim^k=i_{\ell^k}-i_{\ell^k-1}-\cdots -i_1$, and so:
\[\widetilde{e}^k=(i_{\ell^k}-2i_{\ell^k-1}-1)+ (i_{\ell^k-1}-2i_{\ell^k-2}-1)+\cdots + (i_{2}-2i_{1}-1)+(i_1)\geq0.\]
\item Let $f^k=\ell^{k-1}-1-\minDim^k$. This too is nonnegative, as $\minDim^k<\ell^{k-1}$.
\end{itemise}
These two quantities measure how wasteful we have been in choosing $I^k$, if our objective is to make $\ell^k$ as large as possible:
\begin{itemise}
\setlength{\parindent}{.25in}
\item $\widetilde{e}^k$ is the total amount of waste caused, first by choosing $i_1$ unnecessarily high, then by choosing $i_2$ unnecessarily high (subject to the admissibility constraint imposed by $i_1$), etc. [Note that choosing the entries of $I^k$ higher than they need to be cramps us for space, leading to shorter sequences being allowed.]
\item $f^k$ is the waste caused by choosing $I^k$ an unnecessarily short sequence. [Note that given a $\SqShift$-admissible sequence $I$, one can always create another $\SqShift$-admissible sequence $I'$ by adding a single entry onto the left which is as small as possible. This increases both $\ell$ and $\minDim$ by one. If we are trying to maximise $\ell$, we should really do this to $I^k$ whenever $\minDim^k$ is any less than $\ell^{k-1}-1$.]
\end{itemise}
The point, then, is that whenever $\ell^k>0$ for $k\geq2$, $\ell^k=\ell^{k-1}-\widetilde{e}^k-f^k$.
\end{proof}
\end{Omitted}

\begin{lem*}
Suppose that $I\in\admis{\SqShift}$ with $\ell(I)>0$. Then $\ell(I)\leq \minDim(I)+1$, with equality iff $I=(\ldots,7,3,1,0)$. Moreover, $\minDim(I)=e(I)$, the Serre excess of $I$. The following inequalities hold:
\begin{equation}
2^{\ell(I)}-1-\ell(I)\leq n(I)\leq2^{\minDim(I)+1}-1-(\minDim(I)+1).\tag{i.1) \& (i.2}
\end{equation}
If $I$ does not contain 0, then \textup{(i.1)} can be strengthened:
\[2(2^{\ell(I)}-1)-\ell(I)\leq n(I),\]
and if $I$ does not contain either 0 or 1, both \textup{(i.1)} and \textup{(i.2)} can be strengthened:
\[3(2^{\ell(I)}-1)-\ell(I)\leq n(I)\leq 3\cdot2^{\minDim(I)-1}-\minDim(I)-2.\]
%the first inequality can be strengthened to $n(I)\geq 3(2^{\ell(I)}-1)-\ell(I)$.
\end{lem*}
\begin{proof}
Note first that there is a bijection, for $\ell\geq1$:
\begin{alignat*}{2}
\gamma:\left\{(m_{\ell},\ldots,m_1)\ \middle|\ m_\ell,\ldots,m_2\geq1,\ m_1\geq0\right\}&\overset{\cong}{\to}\left\{\textup{$\SqShift$-admissible sequences of length $\ell$}\right\}
\\
(m_\ell,\ldots,m_1)
&\overset{\gamma}{\mapsto}
(\ldots,2^2m_1+2m_2+m_3,2m_1+m_2,m_1)\\
(i_\ell-2i_{\ell-1},\ldots,i_2-2i_1,i_1)
&\overset{\gamma^{-1}}{\mapsfrom}
(i_\ell,\ldots,i_1)%
\end{alignat*}
%The expression for $m(\gamma(\textbf{m}))$ is
Formulae for $m(\gamma(\textbf{m}))$ and $n(\gamma(\textbf{m}))$ are easy to write down:
\[m(\gamma(\textbf{m}))=\max\left\{m_j+\cdots +m_1\right\}_{j=1}^\ell=m_\ell+\cdots +m_1=e(\gamma(\textbf{m}));\]
\[%\minDim(\gamma(\textbf{m})):=\max\{m_{\ell}+\cdots +m_1,\ldots,m_2+m_1,m_1\}=\sum_{i=1}^{\ell}m_i;\quad
n(\gamma(\textbf{m}))=\sum_{i=0}^{\ell-1}\left(2^{i+1}-1\right)m_{\ell-i}.\]
In particular, as all of $m_\ell,\ldots,m_2$ are positive, $\minDim(\gamma(\textbf{m}))\geq\ell-1$, with equality iff $\textbf{m}=(1,\ldots,1,0)$, proving the first claim.
The condition that $\gamma(\textbf{m})$ contains no 0 (resp.\ no 0 or 1) translates simply to $m_1\geq1$ (resp.\ $m_1\geq2$), so that \textup{(i.1)} and its two strengthenings are easy:
\[n(\gamma(\textbf{m}))=\sum_{i=0}^{\ell-1}\left(2^{i+1}-1\right)m_{\ell-i}\geq(2^{\ell}-1)m_1+ \sum_{i=0}^{\ell-2}\left(2^{i+1}-1\right)
=(2^{\ell}-1)m_1+(2^\ell-1)-\ell.\]
For \textup{(i.2)}, fix $M$, and consider those $\textbf{m}$ for which $\minDim(\gamma(\textbf{m}))=M$, so that $M=\sum_im_i$. Then $n(\gamma(\textbf{m}))$ cannot exceed $n(\gamma((1,\ldots,1)))$, where the $1$ is repeated $M$ times. To see this, note that $n(\gamma(\textbf{m}))$ increases as $\textbf{m}$ becomes more weighted towards $m_i$ for $i$ low, so that the maximum must occur when $\textbf{m}$ is of the form $(1,\ldots,1,a)$. But $n(\gamma((1,\ldots,1,a)))\leq n(\gamma((1,\ldots,1,1,a-1)))$ whenever $a\geq1$, with equality iff $a=1$, so $\minDim(\gamma(\textbf{m}))$ is maximised on $\textbf{m}=(1,\ldots,1)$, with $\ell=M$, and:
\[n(\gamma(\textbf{m}))=\sum_{i=0}^{M-1}(2^{i+1}-1)=2^{M+1}-M-2.\]
To prove the strengthening of \textup{(i.2)}, a similar argument, after restricting to those $\textbf{m}$ with $m_1\geq2$, shows that $n(\gamma(\textbf{m}))$ is maximised when $\textbf{m}=(1,\ldots,1,2)$, with $\ell=M-1$. Then
\[n(\gamma(\textbf{m}))=(2^{M-1}-1)\cdot2+\sum_{i=0}^{(M-1)-2}(2^{i+1}-1)=3\cdot2^{M-1}-M-2.\qedhere\]
\end{proof}
%\begin{cor*}Suppose that $N\geq2$ and $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(D)}.
%Then the sequence $(n^N,\ldots,n^1)$ is nondecreasing.%, and whenever $n^k=n^{k-1}$, it must be that $\ell^k=\ell^{k-1}$, and $I^k=(\ldots,7,3,1,0)$.
%\end{cor*}
%\begin{cor*}Suppose that $N\geq2$ and that $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(D)} with $\ell^N>0$.
%Then the sequence $(n^N,\ldots,n^2,n^1/2)$ is nondecreasing, and there's a chain of inequalities, for $N\geq3$:
%\[\ell^N\leq\ell^{N-1}+n^N\leq\ell^{N-2}+n^{N-1}\leq\cdots \leq \ell^2+n^3\leq(\ell^1+n^2)/3.\]
%%\[\ell^1+n^2\geq3(\ell^2+n^3),\]
%If $N=2$ we just obtain $\ell^2\leq(\ell^1+n^2)/3$.
%\end{cor*}
%
%\begin{proof}
%Write $g$ for the integer sequence $i\mapsto 2^i-i-1$. Then $g(0)=g(1)=0$, and $g(i-1)<g(i)$ for $i\geq2$.
%%, and also, $g(i)\leq 2^{i+1}-2$ for $i\geq0$. 
%We've seen that $g(\ell^k)\leq n^k\leq g(\minDim^k+1)$ for all $k\geq2$. That $g$ is nondecreasing, taken with the inequality from constraint \textup{(C)}, gives a chain
%\[\cdots \leq n^k\leq g(\minDim^k+1)\leq g(\ell^{k-1})\leq n^{k-1}\leq\cdots\leq n^2\leq g(\minDim^2+1)\leq g(\ell^{1}). \]
%Although $I^1$ doesn't fit into the same pattern, $n^1$ can be no less than $\sum_{i=1}^{\ell^1}2^i=2^{\ell^1+1}-2$, as a $\delta$-admissible sequence only involves indices of size \emph{at least $2$}. We can then complete the above chain with further inequalities $g(\ell^1)\leq2^{\ell^1}-1\leq n^1/2$. This proves that $(n^N,\ldots,n^2,n^1/2)$ is nondecreasing. As we've shown that $(\ell^N,\ldots,\ell^1)$ is nondecreasing, we've actually shown all  we set out to prove, except that $\ell^1+n^2\geq3(\ell^2+n^3)$.
%
%$I^2$ can contain no 0 or 1, so that $3(2^{\ell^2}-1)-\ell^2\leq n^2$. Moreover, we've just shown that $n^3\leq g(\ell^2)=2^{\ell^2}-\ell^2-1$.
%%Combine these two inequalities with $\ell^1\geq \ell^2$ to get the last result.
%Then $\ell^1+n^2\geq n^2+\ell^2\geq3(2^{\ell^2}-1)\geq3(\ell^2+n^3)$.
%\end{proof}
%\begin{prop*}
%Suppose that $N\geq2$ and that $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(D)} with $\ell^N>0$. Then $a_2\geq 3(a_3+\cdots +a_{N+1})$.
%\end{prop*}
%\begin{proof}
%When $N=2$, this is just the final inequality in the previous corollary, so assume $N\geq3$. In this case, the same corollary's chain of inequalities may be restated as:
%\[a_N\geq a_{N+1},\  a_{N-1}\geq 2^{\ell^{N}}a_N,\ \ldots,\ a_3\geq 2^{\ell^{4}}a_4,\ a_2/3\geq 2^{\ell^{3}}a_3,\]
%and all of the $\ell^i$ are at least 1. Thus
%\[a_2/3\geq 2a_3\geq a_3+2a_4\geq a_3+a_4+2a_5\geq\cdots \geq a_3+\cdots +a_{N+1}.\qedhere\]
%\end{proof}
%\begin{prop*}
%Writing $\left\|\Q(I^N)\cdots \Q(I^2)P(I^1)\imath\right\|=(a_{N+1},\ldots,a_{1})$, suppose that $\ell^N\neq0$. Then $a_i\geq 2a_{i+1}$ for all $i$ with $2\leq i\leq N-1$. Moreover, $a_{N}\geq2a_{N+1}$ unless $I^N=(0)$ and $\ell^{N-1}=1$, when $a_{N+1}=a_N=1$.
%\end{prop*}
%\begin{proof}
%When $i=N$, it's enough to note that $n^N\geq\ell^N$ unless $I^N=(0)$. For the cases $2\leq i\leq N-1$, one uses the fact that the sequences $(n^N,\ldots,n^1)$ and $(\ell^N,\ldots,\ell^1)$ are nondecreasing.
%\end{proof}

%\begin{cor*}Suppose that $N\geq1$ and that $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)} with $\ell^N>0$.
%Then if $N\geq2$ there is a chain of $N-1$ inequalities:
%\[n^N\leq n^{N-1}\leq\cdots \leq n^2\leq \tfrac{1}{2}n^1,\]
%and a chain of $N$ inequalities:
%\[(\ell^N)\leq(\ell^{N-1}+n^N)\leq(\ell^{N-2}+n^{N-1})\leq\cdots \leq (\ell^2+n^3)\leq\tfrac{1}{2}(\ell^1+n^2)\leq \tfrac{1}{3}(n^1+\ell^1).\]
%When $S$ also satisfies \textup{(D)}, we can strengthen the second last inequality:
%\[(\ell^N)\leq(\ell^{N-1}+n^N)\leq(\ell^{N-2}+n^{N-1})\leq\cdots \leq (\ell^2+n^3)\leq\tfrac{1}{3}(\ell^1+n^2)\leq \tfrac{2}{9}(n^1+\ell^1).\]
%%$(n^N,\ldots,n^2,n^1/2)$ is nondecreasing, and there's a chain of inequalities, for $N\geq3$:
%%\[\ell^N\leq\ell^{N-1}+n^N\leq\ell^{N-2}+n^{N-1}\leq\cdots \leq \ell^2+n^3\leq(\ell^1+n^2)/3.\]
%%\[\ell^1+n^2\geq3(\ell^2+n^3),\]
%If $N=1$, the stronger inequality $\ell^1\leq\tfrac{1}{3}(n^1+\ell^1)$ is satisfied.
%\end{cor*}


\begin{cor*}Suppose that $N\geq1$ and that $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)}. % with $\ell^N>0$.
Then if $N\geq2$ there are two chains of $N-1$ inequalities and two chains of $N-2$ inequalities:
\begin{equation}
\ell^N\leq \ell^{N-1}\leq\cdots \leq \ell^2\leq \ell^1;\tag{c.0}
\end{equation}
\begin{equation}
n^N\leq n^{N-1}\leq\cdots \leq n^2\leq \tfrac{1}{2}n^1;\tag{c.1}
\end{equation}
\begin{equation}
\minDim^N\leq \minDim^{N-1}\leq\cdots \leq \minDim^2;\tag{c.2}
\end{equation}
\begin{equation}
(\ell^N)\leq(\ell^{N-1}+n^N)\leq(\ell^{N-2}+n^{N-1})\leq\cdots \leq (\ell^2+n^3).\tag{c.3}
\end{equation}
Moreover (reading $n^3$ as zero when $N=2$):
\begin{equation}
2(\ell^2+n^3)\leq(\ell^1+n^2)\textup{\ and\ }3(\ell^1+n^2)\leq 2(n^1+\ell^1).\tag{i.3) \& (i.4}
\end{equation}
When $N=1$, we obtain only one inequality, a stronger version $3\ell^1\leq(n^1+\ell^1)$ of \textup{(i.4)}.
Finally, when $N\geq2$ and $S$ also satisfies \textup{(D)}, we have a stronger version $3(\ell^2+n^3)\leq(\ell^1+n^2)$ of \textup{(i.3)}.
\end{cor*}

\begin{proof}
Write $g(i):=2^i-i-1$ for $i\geq0$, and $g(-\infty)=0$. Then
\[0=g(-\infty)=g(0)=g(1)<g(2)<g(3)<\cdots,\quad \textup{and}\quad g(i)\leq 2^i-1 \textup{ for $i\geq0$}.\]
Inequalities \textup{(i.1)} and \textup{(i.2)} state that $g(\ell^k)\leq n^k\leq g(\minDim^k+1)$ for all $k\geq2$. %Evidently, $g(0)=g(1)=0$, and $g(i)>g(i-1)$ for $i\geq2$. For convenience, write $g(-\infty)$
%, and also, $g(i)\leq 2^{i+1}-2$ for $i\geq0$.
Moreover, $n^1$ can be no less than $\sum_{i=1}^{\ell^1}2^i=2^{\ell^1+1}-2$, as a $\delta$-admissible sequence only involves indices of size \emph{at least $2$}, implying that $2^{\ell^1}-1\leq n^1/2$. This fact, along with the obeservation that $g$ is nondecreasing, and the inequality $m^i<\ell^{i-1}$ from \textup{(C)}, gives a chain:
\begin{multline*}
g(\ell^N)\leq n^N\leq g(\minDim^N+1)\leq\cdots\\\cdots \leq g(\ell^k)\leq n^k\leq g(\minDim^k+1)\leq g(\ell^{k-1})\leq n^{k-1}\leq g(\minDim^{k-1}+1)\leq\cdots\\
\cdots\leq n^2\leq g(\minDim^2+1)\leq g(\ell^{1})\leq 2^{\ell^1}-1\leq \tfrac{1}{2}n^1
\end{multline*}
This proves \textup{(c.1)}, which is a subchain. Although $g$ is not strictly increasing near zero, \textup{(c.0)} follows anyway, since $\ell^k=0$ implies that $\ell^{k+1}=0$. Equivalently, $m^k=-\infty$ implies $m^{k+1}=-\infty$, and \textup{(c.2)} follows. \textup{(c.3)} is immediate from \textup{(c.0)} and \textup{(c.1)}.
%Although $I^1$ doesn't fit into the same pattern, $n^1$ can be no less than $\sum_{i=1}^{\ell^1}2^i=2^{\ell^1+1}-2$, as a $\delta$-admissible sequence only involves indices of size \emph{at least $2$}. We can then augment the above chain with further inequalities $g(\ell^1)\leq2^{\ell^1}-1\leq n^1/2$, verifying \textup{(c.1)}. As $(\ell^N,\ldots,\ell^1)$ is nondecreasing, \textup{(c.1)} implies \textup{(c.3)}.%, and also the $N=1$ case of \textup{(i.4)}.

The inequality $3\ell^1\leq(n^1+\ell^1)$ in fact holds for all $N$, and follows from the observation that $n^1\geq2\ell^1$ (as $n^1\geq 2^{\ell^1+1}-2\geq 2\ell^1$). This proves the version of \textup{(i.4)} relevant when $N=1$. When $N\geq2$, \textup{(i.4)} follows from established inequalities:
\[2(n^1+\ell^1)-3(\ell^1+n^2)=\tfrac{3}{2}(n^1-2n^2)+\tfrac{1}{2}(n^1-2\ell^1)\geq0+0=0.\]
This leaves the two versions of \textup{(i.3)}. Write $\rho=3$ when \textup{(D)} holds, and $\rho=2$ otherwise. Then
%Let's demonstrate that $(\ell^1+n^2)\geq3(\ell^2+n^3)$ when $N\geq2$ (where if $N=2$, we read $n^3$ as zero). As $I^2$ can contain no 0 or 1, 
the relevant version of \textup{(i.1)} is $\rho(2^{\ell^2}-1)-\ell^2\leq n^2$. Moreover, we've just shown that $n^3\leq g(\ell^2)=2^{\ell^2}-\ell^2-1$.
Then $(\ell^1+n^2)\geq (n^2+\ell^2)\geq\rho(2^{\ell^2}-1)\geq\rho(\ell^2+n^3)$.
\end{proof}
\begin{prop*}
Suppose that $N\geq1$ and that $S=(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)} with $\ell^N>0$. Let $(a_{N+1},\ldots,a_1)$ be the degree of $b(S)$.
\begin{enumerate}[i)]
\setlength{\parindent}{.25in}
\squishlist
\item Suppose that $N=1$. Then
\[a_1\geq3a_2+d.\]
\item Suppose that $N\geq2$. Then 
\[a_1\geq2(a_2+\cdots +a_{N+1})+2^{N-1}(d+1)-1\textup{ \ and \ }a_2\geq2(a_3+\cdots +a_{N+1}).\]
and when $S$ also satisfies \textup{(D)}, these inequalities may be strengthened:
\[a_1\geq\tfrac{9}{4}(a_2+\cdots +a_{N+1})+2^{N-1}(d+1)-1\textup{ \ and \ }a_2\geq3(a_3+\cdots +a_{N+1}).\]
\item Suppose that $N\geq3$. Then for $i$ satisfying $3\leq i\leq N$,
\[a_i\geq a_{i+1}+\cdots +a_{N+1}.\]
\end{enumerate}
\end{prop*}
\begin{proof}
Suppose that $N=1$, so that $(a_2,a_1)=(\ell^1,d+n^1+\ell^1)$. Then the inequality required is equivalent to $n^1\geq2\ell^1$, which we established in the previous proof, demonstrating (i).

Now suppose that $N\geq2$, and as before, write $\rho=3$ when \textup{(D)} holds, and $\rho=2$ otherwise. As all of the $\ell^i$ are at least 1, \textup{(c.3)} and \textup{(i.3)} imply:
\begin{itemise}
%\setlength{\parindent}{.25in}
\item $\rho a_3\leq a_2$ when $N=2$;
\item $a_4\leq a_3$ and $2\rho a_3\leq a_2$ when $N=3$;
\item $a_5\leq a_4$, $2a_4\leq a_3$ and $2\rho a_3\leq a_2$ when $N=4$;
\item $a_6\leq a_5$, $2a_5\leq a_4$, $2a_4\leq a_3$ and $2\rho a_3\leq a_2$ when $N=5$; etc.
\end{itemise}
These imply (iii), as when $3\leq i\leq N$:
\[a_i\geq 2a_{i+1}\geq a_{i+1}+2a_{i+2}\geq\cdots \geq a_{i+1}+\cdots +a_{N+1},\]
and when $N\geq3$, it proves the second inequality in each case of (ii):
\[a_2\geq 2\rho a_3\geq \rho a_3+\rho (a_4+\cdots +a_{N+1})=\rho (a_3+\cdots +a_{N+1}).\]
Note that when $N=2$, the second inequality in each case of (ii) is simply $\rho a_3\leq a_2$, which is already present in the above list.

All that remains is the first inequality in (ii) in each case, which relates $(a_2+\cdots a_{N+1})$ with $\overline{a}_1$, where, for brevity, we write $\overline{a}_1:=a_1-(2^{\ell^N+\cdots +\ell^2}(d+1)-1)$.
%\[\overline{a}_1:=a_1-(2^{\ell^N+\cdots +\ell^2}(d+1)-1)=2^{\ell^N+\cdots +\ell^2}(n^1+\ell^1).\]
By \textup{(i.4)}, and as $\ell^2>0$:%, and the relevant version of \textup{(i.3)}:
\[\overline{a}_1=2^{\ell^N+\cdots \ell^2}(n^1+\ell^1)\geq 3\cdot2^{\ell^N+\cdots +\ell^2-1}(\ell^1+n^2)\geq 3\cdot2^{\ell^N+\cdots +\ell^3}(\ell^1+n^2) =3a_2.\]
We've also shown that $a_2\geq\rho (a_3+\cdots +a_{N+1})$. Thus:
\[(\rho+1)\overline{a}_1\geq 3\rho a_2+3a_2 \geq 3\rho a_2+3\rho (a_3+\cdots a_{N+1})=3\rho(a_2+\cdots a_{N+1}),\]
proving that $\overline{a}_1\geq\frac{3\rho}{\rho+1}(a_2+\cdots a_{N+1})$, the first inequality in (ii) in either case.
\end{proof}

\begin{cor*}Suppose that $N\geq1$ and that $S=(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)}. Suppose further that $S\neq(\emptyset,\ldots,\emptyset)$. Then (without assuming that $\ell^N>0$):
\[a_1\geq2(a_2+\cdots +a_{N+1}+1).\]
If $S$ also satisfies \textup{(D)}, then the factor $2$ can be improved to $\tfrac{9}{4}$.
\end{cor*}
\begin{proof}
We can assume, without loss of generality, that $\ell^N>0$. Now when $d=1$, \textup{(A)} cannot be satisfied unless $I^1=\emptyset$, but this implies that $S=(\emptyset,\ldots,\emptyset)$, so the statement is vacuous unless $d\geq2$. If $N=1$, since $a_2=\ell^1>0$, whether or not $S$ satisfies \textup{(D)}, one finds
\[a_1\geq 3a_2+d \geq \tfrac{9}{4}a_2+ \tfrac{3}{4}+d\geq\tfrac{9}{4}a_2+\tfrac{11}{4}.\]
This leaves those cases when $N\geq2$ and $d\geq2$, but then $2^{N-1}(d+1)-1\geq5>\tfrac{9}{4}$.
\end{proof}
\end{KoszulSequenceCombinatorics}



\begin{CalculatingRepeatedKoszul}
\subsection{Calculation of $H^{(N)}:=(\derived\Ind{\nontop{N}})\cdots (\derived\Ind{\nontop{1}})H$}

What remains to be done then is to calculate the $H^{(N)}$, by calculating the Koszul complex on $H^{(N-1)}$ along with its differential, and taking homology. If there were no differentials at any stage, $H^{(N)}$ would have basis the $\Q(I^N)\cdots \Q(I^2)P(I^1)\imath$ for which $(I^N,\ldots,I^1)$ satisfies \textup{(A)}-\textup{(C)}. This is almost true: except for the Koszul complex on $H^{(1)}$ which calculates $H^{(2)}$, all of the Koszul complexes have zero differential. Thus, the correct subquotient of the above vector space takes a rather simple form.



%\begin{prop*}
%As a graded vector space,
%\[H^{(0)}=\left\langle \imath\right\rangle\]
%where $\|\imath\|=d$. As an object of $\LL{1}$, all the structure maps are trivial.
%\end{prop*}

\begin{prop*}
As a graded vector space,
\[H^{(1)}=\left\langle P(I^1)\imath\ \middle|\ (I^1)\textup{ satisfies \textup{(A)}}\right\rangle\]
%where $\|P(I^1)\imath\|=(\ell^1,d+n^1+\ell^1)$. 
As an object of $\LL{2}$, all the structure maps are trivial except for $\Q^1$, which is defined whenever $\ell^1>0$, and given by the formula
\[\Q^1:P(I^1)\imath\overset{\Q^1}{\mapsto} P(t_dI^1)\imath\textup{ when $\ell^1>0$}.\]
\end{prop*}
\begin{proof}
As $H^{(0)}=\left\langle \imath\right\rangle$ has all structure trivial, the Koszul complex has zero differential, and so \emph{equals} $H^{(1)}$. The calculation of $\LL{2}$ structure was made above.
\end{proof}

\begin{prop*}
As a graded vector space,
%\[H^{(2)}=\frac{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\ 1\notin I^2\right\rangle}{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\ 1,2\notin I^2,\ I^1\in\im(t_d)\textup{, and $\ell^1>2$}\right\rangle}.\]
%\[H^{(2)}=\frac{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\  (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(D)}}\right\rangle}{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\  (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(E)}}\right\rangle}.\]
\begin{alignat*}{2}
H^{(2)}
&=
\frac{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\  (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(D)}}\right\rangle}{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\  (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(E)}}\right\rangle}%
\\
% Left hand side
% Relation
&\cong
% Right hand side
{\left\langle \Q(I^2)P(I^1)\imath\ \middle|\  (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(D)} but not \textup{(E)}}\right\rangle}%
% Comment
\end{alignat*}
As an object of $\LL{3}$, all the structure maps are trivial except for $\Q^0$, which is defined whenever $\ell^1+n^2>0$, and is zero unless $\ell^2=0$ and $\ell^1=1$, in which case it is given by the formula \[\Q(\emptyset)P(I^1)\imath \overset{\Q^0}{\mapsto} \Q(\emptyset)P(t_dI^1)\imath\textup{ when $(\ell^2,\ell^1)=(0,1)$}.\]
\end{prop*}
\begin{proof}
The Koszul complex, as a vector space, is $\left\langle \Q(I^2)P(I^1)\imath\ \middle|\ (I^2,I^1)\textup{ satisfies \textup{(A)}-\textup{(C)}}\right\rangle$. % --- as $H^{(1)}$ is an object of $\LL{2}$, it supports no $\Q^0$ operations, explaining why $I^2$ mustn't contain zero. 
Now to calculate the differential, we use the following formula, setting $x=P(I^1)\imath$ and $I^2=(i_{\ell^2},\ldots,i_2,i_1)$
\[\partial(\Q(I^2)x)=\Q((i_{\ell^2},\ldots,i_2))(\Q^{i_1}x)+\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\sum_{\substack{\produces{J}{I^2}{\SqShift}\\(j_{\ell^2},\ldots,j_2)\in\admis{\SqShift}}}\!\!\!\!\!\!\!\!\!\!\!\! \Q((j_{\ell^2},\ldots,j_2))(\Q^{j_1}x).\]
Now the format of the $\SqShift$-Adem relations shows that in each summand, $j_1$ exceeds $i_1$. As $i_1$ cannot be zero, $j_1$ must then be at least two, so that $Q^{j_1}x=0$ by our calculation of the $\LL{2}$ structure of $H^{(1)}$. Thus, only the first term can be nonzero, and even this term vanishes if $i_1>1$. If $i_1=1$, then $\Q^{i_1}x=\Q^1x=P(I^1)\imath$, so that the differential is
\[\Q((i^2_{\ell^2},i^2_{\ell^2-1},\ldots,i^2_{2},1))P(I^1)\imath\mapsto \Q((i^2_{\ell^2},i^2_{\ell^2-1},\ldots,i^2_{2}))P(t_dI^1)\imath,\]
where any $\Q(I^2)P(I^1)\imath$ in which $I^2$ does not end in 1 is sent to zero. As all of these images are linearly independent (when nonzero), the kernel of $\partial$ is spanned by those basis elements in which $I^2$ contains no 1, explaining the presence of condition \textup{(D)} in the numerator.

Evidently, the denominator is to be the image of $\partial$. In order that $\Q(I^2)P(I^1)\imath$ is in the image, it must be that $I^1=t_dJ$, with the following conditions satisfied:
\begin{enumerate}[a)]
\squishlist
\setlength{\parindent}{.25in}
\item $J$ is $\delta$-admissible (with entries at least 2) and satisfies $\minDimP(J)\leq d$;
\item $I^2\star(1)$ is $\SqShift$-admissible;
\item $I^2\star(1)$ does not contain zero, and $\minDim(I^2\star(1))<\ell(J)$.
\end{enumerate}
%\begin{itemise}
%\setlength{\parindent}{.25in}
%\item[a)] $J$ is $\delta$-admissible and $\minDimP(J)\leq d$;
%\item[b)] $I^2\star(1)$ is $\SqShift$-admissible, with $\minDim(I^2\star(1))<\ell(J)$.
%\end{itemise}
We saw above that (a) is equivalent to the standard condition \textup{(A)} for $I^1$. Condition (b) and the first half of condition (c) together require simply that $I^2$ is $\SqShift$-admissible and does not contain any of 0, 1 or 2.

The condition on $\ell(J)$ is more interesting, and we consider two cases. Firstly, if $I^2=\emptyset$, it becomes $1<\ell(J)$, i.e.\ $\ell^1>2$. Secondly, if $I^2$ is nonempty, the admissibility condition in (b) demands that $I^2$ contains no 1 or 2, in which case $\minDim(I^2\star(1))=\minDim(I^2)-1$, so that $\minDim(I^2\star(1))<\ell(J)$ is equivalent to the standard condition $\minDim^2<\ell^1$. Note finally that we don't have to explicitly remove the condition $\ell^1>2$ in this case, as it holds automatically when $I^2$ is nonempty but contains no 1 or 2. This completes our identification of the image of $\partial$, as those sequences satisfying \textup{(A)}-\textup{(E)}.


%$J$ is $\delta$-admissible and $\minDimP(J)\leq d$, and It is in the image iff $I^1$ has a top operation at the left, say $t$, and $\Q(I^2\star(1))P(I^1\setminus \{t\})\imath$ is a valid element of $H^{(1)}$. In order for it to be valid, the $\SqShift$-admissibility condition implies that $I^2$ is either empty, or has rightmost entry at least 3. If $I^2$ is empty, in order that $\Q(I^2\star(1))P(I^1\setminus \{t\})\imath$ is allowable we need  $\minDim((1))=1<\ell^1-1$, explaining the condition on $\ell^1$. If $I^2$ is nonempty, one finds that the two inequalities $m(I^2\star(1))<\ell^1-1$ and $m(I^2)<\ell^1$ are equivalent, and as $I^2$ has a 3 or greater at right, $3\leq\minDim(I^2)<\ell^1$ implies the extra condition ``$\ell^1>2$'' anyway, so that we can leave the condition $\ell^1>2$ on the denominator without adding the caveat ``when $I^2$ is empty''. This completes the identification of the underlying vector space.

Next, by the results of the previous section, all operations but $\Q^0$ are zero. Consider the operation $Q^0$ on cycles $\Q(I^2)P(I^1)\imath$ with $\ell^2>0$. As we look only at cycles, none of the $I^2$ appearing contain a 1. However, it is only $\Q^1$ which can be nonzero on $H^{(1)}$, so our lemma above applies, and these operations vanish. Finally, if $\ell^2=0$ we are supposed to simply apply $\Q^{\ell^1}$ to $P(I^1)\imath$, and this is only nonzero when $\ell^1=1$, finishing the proof.
\end{proof}

\begin{prop*}
For $N\geq2$, as a graded vector space,
%\[H^{(N)}=\frac{\left\langle \Q(I^N)\cdots \Q(I^2)P(I^1)\imath\ \middle|\ 1\notin I^2\right\rangle}{\left\langle \Q(I^N)\cdots \Q(I^2)P(I^1)\imath\ \middle|\ 1,2\notin I^2,\ I^1\in\im(t_d)\textup{, and $\ell^1>2$}\right\rangle}.\]
\[H^{(N)}={\left\langle \Q(I^N)\cdots \Q(I^2)P(I^1)\imath\ \middle|\  (I^N,\ldots,I^1)\textup{ satisfies \textup{(A)}-\textup{(D)} but not \textup{(E)}}\right\rangle}.\]
As an object of $\LL{N+1}$, all the structure maps are trivial except for $\Q^0$, which is zero unless $\ell^N=\cdots =\ell^2=0$ and $\ell^1=1$, in which case it is given by the formula
\[\Q(\emptyset)\cdots \Q(\emptyset)P(I^1)\imath \overset{\Q^0}{\mapsto} \Q(\emptyset)\cdots \Q(\emptyset)P(t_dI^1)\imath\textup{ when $(\ell^N,\ldots,\ell^1)=(0,\ldots,0,1)$}.\]
%$\Q(\emptyset)\cdots \Q(\emptyset)P(I^1)\imath\mapsto \Q(\emptyset)\cdots \Q(\emptyset)P(t_dI^1)\imath$.
\end{prop*}
\begin{proof}
In order to obtain this description of the underlying vector space, we must show that none of the Koszul complexes have nonzero differential from this point on. This is true of the Koszul complex calculating $H^{(3)}$, as the only nonzero operation on $H^{(2)}$ is a \emph{top} operation. If this pattern continues, we'll never see any differentials.

By our theorems above, the only operations with a chance of being nonzero are the $Q^0$. As before, consider the operation $Q^0$ on cycles $\Q(I^3)\Q(I^2)P(I^1)\imath$ with $\ell^3>0$. On these classes, $\ell^2>0$, so that $\Q(I^2)P(I^1)\imath$ is in the kernel of $\Q$ operation defined thereupon. Our lemma above then shows that $Q^0$ vanishes on such cycles. Next, consider $\Q^0$ on cycles $\Q(\emptyset)\Q(I^2)P(I^1)\imath$. This takes value $\Q(\emptyset)\Q^{\ell^2}\Q(I^2)P(I^1)\imath$, which is only nonzero if $\ell^2=0$ and $\ell^1=1$. This confirms all our claims for $N=3$, and these arguments can be repeated for larger $N$.
\end{proof}
\subsection{Concise descriptions of the $H^{(N)}$}
In order to simplify notation, we'll organise the relevant sequences $(I^{N},\ldots,I^1)$ of admissible sequences parameterising a basis of $H^{{(N)}}$ as follows.
\begin{itemize}
\squishlist
\item Let $\calS^{(0)}$ be the set which contains only the empty sequence.
\item Let $\calS^{(1)}$ be the set of (length one) sequences of sequences $(I^1)$ satisfying \textup{(A)}.
%\item For $N\geq2$, let $\calS^{(N)}$ be the set of (length $N$) sequences of sequences $(I^{N},\ldots,I^1)$ satisfying conditions \textup{(A)}-\textup{(C)}, such that $1\notin I^2$, and for which it is not true that ``$1,2\notin I^2,\ I^1\in\im(t_d)\textup{, and $\ell^1>2$}$''.
\item For $N\geq2$, let $\calS^{(N)}$ be the set of (length $N$) sequences of sequences $(I^{N},\ldots,I^1)$ satisfying conditions \textup{(A)}-\textup{(D)} but not \textup{(E)}.
%\item Write $b(S):=\Q(I^{N})\cdots \Q(I^2)P(I^1)\imath\in H^{(N)}$, for $S=(I^{N},\ldots,I^1)\in \calS^{(N)}$.
\end{itemize}
Then we've proven that for all $N\geq0$, $H^{(N)}=\langle b(S)\ |\ S\in\calS^{(N)}\rangle$.
%Note also that for $N\geq1$ we have $H^{(N)}_0=\langle b(S)\ |\ S\in\calS^{(N-1)}\rangle$. Next we form three subsets of $\calS^{(N)}$ (what range on $N$?).
In order to help simplify the continuing exposition, define, for $N\geq0$:
\begin{alignat*}{2}
\calS^{(N)}_1
&:=
\{S\in \calS^{(N)}\ |\ \ell^{N}=\cdots =\ell^2=0,\ \ell^1=1\}%
\\
&\phantom{:}=
\{(\emptyset,\ldots,\emptyset,(i))\ |\ 2\leq i\leq d\}&\qquad&\text{(if $N>0$)}
\end{alignat*}
and let $\overline{t}_d:\calS_1^{(N)}\to\calS^{(N)}$ be the function $(\emptyset,\ldots,\emptyset,I^1)\mapsto (\emptyset,\ldots,\emptyset,t_dI^1)$. Next, define
%\[\calS^{(N)}_2=\im(\overline{t}_d)=\{(\emptyset,\ldots,\emptyset,(d+i+1,i))\ |\ 2\leq i\leq d\},\]
\begin{alignat*}{2}
\calS^{(N)}_2
&:=
\im(\overline{t}_d)%
\\
% Left hand side
% Relation
&\phantom{:}=
% Right hand side
\{(\emptyset,\ldots,\emptyset,(d+i+1,i))\ |\ 2\leq i\leq d\}% Comment
&\qquad&\text{(if $N>0$)}
\end{alignat*}
and finally:
\[\calS^{(N)}_3:=\calS^{(N)}\setminus(\calS^{(N)}_1\cup \calS^{(N)}_2\cup\{(\emptyset,\ldots,\emptyset)\}).\]
In case $N=0$, $\calS^{(N)}_1$, $\calS^{(N)}_2$ and $\calS^{(N)}_3$ are all empty. For all $N\geq0$, $\calS^{(N)}$ is the disjoint union:
\[\calS^{(N)}=\{(\emptyset,\ldots,\emptyset)\}\cup\calS^{(N)}_1\cup\calS^{(N)}_2\cup\calS^{(N)}_3.\]

\begin{thm*}
If we decompose $H^{(1)}\in\LL{2}$ as
%\[H^{(1)}= \left\langle b(S)\ \middle|\ S\textup{ satisfies \textup{(A)}, $S\notin\im(t_d)$}\right\rangle\oplus \left\langle b(S)\ \middle|\ S\textup{ satisfies \textup{(A)}, $S\in\im(t_d)$}\right\rangle\]
\[H^{(1)}= \left\langle \Q(I^1)\imath\ \middle|\ I^1\textup{ satisfies \textup{(A)}, $I^1\notin\im(t_d)$}\right\rangle\oplus \left\langle \Q(I^1)\imath\ \middle|\ I^1\textup{ satisfies \textup{(A)}, $I^1\in\im(t_d)$}\right\rangle\]
then $\Q^1$, the only operation which is ever nonzero, has image the second summand. [Recall that $t_d$ is only defined when $\ell^1\geq1$, just as $Q^1$ is only defined on $Q(I^1)\imath$ when $\ell^1\geq1$.]

For $N\geq2$, if we decompose $H^{(N)}\in\LL{N+1}$ as
%Then we can further decompose $H^{(N)}$ as follows:
%\[H^{(n)}=\langle \imath\rangle\oplus \left\langle b(S)\ \middle|\ S\in\calS_3^{(N)}\cup \calS_1^{(N)}\right\rangle \oplus \left\langle b(S)\ \middle|\ S\in\calS_2^{(N)}\right\rangle\]
\[H^{(N)}=
\left\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle\oplus 
\left\langle b(S)\ \middle|\ S\in\calS_1^{(N)}\right\rangle \oplus \left\langle b(S)\ \middle|\ S\in\calS_2^{(N)}\right\rangle \oplus\left\langle b(S)\ \middle|\ S\in\calS_3^{(N)}\right\rangle\]
then the first, second and fourth summands consist of indecomposable elements, while the third summand is the isomorphic image of the second under the operation $\Q^0$.

For $N\geq1$, if we decompose $H^{(N)}_0\in\PRLie{N}$ as 
\[H^{(N)}_0=\left\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle\oplus \left\langle b(S)\ \middle|\ S\in\calS_1^{(N-1)}\right\rangle \oplus \left\langle b(S)\ \middle|\ S\in\calS_2^{(N-1)}\right\rangle \oplus\left\langle b(S)\ \middle|\ S\in\calS_3^{(N-1)}\right\rangle,\]
and the restriction, defined on the last three summands, sends the second isomorphically onto the third, and vanishes on the third and fourth summands.
\end{thm*}
%Then for $N\geq2$, if we decompose $H^{(N)}$ as
%%Then we can further decompose $H^{(N)}$ as follows:
%%\[H^{(n)}=\langle \imath\rangle\oplus \left\langle b(S)\ \middle|\ S\in\calS_3^{(N)}\cup \calS_1^{(N)}\right\rangle \oplus \left\langle b(S)\ \middle|\ S\in\calS_2^{(N)}\right\rangle\]
%\[H^{(n)}=\langle \imath\rangle\oplus \left\langle b(S)\ \middle|\ S\in\calS_1^{(N)}\right\rangle \oplus \left\langle b(S)\ \middle|\ S\in\calS_2^{(N)}\right\rangle \oplus\left\langle b(S)\ \middle|\ S\in\calS_3^{(N)}\right\rangle\]
%then the first, second and fourth summands consist of indecomposable elements, while the third summand is the isomorphic image of the second under the operation $\Q^0$.
%
%Next, for $N=1$, if we decompose $H^{(1)}$ as
%\[H^{(1)}= \left\langle b(S)\ \middle|\ S\textup{ satisfies \textup{(A)}, $S\notin\im(t_d)$}\right\rangle\oplus \left\langle b(S)\ \middle|\ S\textup{ satisfies \textup{(A)}, $S\in\im(t_d)$}\right\rangle\]
%then $\Q^1$, the only operation which is ever nonzero, has image the second summand. Recall that $t_d$ is only defined on $I^1$ such that $\ell^1\geq1$.
%




%\begin{itemize}
%\squishlist
%\setlength{\parindent}{.25in}
%%\item Define $\calS^{(N)}_1:=\calS^{(N)}\cap\{(I^{N},\ldots,I^1)\ |\ \ell^{N}=\cdots =\ell^2=0,\ \ell^1=1\}$. This is the set of sequences $S$ such that $b(S)\in H^{(N+1)}_0$ supports a nonzero restriction.
%%\item Define $\calS^{(N)}_1:=\calS^{(N)}\cap\{(I^{N},\ldots,tI^1)\ |\ \ell^{N}=\cdots =\ell^2=0,\ \ell^1=1\}$. This is the set of sequences $S$ such that $b(S)\in H^{(N+1)}_0$ is the image of a restriction.
%%%\item Define $\calS^{(N-1)}_2:=S^{(N-1)}\cap\{(I^{N-1},\ldots,t(I^1))\ |\ \ell^{N-1}=\cdots =\ell^2=0,\ \ell^1=1\}$, the set of sequences $S$ such that $b(S)\in H^{(N)}_0$ is the image of a restriction.
%%\item Let $t:\calS_1^{(N)}\to\calS_2^{(N)}$ be the function $(I^{N},\ldots,I^1)\mapsto (I^{N},\ldots,tI^1)$.
%%\item Define $\calS^{(N)}_3:=\calS^{(N)}\setminus(\calS^{(N)}_1\cup \calS^{(N)}_2\cup\{(\emptyset,\ldots,\emptyset)\})$, the set of sequences $S$, not in $\calS^{(N)}_1$ or $\calS^{(N)}_2$, such that the restriction is defined on $b(S)$.
%\item %$\calS^{(N)}_1:=\{S\in \calS^{(N)}\ |\ \ell^{N}=\cdots =\ell^2=0,\ \ell^1=1\}=\calS^{(N)}\cap\{(\emptyset,\ldots,\emptyset,I^1)\ |\ \ell^1=1\}$.
%\begin{alignat*}{2}
%\calS^{(N)}_1
%&:=
%\{S\in \calS^{(N)}\ |\ \ell^{N}=\cdots =\ell^2=0,\ \ell^1=1\}%
%\\
%&=
%\{(\emptyset,\ldots,\emptyset,(i))\ |\ 2\leq i\leq d\}
%\end{alignat*}
%
%
%%\item Define $\calS^{(N)}_2:=\calS^{(N)}\cap\{(\emptyset,\ldots,\emptyset,t_dI^1)\ |\ \ell^1=1\}$.
%\item Let $t:\calS_1^{(N)}\to\calS^{(N)}$ be the function $(\emptyset,\ldots,\emptyset,I^1)\mapsto (\emptyset,\ldots,\emptyset,t_dI^1)$.
%\item Let $\calS^{(N)}_2$ be the image of $t_d$.
%\item Define $\calS^{(N)}_3:=\calS^{(N)}\setminus(\calS^{(N)}_1\cup \calS^{(N)}_2\cup\{(\emptyset,\ldots,\emptyset)\})$.
%\end{itemize}
\end{CalculatingRepeatedKoszul}

\begin{DimZeroPart}
\subsection{Calculation of $E^{2,N}=(\derived\Ind{\LL{N+1}})H^{(N)}$ along the first two axes}

\begin{shaded}
\[E^{2,N}_{0,a_{N+1},a_N,\ldots,a_1}=(\Ind{\LL{N+1}}H^{(N)})_{a_{N+1},\ldots,a_1}.\]
\[E^{2,N}_{a_{N+2},0,a_N,\ldots,a_1}=H_{a_{N+2}+1}\left(H^{(N)}_0\right)_{a_N,\ldots,a_1}\]
\[H_{*}\left(H^{(N)}_0\right)=E\left\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle \otimes E\left\langle b(S)\ \middle|\ S\in\calS_1^{(N-1)}\right\rangle\otimes \Gamma_\textup{ev}\left\langle b(S)\ \middle|\ S\in\calS_2^{(N-1)}\right\rangle\otimes \Gamma\left\langle b(S)\ \middle|\ S\in\calS_3^{(N-1)}\right\rangle \]
\end{shaded}

Suppose that $N\geq1$, so that $E^{2,N}:=(\derived\Ind{\LL{N+1}})H^{(N)}\in\GR{N+2}$ is the $E^2$ page of the $N^\textup{th}$ Grothendieck spectral sequence. The results of the previous section allow a complete calculation of the groups
\[E^{2,N}_{0,a_{N+1},a_N,\ldots,a_1}=\Ind{\LL{N+1}}H^{(N)}.\]
\begin{prop*}
The graded vector space $E^{2,N}_{0,a_{N+1},a_N,\ldots,a_1}\in\GR{N+1}$ is
\[\left\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle\oplus\left\langle b(S)\ \middle|\ S\in\calS_3^{(N)}\cup\calS_1^{(N)}\right\rangle.\]
\end{prop*}
%\subsection{Calculation of $E^{2,N}=(\derived\Ind{\LL{N+1}})H^{(N)}$ in zero internal dimension}

We can also completely calculate the groups
\[E^{2,N}_{a_{N+2},0,a_N,\ldots,a_1}\]
using partially restricted Lie algebra homology. From the section on low dimensional calculations:
\[E^{2,N}_{a_{N+2},0,a_N,\ldots,a_1}:=((\derived_{a_{N+2}}\Ind{\LL{N+1}})H^{(N)})_{0,a_{N},\ldots,a_1}\cong ((\derived_{a_{N+2}}\Ind{\PRLie{N}})H^{(N)}_0)_{a_{N},\ldots,a_1}\]
%The point now is that $H^{(N)}_0\in\PRLie{N}$ is easy to describe, for all $N\geq1$. As a vector space it is $\langle b(S)\ |\ S\in\calS^{(N-1)}\rangle$. It has Lie bracket zero. Its restriction, defined whenever $\ell_{N-1},\ldots,\ell_1$ are not all zero, is only nonzero when %in case $a_N=\cdots =a_3=0$ and $a_2=1$, that is, when 
%$\ell^N=\cdots =\ell^2=0$ and $\ell^1=1$, in which case:
%\[\Q(\emptyset)\cdots \Q(\emptyset)P(I^1)\imath\overset{\restn{}}{\mapsto}\Q(\emptyset)\cdots \Q(\emptyset)P(t_dI^1)\imath.\]
%Note that all of the classes $\Q(\emptyset)\cdots \Q(\emptyset)P(t_dI^1)\imath$, where $\ell^1=1$, are linearly independant in $H^{(N)}_0$. Moreover, there is only one basis element in non-restrictable dimensions, and that is $\Q(\emptyset)\cdots \Q(\emptyset)P(\emptyset)\imath$.
\begin{prop*}
The graded vector space $E^{2,N}_{a_{N+2},0,a_N,\ldots,a_1}\in\GR{N+1}$ is isomorphic (as a graded vector space only) to the kernel of the counit of the coalgebra
\[E\left\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle \otimes E\left\langle b(S)\ \middle|\ S\in\calS_1^{(N-1)}\right\rangle\otimes \Gamma_\textup{ev}\left\langle b(S)\ \middle|\ S\in\calS_2^{(N-1)}\right\rangle\otimes \Gamma\left\langle b(S)\ \middle|\ S\in\calS_3^{(N-1)}\right\rangle \]
where by $\Gamma_{\textup{ev}}$ we mean the even divided powers. To calculate the degree of an expression $\prod_j\gamma_{i_j}(x_j)$, one takes $a_{N+2}$ to be $\sum_ji_j-1$, $a_{N+1}$ to be 0, and $(a_N,\ldots,a_1)$ to be $\sum_ji_j\|x_j\|$. That is, to calculate the degree $a_{N+2}$ part, we need to look at monomials of total exponent $a_{N+2}+1$.
\end{prop*}
\begin{proof} %For the course of this proof, we will supress the $(N-1)$ superscripts that normally appear on the $\calS^{(N-1)}$, and also the parentheses that usually appear in $b(S)$.
The Eilenberg-Cartan-May complex is $E\langle \imath\rangle\otimes \Gamma\left\langle bS\ \middle|\ S\in \calS_1^{(N-1)}\cup\calS_2^{(N-1)}\cup\calS_3^{(N-1)}\right\rangle$ as a vector space. As so few operations are nonzero, it splits into a tensor product of complexes
\[E\langle \imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\rangle\otimes \!\!\!\!\!\bigotimes_{S\in\calS_1^{(N-1)}}\!\!\!\!\!\Gamma\langle\rule{0mm}{\heightof{$\calS_1^{(N)}$}} bS,b\overline{t}_dS\rangle\otimes \Gamma\left\langle bS\ \middle|\ S\in \calS_3^{(N-1)}\right\rangle\]
where only the factors $\Gamma\langle bS,b\overline{t}_dS\rangle$ have nonzero differential. The differential on $\Gamma\langle bS,b\overline{t}_dS\rangle$ is
\[\gamma_i( bS)\cdot\gamma_j(b\overline{t}_dS)\mapsto\gamma_{i-2}( bS)\cdot b\overline{t}_dS\cdot\gamma_j(b\overline{t}_dS)=\begin{cases}
\gamma_{i-2}(bS)\cdot\gamma_{j+1}(b\overline{t}_dS),&\textup{if }j\textup{ is even};\\
0,&\textup{if }j\textup{ is odd},
%\\,&\textup{if }
\end{cases}
\]
so that $H_*(\Gamma\langle bS,b\overline{t}_dS\rangle)$ has basis the expressions $\gamma_i(bS)\cdot\gamma_j(b\overline{t}_dS)$ for $i\leq1$ and $j$ even.

Finally note that the CEM complex calculates partially restricted Lie algebra homology, which is only Quillen homology up to a shift, explaining why $a_{N+2}$ is $(\sum i_j)-1$.
\end{proof}

\end{DimZeroPart}

\begin{VanishingLines}
\subsection{A vanishing line}
A class in $E^{2,N}_{a_{N+2},\ldots,a_1}$ has dimensions $s=a_{N+2}+\cdots +a_2$ and $t=a_1$ on the $E_2$ page of the Adams spectral sequence. Now we've seen above that $E^{2,N}_{0,a_{N+1},a_N,\ldots,a_1}$ is a subquotient of
\[\left\langle b(S)\ \middle|\ S\in\calS^{(N)}\right\rangle_{a_{N+1},\ldots,a_1}\]
so that any homogeneous class therein satisfies $t\geq\tfrac{9}{4}s$.
Next, $E^{2,N}_{a_{N+2},0,a_N,\ldots,a_1}$ is a subquotient of
\[\left(\Sigma^{-1}\left(E\left\langle s\imath\rule{0mm}{\heightof{$\calS_1^{(N)}$}}\right\rangle\otimes \Gamma\left\langle sb(S)\ \middle|\ S\in\calS^{(N-1)}\right\rangle\right)\right)_{a_{N+2},0,a_N,\ldots,a_1}\]
Now an expression in this algebra is $\gamma_a(s\imath)\cdot\prod_{j}\gamma_{b_j}(sb(S))$, where $a$ is either 0 or 1, and the $b_j$ are positive integers. Every $sb(S)$ has degree $(1,0,a_N,\ldots,a_1)$, where we've proven that $a_1\geq \tfrac{9}{4}(a_2+\cdots +a_{N+1})$. On the other hand, $s\imath$ has degree $(1,0,\ldots,0,d)$, which does not satisfy that inequality unless $d\geq3$. Thus that the dimension of a product $\gamma_a(s\imath)\cdot\prod_{j}\gamma_{b_j}(sb(S))$, when viewed as being in $E^{2,N}$, satisfies $t\geq\tfrac{9}{4}s-1-\tfrac{5}{4}$. Here, the $-1$ comes from the desuspension, and the $-\tfrac{5}{4}$ comes from the possible appearance of the class $s\imath$. This proves
\begin{thm*}
The Adams spectral sequence for a positive sphere admits a vanishing line of slope $\tfrac{4}{5}$: 
\[E_2^{s,t}=0\textup{\ for $s> \tfrac{4}{5}(t-s)+\tfrac{9}{5}$.}\]
%In particular, the Adams spectral sequence converges on positive spheres.
\end{thm*}
In fact, the same arguments will prove the following
\begin{thm*}
Suppose that $X$ is a simplicial commutative algebra which is connected, and is of finite type in dimension 1. That is, $H^0_Q(X)=0$ and $H^1_Q(X)$ is a finite dimensional $\F_2$-vector space. Then the Adams spectral sequence for $X$ has a vanishing line of slope 1.
\end{thm*}

\end{VanishingLines}


\begin{TotalisationInSAlg}
\section{The Adams Spectral Sequence}
\subsection{Cosimplicial objects in $s\Comm$}
\begin{prop*}
Suppose that $X^\bullet$ is a cosimplicial object in $s\Comm$. Then for $0\leq m\leq\infty$, $I\Tot_m(X^\bullet)\cong\Tot_m(IX^\bullet)$, where $I$ is the right adjoint in the adjunction $\textup{Sym}:s\Vect\rightleftarrows s\Comm:I$, and the second totalization is that of a cosimplicial simplicial vector space.
\end{prop*}
\begin{proof}
The totalization of a cosimplicial object in $s\Comm$ is defined by the end
\[\Tot_m(X^\bullet):= \int_{[k]\in\Delta}\left(X^k\right)^{\textup{sk}_m\Delta[k]}\]
where for each $k$, the cotensor within the end is defined by taking various powers of the $X^k_t$ in each simplicial dimension $t$. As $I$ is the prolongation of the right adjoint in $\Vect\rightleftarrows\Comm$, it commutes with all of these limits.
\end{proof}
Following \cite{BousfieldHSSCS.pdf}, for $\textbf{B}$ a cosimplicial simplicial vector space, let $N^*N_*\textbf{B}$ be the normalized double complex. The total complex $T\textbf{B}$ is then defined by
\[(T\textbf{B})_n=\prod_{t-s=n}N^sN_t\textbf{B},\ \textup{with filtration }(F^mT\textbf{B})_n=\prod_{\substack{t-s=n\\t\geq m}}N^sN_t\textbf{B}.\]
Now if we write
\[(T_m\textbf{B})_n:=(T\textbf{B}/F^{m+1} T\textbf{B})_n\cong\prod_{\substack{t-s=n\\t\leq m}}N^sN_t\textbf{B}, \]
then $F^mT\textbf{B}$ is a decreasing filtration and the $T_m\textbf{B}$ form a tower of surjections of chain complexes with inverse limit $T_\infty\textbf{B}=T\textbf{B}$. 
\begin{lem*}[{\cite[Lemma 2.2]{BousfieldHSSCS.pdf}}]
There are natural chain maps $\phi_m:N_*\Tot_m\textbf{B}\to T_m\textbf{B}$ for $m\leq\infty$ which induce isomorphisms $\pi_*\Tot_m\textbf{B}\to H_*T_m\textbf{B}$ and are compatible with the tower maps $\Tot_{s}\textbf{B}\to\Tot_m\textbf{B}$ and $T_{s}\textbf{B}\to T_m\textbf{B}$ for $s\geq m$.
\end{lem*}
\begin{cor*}
Suppose that $X^\bullet$ is a cosimplicial object in $s\Comm$. Then there is a map of spectral sequences, which is an isomorphism from $E^1$, from the homotopy spectral sequence of the $\Tot$ tower $\{I\Tot_mX^\bullet\}$ to the spectral sequence of the bicomplex underlying $IX^\bullet$. Moreover, there is an isomorphism $\pi_*I\Tot X^\bullet\to H_*TIX^\bullet$ (to the homology of the total complex of the bicomplex), which is compatible with the map of spectral sequences.
\end{cor*}
\begin{cor*}
Suppose that $X$ is a connected element of $s\Comm$. Then the Adams spectral sequence for $X$ is the spectral sequence of the bicomplex underlying the cosimplicial simplicial vector space $I((c(K\overline{Q})^\bullet X)^{\textup{rf}})$. This spectral sequence admits a vanishing line from $E^2$, and so converges strongly to its target, $\pi_{t-s}(I\hat X)$.
\end{cor*}
\end{TotalisationInSAlg}



\begin{Endmatter}
\printbibliography
\end{Endmatter}
\end{document}














