% !TEX root = z_output/_questions.tex
\documentclass[11pt]{article}
%\newcommand{\dontloadhyperref}{}
\input{../macros.tex}
\setcounter{secnumdepth}{1}

\title{Questions}
\begin{document}
\tableofcontents
\newcommand{\HSsection}[2]{\subsection{#1}}
%{\subsection{#1 \hfill \small{#2}}} Doesn't work well with contents page


\HSsection{Preface}{}
Some things I should figure out some time.

\HSsection{Things to read}{}
\newcommand{\BooK}[2]{\item #1 --- #2}
\begin{itemise}
\BooK{Atiyah}{K-Theory}
\BooK{Rudyak}{On Thom Specta, Orientability and Cobordism}
\BooK{May}{The Geometry of Iterated Loop Spaces}
\BooK{Mosher \& Tangora}{Cohomology operations, etc.}
\BooK{Adams}{Stable Homotopy and Generalised Homology}
\BooK{Adams}{On the structure and applications of the Steenrod algebra}
\BooK{May}{Simplicial Objects in Algebraic Topology}
\BooK{Dwyer and Spalinski}{Homotopy theories and model categories}
\BooK{Adams}{Algebraic Topology in the Last Decade}
\end{itemise}

\HSsection{Two definitions of the transgression}{29/6/11}
Why does the normal definition of the transgression agree with Mark's?
%\[H^n(F)\to H^n(\Omega B)=H^{n+1}(\Sigma\Omega B)\longleftarrow H^{n+1}(B).\]
\[\xymatrix{
\text{Mark's:}&&\ar[dr]H^n(F)\ar[r]& H^n(\Omega B)\ar@{=}[r]&H^{n+1}(\Sigma\Omega B)&\ar[l] H^{n+1}(B)\\
\text{Normal:}&&&H^{n+1}(E,F)&H^{n+1}(B,*)\ar[ru]\ar[l]
}\]
What's the dual picture for homology?
How does the transgression really work in the first place?
\HSsection{Figure out what's going on with the Bockstein}{30/6/11}
Is the idea to write the exact couple whose top line is:
\[\xymatrix{
H^*\ar@{=}[r]&H^*\ar[r]^{\times2}&H^*\ar[r]^{\times2}&H^*\ar[r]^{\times2}&H^*\ar[r]&\cdots\ar[r]&\varprojlim H^*=H^*[\nicefrac{1}{2}]
}\]
and thus analyze the failure of $H^*\to H^*[\nicefrac{1}{2}]$ to be an isomorphism?

Also, read http://eom.springer.de/c/c023150.htm for how to figure out stuff about $H(\DASH)$ from differentials in the BSS.
\HSsection{Why is a grouplike topological monoid a topological group?}{30/6/11}

\HSsection{Spaces which are products of Eilenberg-MacLane spaces}{6/7/11}
A connected space $X$ is a product of EM spaces iff the Hurewicz homomorphism is the 
inclusion of a direct summand $\pi_*(X)\to H_*(X)$. See May's `Simplicial objects',
Thm 24.5.

\HSsection{Is a Serre fibration of CW-complexes a Hurewicz fibration?}
{10/8/11}
There's a lot of doubt about this.
\end{document}
















