% !TEX root = z_output/_Recitations.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%% 80 characters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\input{../macros.tex}

\excludeversion{1802Graphing}
\includeversion{Minseon Chat on Rep thy}

\begin{document}
\begin{1802Graphing}

\subsection*{An 18.02A recitation on graphing functions}

\begin{enumerate}\squishlist
\item Define $f(x,y)=\sqrt{16-x^2-y^2}$.
\begin{enumerate}
\item For what values of $(x,y)$ is this function defined?
\item Draw the contours $z=4,2,0$. (What happens when $z>4$ or $z<0$?)
\item Find where $f(x,y)$ takes minimum/maximum values.
\item Calculate the partial derivatives $\frac{\partial f}{\partial x}$ and $\frac{\partial f}{\partial y}$, and check that these are zero at the maximum point.
\item Describe the surface.
\item Consider the parametric equation $r(t)=2\hat i + t\hat j + f(x_0,t)\hat k$. This is a curve parameterising the cross-section $x=1$. Calculate the velocity vector at $t=1$. 
\item Calculate $\frac{\partial f}{\partial y}\bigr|_{(2,1)}$.
\end{enumerate}
\item Define  $f(x,y)=1+|x-y|$.
\begin{enumerate}
\item Draw the contours $z=2,1,0,-1,-2$.
\item Identify the direction of steepest ascent at the point $(x,y)=(1,0)$, (it should be perpendicular to the contour through that point).
\item How does the direction of steepest ascent relate to the vector $\left(\frac{\partial f}{\partial x}|_{(1,0)},\frac{\partial f}{\partial y}|_{(1,0)}\right)$
\item Find where $f(x,y)$ takes minimum/maximum values.
\end{enumerate}
\item Define  $f(x,y)=e^{x}\sin y$.
\begin{enumerate}
\item Draw the cross-sections $x=-1$, $x=0$ and $y=1$.
\item Draw the surface!
%\item Fix $x_0$, and parameterise a path $r(t)$ in $\R^3$ by $r(t)=x_0\hat i + t\hat j + f(x_0,t)\hat k$. This path traces out the cross-section $x=x_0$ of the graph. Calculate the velocity vector at $t=t_0$. How does it relate to the value of the partial derivative $\frac{\partial f}{\partial x}|_{(x_0,t_0)}$? To 1.
\end{enumerate}
%\item Define  $f(x,y)=\sin(\sqrt{x^2+y^2})$.
%\begin{enumerate}
%\item Draw the contours $z=1,0,-1$, and any more that you would like to.
%\item Draw the surface!
%\end{enumerate}
%\item Graph $f(x,y)=x^2y^2$
%\begin{enumerate}
%\item Draw the contours $z=2,1,0,-1$.
%\item Draw the cross-sections $x=-1,x=0,x=1$.
%\item Draw the surface!
%\end{enumerate}
%\item Using these techniques, graph: $f(x,y)=x/|y|$.
\end{enumerate}
\end{1802Graphing}
\begin{Minseon Chat on Rep thy}
\subsection*{What we talked about today...}
Suppose that $k$ is an algebraically closed field of characteristic 0.
\begin{itemize}\squishlist
\item  Suppose that $G$ is a finite group:
\begin{itemize}\squishlist

\item there are $r$ irreducible modules\footnote{An irreducible module $W$ of $G$ is a module with no submodule $W'$ other than $0$ and $W$ itself.} $I_1,\ldots,I_r$ of $G$, where $r$ is the number of conjugacy classes of $G$.
\item Whenever $W$ is a module of $G$, we have an isomorphism, for unique $n_1,\ldots,n_r\geq0$:
\[W=\bigoplus_{i=1}^{r}I_i^{n_i}\]
Choose any isomorphism of $G$-modules:
\[f:\bigoplus_{i=1}^{r}I_i^{n_i}\to W.\]
Then the submodule $f(I_i^{n_i})\subset W$ is independent of choice of $f$. Call it $W_i$, so that we have a canonical decomposition:
\[W=\bigoplus_{i=1}^{r}W_i.\]
This gave a canonical decomposition of $W$ into submodules which, while \textbf{not} being irreducible, are direct sums of irreducibles of the same isomorphism type.
\end{itemize}
\item Suppose further that $G$ is abelian. 
\begin{itemize}\squishlist
\item From the formula $\sum(\dim I_i)^2=\# G$, we deduce that each $I_i$ is 1-dimensional.
\item The group $\Aut k$ of automorphisms of a 1-dimensional vector space is isomorphic to the group $k^*$ of nonzero elements of $k$.
 Thus, 1-dimensional modules are the same as homomorphisms $G\to k^*$.
\end{itemize}
\item Suppose further that $G=\Z/n\Z$ is cyclic of order $n$.
\begin{itemize}\squishlist
\item Then a homomorphism $G\to k^*$ is the same as an $n^\textup{th}$ root of unity in $k$, as given $\rho$ such that $\rho^n=1$, we can define a homomorphism:
\[k+n\Z\mapsto \rho^k.\]
\item The irreducible modules are given by setting $I_i=k$, with action
\[(k+n\Z)\cdot v:=\rho^kv.\]
\item Finally, given any module $W$ of $G$, one can recover the subspaces $W_i$ as the $\rho^i$-eigenspace of the operator $(1+n\Z)$ acting on $W$!
\end{itemize}
\end{itemize}
We can talk more later about how this relates to your question, but hey, I thought it might be helpful for me to get this down. Maybe you'd like to think about it in the meantime.
%Ok, so now, let $W=I(V)$, where $V$ is a nonempty algebraic set in $\A^1$ which is a union of lines through the origin. Then $W$ is a $k^*$-module, as we saw today. It's infinite dimensional, but it's the union of the finite dimensional submodules 
%\[W^{\leq N}=\left\{f\in I(V)\,:\,\deg(f)\leq N\right\}.\]
%Let $N$ be really really big, so that we only need to think about $W':=W^{\leq N}$.
%
%Now for any $n$, $C_n$ lives inside $k^*$ as the group of $n^{\textup{th}}$ roots of unity. Thus $C_n$ acts of $W'$. I claim that considering the subspaces $(W')_i$ of $W'$ for various $i$ and $n$, one can see that $W$ splits up.
\end{Minseon Chat on Rep thy}

\end{document}


























